---
title: "moodVariability"
author: "Ryan Yan"
date: "2024-01-16"
output:
  html_document:
    df_print: paged
  html_notebook:
    code_folding: hide
  pdf_document: default
---
Paper 2: There is specificity concerning the association between self report
scales and different sorts of real world variability.

The logic of this paper is that: mood variability has been associated with
mental health problems, although there are different sorts of mood
variability and it is not obvious whether there is any specificity to
these associations, we find specificity in terms of different scales and them map them onto general positive/negative affective dimensions.

# library 
```{r warning=FALSE,message=FALSE}
source(here::here("load_library.R"))
```

```{r warning=FALSE,message=FALSE}
theme_set(theme_classic()+
          theme(text = element_text(family = "Helvetica", size = 10)))
vmuColor <- "red"
noiseColor <- 'royalblue3'
muColor <- 'forestgreen'
```

# load and combine data
```{r warning=FALSE,message=FALSE}
rmarkdown::render("read_data.Rmd")
```

# Part 2: Relationship between EMA and baseline questionnaires
## 2.1 EMA summary statistics and baseline questionnaires (gist: poor differentiation between mean and se)

P.S. We used PA and NA separately due to differentiation in the literature and RDoc
```{r}
chart.Correlation(df_master %>% 
                    dplyr::select(TEPS_sum,HPS_sum,CESD_sum,STAI_SA_sum,STAI_TA_sum,
                           PA_mean,PA_se,NA_mean,NA_se))
```

## 2.2 EMA bayes params and baseline questionnaires
*Ask Mike here: how to justify using posminusneg vs. pos and neg separately?*

### When using the difference score (PA minus NA), we see that the noise of this 'net mood rating' is correlated with HPS; mu is correlated with TEPS and negative affectivity in the expected direction.

```{r}
chart.Correlation(df_master %>% 
                    dplyr::select(TEPS_sum,HPS_sum,CESD_sum, STAI_TA_sum,STAI_TA_sum,
                           mean5_vmu_pos,mean_mu_pos,mean_s_pos,
                           mean5_vmu_neg,mean_mu_neg,mean_s_neg))
```

### We would expect some differentiation between PA and NA parameters; TEPS should be correlated with PA variability., and depression/anxiety should be correlated with NA variability. Motivated by this differentiability, we will now examine these specific links.

```{r echo=FALSE}
ppcor::pcor(df_master %>% dplyr::select(HPS_sum,mean5_vmu_pos,TEPS_sum))
ppcor::pcor(df_master %>% dplyr::select(HPS_sum,mean_s_pos,TEPS_sum))
ppcor::pcor(df_master %>% dplyr::select(HPS_sum,mean5_vmu_neg,TEPS_sum))
ppcor::pcor(df_master %>% dplyr::select(HPS_sum,mean_s_neg,TEPS_sum))
```

### Here, we see that TEPS and HPS are differentially associated with the variability of EMA PA.
```{r fig.width= 12,fig.height= 8}
ggplot(df_master, aes(x = TEPS_sum, y = mean5_vmu_pos))+
  geom_point(size = 0.5)+
  geom_smooth(method = "lm", fill = vmuColor, color = vmuColor) +
  stat_poly_eq(use_label(c("R2","p")))+
  labs(title = "TEPS",
       y = "PA vmu",
       subtitle = "partial r = 0.156, p = .004")+
ggplot(df_master, aes(x = TEPS_sum, y = mean_s_pos))+
  geom_point(size = 0.5)+
  geom_smooth(method = "lm", fill = 'grey', color = 'grey') +
  stat_poly_eq(use_label(c("R2","p")))+
  labs(y = "PA noise",
       subtitle = "partial r = -0.028, p = .608")+
ggplot(df_master, aes(x = TEPS_sum, y = mean5_vmu_neg))+
  geom_point(size = 0.5)+
  geom_smooth(method = "lm", fill = 'grey', color = 'grey', linetype = "dashed") +
  stat_poly_eq(use_label(c("R2","p")))+
  labs(y = "NA vmu",
       subtitle = "partial r = -0.091, p = .093")+
ggplot(df_master, aes(x = TEPS_sum, y = mean_s_neg))+
  geom_point(size = 0.5)+
  geom_smooth(method = "lm", fill = 'grey', color = 'grey', linetype = "dashed") +
  stat_poly_eq(use_label(c("R2","p")))+
  labs(y = "NA noise",
       subtitle = "partial r = -0.109, p = .045") + 
ggplot(df_master, aes(x = HPS_sum, y = mean5_vmu_pos))+
  geom_point(size = 0.5)+
  geom_smooth(method = "lm", fill = 'grey', color = 'grey') +
  stat_poly_eq(use_label(c("R2","p")))+
  labs(title = "HPS",y = "PA vmu",
       subtitle = "partial r = 0.064, p = .240")+
ggplot(df_master, aes(x = HPS_sum, y = mean_s_pos))+
  geom_point(size = 0.5)+
  geom_smooth(method = "lm", fill = 'grey', color = 'grey') +
  stat_poly_eq(use_label(c("R2","p")))+
  labs(y = "PA noise",
       subtitle = "partial r = 0.092, p = .091")+
ggplot(df_master, aes(x = HPS_sum, y = mean5_vmu_neg))+
  geom_point(size = 0.5)+
  geom_smooth(method = "lm", color = vmuColor, fill = vmuColor, linetype = "dashed") +
  stat_poly_eq(use_label(c("R2","p")))+
  labs(y = "NA vmu",
       subtitle = "partial r = 0.118, p = .029")+
ggplot(df_master, aes(x = HPS_sum, y = mean_s_neg))+
  geom_point(size = 0.5)+
  geom_smooth(method = "lm", color = noiseColor, fill = noiseColor, linetype = "dashed") +
  stat_poly_eq(use_label(c("R2","p")))+
  labs(y = "NA noise",
       subtitle = "partial r = 0.298, p < .001")+
  plot_layout(nrow = 2)

```

## 2.3 factor analysis of all baseline questionnaires to capture positive and negative affectivity
```{r}
df_fa <- df_master %>% dplyr::select(HPS_sum,TEPS_ant_sum,TEPS_con_sum,CESD_sum, STAI_TA_sum,STAI_SA_sum)

ev <- eigen(cor(na.omit(df_fa))) # get eigenvalues
ap <- parallel(subject=nrow(df_fa),var=ncol(df_fa),rep=100,cent=.05)
nS <- nScree(x=ev$values, aparallel=ap$eigen$qevpea)
plotnScree(nS)# scree plot

psych::fa(df_fa, nfactors = 2,
          rotate = "varimax",
          scores = "regression")

df_master_ <- cbind(df_master, psych::fa(df_fa, nfactors = 2,
          rotate = "varimax",
          scores = "regression")$scores) %>% 
  rename(trait_NA = MR1,
         trait_PA= MR2)
```

### Similar to what we found in 2.2, trait PA (hedonia) is associated with higher PA volatility but not NA; trait NA is associated with higher NA but not variability.
```{r fig.width= 12,fig.height= 8}
ggplot(df_master_, aes(x = trait_NA, y = mean5_vmu_pos))+
  geom_point(size = 0.5)+
  geom_smooth(method = "lm", fill = 'grey', color = 'grey') +
  stat_poly_eq(use_label(c("R2","p")))+
  labs(title = "EMA variability and Trait NA",
       y = "PA vmu")+
ggplot(df_master_, aes(x = trait_NA, y = mean_s_pos))+
  geom_point(size = 0.5)+
  geom_smooth(method = "lm", fill = 'grey', color = 'grey') +
  stat_poly_eq(use_label(c("R2","p")))+
  labs(y = "PA noise")+
ggplot(df_master_, aes(x = trait_NA, y = mean5_vmu_neg))+
  geom_point(size = 0.5)+
  geom_smooth(method = "lm", color = vmuColor, fill = vmuColor, linetype = "dashed") +
  stat_poly_eq(use_label(c("R2","p")))+
  labs(y = "NA vmu")+
ggplot(df_master_, aes(x = trait_NA, y = mean_s_neg))+
  geom_point(size = 0.5)+
  geom_smooth(method = "lm", color = noiseColor, fill = noiseColor, linetype = "dashed") +
  stat_poly_eq(use_label(c("R2","p")))+
  labs(y = "NA noise")+

ggplot(df_master_, aes(x = trait_PA, y = mean5_vmu_pos))+
  geom_point(size = 0.5)+
  geom_smooth(method = "lm", color = vmuColor, fill = vmuColor) +
  stat_poly_eq(use_label(c("R2","p")))+
  labs(title = "EMA variability and Trait PA",y = "PA vmu")+
ggplot(df_master_, aes(x = trait_PA, y = mean_s_pos))+
  geom_point(size = 0.5)+
  geom_smooth(method = "lm", fill = 'grey', color = 'grey') +
  stat_poly_eq(use_label(c("R2","p")))+
  labs(y = "PA noise")+
ggplot(df_master_, aes(x = trait_PA, y = mean5_vmu_neg))+
  geom_point(size = 0.5)+
  geom_smooth(method = "lm", fill = 'grey', color = 'grey', linetype = "dashed") +
  stat_poly_eq(use_label(c("R2","p")))+
  labs(y = "NA vmu")+
ggplot(df_master_, aes(x = trait_PA, y = mean_s_neg))+
  geom_point(size = 0.5)+
  geom_smooth(method = "lm", fill = 'grey', color = 'grey', linetype = "dashed") +
  stat_poly_eq(use_label(c("R2","p")))+
  labs(y = "NA noise")+

  plot_layout(nrow = 2)
```

# Part 3 (SI): diurnal contributions to the EMA variability
```{r warning=FALSE,message=FALSE}
source(here::here("fit_diurnal_model.R"))
```

## 3.1 plot example diurnal fit
### PA: Across subjects, the quadratic term is negative and linear term is positive.

```{r}
lm_diurn_pa <- lmer(PA_sum_scaled ~ I(time_index^2) + time_index +(1|day_index/Prolific.Id),data=df_PANAS_forlm)

summary(lm_diurn_pa)

df_PANAS_forlm1 <- df_PANAS_forlm %>%
  filter(!is.na(PA_sum_scaled)) 
df_PANAS_forlm1$PA_pred_val = fitted(lm_diurn_pa)

ggplot(data=df_PANAS_forlm1)+
    theme_classic()+
    stat_summary(aes(x=time_index, y=PA_pred_val,group = Prolific.Id), 
                 geom = "line", alpha = 0.1)+
  stat_summary(aes(x=time_index, y=PA_pred_val,group = 1), 
                 geom = "pointrange", color = "red", size = 0.5)+
    labs(title = 'Diurnal Variation Model prediction - PA',
         y = 'predicted scaled PA', x = 'time of day')+
   scale_x_continuous(breaks = 1:6, labels = c("9-11AM","11AM-1PM","1-3PM","3-5PM","5-7PM","7-9PM"))
```
### NA: Across subjects, there is no significant diurnal effect.

```{r}
lm_diurn_na <- lmer(NA_sum_scaled ~ I(time_index^2) + time_index +(1|day_index/Prolific.Id),data=df_PANAS_forlm)

summary(lm_diurn_na)

df_PANAS_forlm2 <- df_PANAS_forlm %>%
  filter(!is.na(NA_sum_scaled)) 
df_PANAS_forlm2$NA_pred_val = fitted(lm_diurn_na)

ggplot(data=df_PANAS_forlm2)+
    theme_classic()+
    stat_summary(aes(x=time_index, y=NA_pred_val,group = Prolific.Id), 
                 geom = "line", alpha = 0.1)+
  stat_summary(aes(x=time_index, y=NA_pred_val,group = 1), 
                 geom = "pointrange", color = "red", size = 0.5)+
    labs(title = 'Diurnal Variation Model prediction - NA',
         y = 'predicted scaled NA', x = 'time of day')+
   scale_x_continuous(breaks = 1:6, labels = c("9-11AM","11AM-1PM","1-3PM","3-5PM","5-7PM","7-9PM"))
```
```{r}
df_lm_sum <- read_csv(paste(outdir, 'panas_lm_params.csv'))

df_master <- left_join(df_master, df_lm_sum %>% 
  dplyr::select(Prolific.Id,model,Intercept_Estimate:t_Estimate,R2c) %>% 
  pivot_wider(names_from = model, values_from = c(Intercept_Estimate:R2c)))


ggplot(df_master %>% 
         dplyr::select(`t^2_Estimate_PA`,`t^2_Estimate_NA`) %>% 
         rename(PosAff = `t^2_Estimate_PA`,
                NegAff = `t^2_Estimate_NA`) %>% 
         pivot_longer(PosAff:NegAff,
                      names_to = "Affect", values_to = "quad_term"), aes(x = Affect, y = quad_term))+
  geom_violin(aes(color = Affect))+
  geom_jitter(width = 0.3, size = 0.4)+
  stat_summary(aes(color = Affect),geom = "pointrange")+
  scale_color_brewer(palette = "Set1")+
  geom_hline(yintercept = 0, linetype = "dotted")

t.test(df_master$`t^2_Estimate_PA`, mu = 0)
t.test(df_master$`t^2_Estimate_NA`, mu = 0)

ggplot(df_master %>% 
         dplyr::select(`t_Estimate_PA`,`t_Estimate_NA`) %>% 
         rename(PosAff = `t_Estimate_PA`,
                NegAff = `t_Estimate_NA`) %>% 
         pivot_longer(PosAff:NegAff,
                      names_to = "Affect", values_to = "lin_term"), aes(x = Affect, y = lin_term))+
  geom_violin(aes(color = Affect))+
  geom_jitter(width = 0.3,size=0.4)+
  stat_summary(aes(color = Affect),geom = "pointrange")+
  scale_color_brewer(palette = "Set1")+
  geom_hline(yintercept = 0, linetype = "dotted")

t.test(df_master$`t_Estimate_PA`, mu = 0)
t.test(df_master$`t_Estimate_NA`, mu = 0)
```

## 3.2 demonstrate that diurnal variation of PA contributes to noise, but not volatility

```{r fig.width= 12,fig.height= 8}
ggplot(df_master, aes(x = mean5_vmu_pos, y = `t^2_Estimate_PA`))+
  geom_point(size = 0.5)+
  geom_smooth(method = "lm", color = vmuColor, fill = vmuColor) +
  geom_hline(yintercept = 0, linetype = "dashed")+
  stat_poly_eq(use_label(c("R2","p")))+
  labs(title = "Quadratic term (negative)",
       x = "log PA volatility",
       y = "quadratic term")+
ggplot(df_master, aes(x = mean_s_pos, y = `t^2_Estimate_PA`))+
  geom_point(size = 0.5)+
  geom_smooth(method = "lm", color = noiseColor, fill = noiseColor) +
  geom_hline(yintercept = 0, linetype = "dashed")+
  stat_poly_eq(use_label(c("R2","p")))+
  labs(x = "log PA noise",
       y = "quadratic term")+
ggplot(df_master, aes(x = mean_mu_pos, y = `t^2_Estimate_PA`))+
  geom_point(size = 0.5)+
  geom_smooth(method = "lm", color = "grey", fill = "grey") +
  geom_hline(yintercept = 0, linetype = "dashed")+
  stat_poly_eq(use_label(c("R2","p")))+
  labs(x = "log PA mu",
       y = "quadratic term")+

ggplot(df_master, aes(x = mean5_vmu_pos, y = `t_Estimate_PA`))+
  geom_point(size = 0.5)+
  geom_smooth(method = "lm", color = vmuColor, fill = vmuColor) +
  geom_hline(yintercept = 0, linetype = "dashed")+
  stat_poly_eq(use_label(c("R2","p")))+
  labs(title = "Linear term (positive)",
       x = "log PA volatility",
       y = "linear term")+
ggplot(df_master, aes(x = mean_s_pos, y = `t_Estimate_PA`))+
  geom_point(size = 0.5)+
  geom_smooth(method = "lm", color = noiseColor, fill = noiseColor) +
  geom_hline(yintercept = 0, linetype = "dashed")+
  stat_poly_eq(use_label(c("R2","p")))+
  labs(x = "log PA noise",
       y = "linear term")+
ggplot(df_master, aes(x = mean_mu_pos, y = `t_Estimate_PA`))+
  geom_point(size = 0.5)+
  geom_smooth(method = "lm", color = "grey", fill = "grey") +
  geom_hline(yintercept = 0, linetype = "dashed")+
  stat_poly_eq(use_label(c("R2","p")))+
  labs(x = "log PA mu",
       y = "linear term")
```
```{r}
summary(lm(`t^2_Estimate_PA`~ mean5_vmu_pos + mean_s_pos,df_master))
summary(lm(`t_Estimate_PA`~ mean5_vmu_pos + mean_s_pos,df_master))
```

