---
title: "moodVariability"
author: "Ryan Yan"
date: "2024-01-16"
output:
  html_document:
    df_print: paged
  html_notebook:
    code_folding: hide
  pdf_document: default
---
Paper 2: There is specificity concerning the association between self report
scales and different sorts of real world variability.

The logic of this paper is that: mood variability has been associated with
mental health problems, although there are different sorts of mood
variability and it is not obvious whether there is any specificity to
these associations, we find specificity in terms of different scales and them map them onto general positive/negative affective dimensions.

# library 
```{r warning=FALSE,message=FALSE}
rm(list = ls())
source(here::here("../scripts/load_library.R"))
```

```{r warning=FALSE,message=FALSE}
theme_set(theme_classic()+
          theme(text = element_text(family = "Helvetica", size = 10)))
vmuColor <- "red"
noiseColor <- 'royalblue3'
muColor <- 'forestgreen'
```

# load and combine data
```{r warning=FALSE,message=FALSE}
rmarkdown::render("read_data_survey_ema.Rmd")
```

```{r warning=FALSE,message=FALSE}
source(here::here("../scripts/fit_diurnal_model.R"))

df_lm_sum <- read_csv(paste(outdir, 'panas_lm_params.csv'))

df_master_ema <- left_join(df_master_ema, df_lm_sum %>% 
  dplyr::select(Prolific.Id,model,Intercept_Estimate:t_Estimate,R2c) %>% 
  pivot_wider(names_from = model, values_from = c(Intercept_Estimate:R2c)))

source(here::here("AR.R"))#autoregressive model functions

#join autoregressive PANAS
str <- c("PA_sum", "NA_sum","PAminusNA_sum") # your strings for naming the variables
result <- AR_PANAS(df_PANAS, str)
df_AR_PANAS <- data.frame(cbind(result$S,result$ui))
names(df_AR_PANAS) <- c(result$names,"Prolific.Id")

# 
# str = c("day1_block1","day1_block2","day2_block1","day2_block2")
# result <- AR_task(df_mood_AR, str)
# df_AR_task <- data.frame(cbind(result$S,result$ui))
# names(df_AR_task) <- c(result$names,"Prolific.Id")

df_master_ema <- left_join(df_master_ema,df_AR_PANAS,by = "Prolific.Id")%>% 
  mutate(AR_PA_sum = as.numeric(AR_PA_sum),
         AR_NA_sum = as.numeric(AR_NA_sum))

```
# demographics
```{r}
#sex
sum(is.na(demo_info_ema$Sex))
table(demo_info_ema$Sex)
table(demo_info_ema$Sex)/343*100

#age
sum(is.na(demo_info_ema$age))
table(demo_info_ema$age)
mean(demo_info_ema$age, na.rm = T)
sd(demo_info_ema$age, na.rm = T)
min(demo_info_ema$age, na.rm = T)
max(demo_info_ema$age, na.rm = T)

#country

table(demo_info_ema$`Country of Birth`)
table(demo_info_ema$`First Language`)


#questionnaires
nrow(df_master_ema)
summary(df_master_ema$CESD_sum)
sd(df_master_ema$CESD_sum)

summary(df_master_ema$TEPS_sum)
sd(df_master_ema$TEPS_sum)

summary(df_master_ema$HPS_sum)
sd(df_master_ema$HPS_sum)

summary(df_master_ema$STAI_SA_sum)
sd(df_master_ema$STAI_SA_sum)

summary(df_master_ema$STAI_TA_sum)
sd(df_master_ema$STAI_TA_sum)

#missing panas
table(df_PANAS_availability$n_panas)
mean(df_PANAS_availability$n_panas)
sd(df_PANAS_availability$n_panas)
```

## 1.1 EMA summary statistics and baseline questionnaires

### motivating the use of the model
P.S. We used PA and NA separately due to differentiation in the literature and RDoc

HPS correlated with higher PA and NA; TEPS correlated with higher PA and lower NA; CESD/STAI correlated with higher NA and lower PA

HPS correlated with every variability measure; TEPS correlated with PA variability; CESD/STAI correlated with NA variability 

```{r}
chart.Correlation(df_master_ema %>% 
                    dplyr::select(TEPS_sum,HPS_sum,CESD_sum,
                                  PA_mean,NA_mean))

chart.Correlation(df_master_ema %>% 
                    dplyr::select(TEPS_sum,HPS_sum,CESD_sum,
                                  PA_se,PA_mssd,NA_se,NA_mssd))
```


```{r}
df_corr <- df_master_ema %>% 
  ungroup() %>% 
  dplyr::select(TEPS_sum,HPS_sum,CESD_sum,#STAI_SA_sum,STAI_TA_sum,#trait_NA,
                           PA_mean,AR_PA_sum,PA_se,PA_mssd,NA_mean,AR_NA_sum,NA_se, NA_mssd) %>% 
  rename(TEPS = TEPS_sum, HPS = HPS_sum, CESD = CESD_sum) 

chart.Correlation(df_corr)

corm <- cor(df_corr,
            method = "pearson", use = "complete.obs")

p.mat <- cor_pmat(df_corr,
            method = "pearson", use = "complete.obs")

knitr::kable(corm, digits = 3)
knitr::kable(p.mat, digits = 3)

ggcorrplot::ggcorrplot(corm, 
           p.mat = p.mat, lab = T, insig = "blank", type = "lower",
           colors = c("skyblue", "white", "orange"))

ggsave("./figures/figure_corr.png",width = 8, height = 6)
```


Here, we see that the computational model reduced correlations among the variability measures
```{r}
chart.Correlation(df_master_ema %>% 
                    dplyr::select(PA_se,PA_mssd,AR_PA_sum,NA_se,NA_mssd,AR_NA_sum))

chart.Correlation(df_master_ema %>% 
                    dplyr::select(mean5_vmu_pos,mean5_s_pos,mean5_vmu_neg,mean5_s_neg))
```


## 1.2 EMA bayes params and baseline questionnaires

### Here, we see that TEPS and HPS are differentially associated with the variability of EMA PA.
```{r}
df_corr2 <- df_master_ema %>% 
  dplyr::select(TEPS_sum,CESD_sum,HPS_sum,#STAI_SA_sum,STAI_TA_sum,#trait_NA,
                            mean5_vmu_pos, mean5_s_pos, mean5_vmu_neg, mean5_s_neg) %>% 
  rename(TEPS = TEPS_sum, HPS = HPS_sum, CESD = CESD_sum,
         'PA volatility' = mean5_vmu_pos,
         'NA volatility' = mean5_vmu_neg,
         'PA noise' = mean5_s_pos,
         'NA noise' = mean5_s_neg,)

corm2 <- cor(df_corr2,
            method = "pearson", use = "complete.obs")

p.mat2 <- cor_pmat(df_corr2,
            method = "pearson", use = "complete.obs")

knitr::kable(corm2, digits = 3)
knitr::kable(p.mat2, digits = 3)

ggcorrplot::ggcorrplot(corm2, 
           p.mat = p.mat2, lab = T, insig = "blank", type = "lower",
           colors = c("skyblue", "white", "orange"))

ggsave("./figures/figure_corr.png",width = 8, height = 5)
```

```{r}
l1 <- lm(TEPS_sum ~ mean5_vmu_pos + mean5_s_pos + mean5_vmu_neg + mean5_s_neg,df_master_ema)
l1b <- lm(scale(TEPS_sum) ~ scale(mean5_vmu_pos) + scale(mean5_s_pos) + scale(mean5_vmu_neg) + scale(mean5_s_neg),df_master_ema)
summary(l1b)
summary(lm(scale(TEPS_ant_sum) ~ scale(mean5_vmu_pos) + scale(mean5_s_pos) + scale(mean5_vmu_neg) + scale(mean5_s_neg),df_master_ema))
summary(lm(scale(TEPS_con_sum) ~ scale(mean5_vmu_pos) + scale(mean5_s_pos) + scale(mean5_vmu_neg) + scale(mean5_s_neg),df_master_ema))

l2 <- lm(HPS_sum ~ mean5_vmu_pos + mean5_s_pos + mean5_vmu_neg + mean5_s_neg,df_master_ema)
l2b <- lm(scale(HPS_sum) ~ scale(mean5_vmu_pos) + scale(mean5_s_pos) + scale(mean5_vmu_neg) + scale(mean5_s_neg),df_master_ema)
summary(l2b)

summary(lm(scale(HPS_sum) ~ scale(mean5_vmu_pos) + scale(mean5_s_pos),df_master_ema))
summary(lm(scale(HPS_sum) ~ scale(mean5_vmu_pos),df_master_ema))
summary(lm(scale(HPS_sum) ~ scale(mean5_s_pos),df_master_ema))
summary(lm(scale(HPS_sum) ~ scale(mean5_vmu_neg) + scale(mean5_s_neg),df_master_ema))

l3 <- lm(CESD_sum ~ mean5_vmu_pos + mean5_s_pos + mean5_vmu_neg + mean5_s_neg,df_master_ema)
l3b <- lm(scale(CESD_sum) ~ scale(mean5_vmu_pos) + scale(mean5_s_pos) + scale(mean5_vmu_neg) + scale(mean5_s_neg),df_master_ema)
summary(l3b)

summary(lm(mean5_s_neg ~ CESD_sum + HPS_sum,df_master_ema))

(plot_model(l1, type = "pred", terms = "mean5_vmu_pos", show.data = T,
           dot.size = 0.5, color = vmuColor)+
  labs(x = "PA volatility", y = "TEPS score",title = "",
       subtitle = paste0("r = ", round(summary(l1b)$coefficients[2,1],2),
                      ", p = ", round(summary(l1b)$coefficients[2,4],3))))+
(plot_model(l1, type = "pred", terms = "mean5_s_pos", show.data = T,
           dot.size = 0.5, color = noiseColor, alpha = 0.1)+
  labs(x = "PA noise", y = "TEPS score",title = "",
       subtitle = paste0("r = ", round(summary(l1b)$coefficients[3,1],2),
                      ", p = ", round(summary(l1b)$coefficients[3,4],3))))+
plot_model(l1, type = "pred", terms = "mean5_vmu_neg", show.data = T,
           dot.size = 0.5, color = vmuColor)+
  labs(x = "NA volatility", y = "TEPS score",title = "",
       subtitle = paste0("r = ", round(summary(l1b)$coefficients[4,1],2),
                      ", p = ", round(summary(l1b)$coefficients[4,4],3)))+
plot_model(l1, type = "pred", terms = "mean5_s_neg", show.data = T,
           dot.size = 0.5, color = noiseColor)+
  labs(x = "NA noise", y = "TEPS score",title = "",
       subtitle = paste0("r = ", round(summary(l1b)$coefficients[5,1],2),
                      ", p = ", round(summary(l1b)$coefficients[5,4],3)))+
  
plot_model(l2, type = "pred", terms = "mean5_vmu_pos", show.data = T,
           dot.size = 0.5, color = vmuColor)+
  labs(x = "PA volatility", y = "HPS score",title = "",
       subtitle = paste0("r = ", round(summary(l2b)$coefficients[2,1],2),
                      ", p = ", round(summary(l2b)$coefficients[2,4],3)))+
plot_model(l2, type = "pred", terms = "mean5_s_pos", show.data = T,
           dot.size = 0.5, color = noiseColor)+
  labs(x = "PA noise", y = "HPS score",title = "",
       subtitle = paste0("r = ", round(summary(l2b)$coefficients[3,1],2),
                      ", p = ", round(summary(l2b)$coefficients[3,4],3)))+
plot_model(l2, type = "pred", terms = "mean5_vmu_neg", show.data = T,
           dot.size = 0.5, color = vmuColor)+
  labs(x = "NA volatility", y = "HPS score",title = "",
       subtitle = paste0("r = ", round(summary(l2b)$coefficients[4,1],2),
                      ", p = ", round(summary(l2b)$coefficients[4,4],3)))+
plot_model(l2, type = "pred", terms = "mean5_s_neg", show.data = T,
           dot.size = 0.5, color = noiseColor)+
  labs(x = "NA noise", y = "HPS score",title = "",
       subtitle = paste0("r = ", round(summary(l2b)$coefficients[5,1],2),
                      ", p = ", round(summary(l2b)$coefficients[5,4],3)))+
  
plot_model(l3, type = "pred", terms = "mean5_vmu_pos", show.data = T,
           dot.size = 0.5, color = vmuColor)+
  labs(x = "PA volatility", y = "CESD score",title = "",
       subtitle = paste0("r = ", round(summary(l3b)$coefficients[2,1],2),
                      ", p = ", round(summary(l3b)$coefficients[2,4],3)))+
plot_model(l3, type = "pred", terms = "mean5_s_pos", show.data = T,
           dot.size = 0.5, color = noiseColor)+
  labs(x = "PA noise", y = "CESD score",title = "",
       subtitle = paste0("r = ", round(summary(l1b)$coefficients[3,1],2),
                      ", p = ", round(summary(l1b)$coefficients[3,4],3)))+
plot_model(l3, type = "pred", terms = "mean5_vmu_neg", show.data = T,
           dot.size = 0.5, color = vmuColor)+
  labs(x = "NA volatility", y = "CESD score",title = "",
       subtitle = paste0("r = ", round(summary(l3b)$coefficients[4,1],2),
                      ", p = ", round(summary(l3b)$coefficients[4,4],3)))+
plot_model(l3, type = "pred", terms = "mean5_s_neg", show.data = T,
           dot.size = 0.5, color = noiseColor)+
  labs(x = "NA noise", y = "CESD score",title = "",
       subtitle = paste0("r = ", round(summary(l3b)$coefficients[5,1],2),
                      ", p = ", round(summary(l3b)$coefficients[5,4],3)))+
  plot_layout(nrow = 3)
ggsave("./figures/figure_hpsteps1.png",width = 7, height = 7)
```

```{r}
bars <- Reduce(rbind,
       list(as.data.frame(summary(l1b)$coefficients) %>% 
              mutate(reg = "TEPS score"),
            as.data.frame(summary(l2b)$coefficients) %>% 
              mutate(reg = "HPS score"),
            as.data.frame(summary(l3b)$coefficients) %>% 
              mutate(reg = "CESD score"))) %>% 
  rownames_to_column() %>% 
  rename(variable = rowname,
         se = `Std. Error`,
         p_val = `Pr(>|t|)`) %>% 
  mutate(sig = ifelse(p_val < .001, "***",
                      ifelse(p_val < .01, "**",
                             ifelse(p_val < .05,"*",
                                    ifelse(p_val < .1,"†","ns")))))

bars$valence[grepl("pos",bars$variable)] <- "Positive"
bars$valence[grepl("neg",bars$variable)] <- "Negative"

bars$variable[grepl("vmu",bars$variable)] <- "volatility"
bars$variable[grepl("_s_",bars$variable)] <- "noise"

bars <- bars %>% 
  rowwise() %>% 
  mutate(alpha = ifelse(grepl("\\*\\*", sig), "1",
                        "0"))

p1a <-  ggplot(bars %>% 
         filter(!grepl("Intercept", variable),
                reg == "TEPS score") %>% 
         mutate(variable = factor(variable, levels = c("volatility", "noise")),
                valence = factor(valence, levels = c("Positive", "Negative")),
                reg = factor(reg, levels = c("TEPS score", "HPS score", "CESD score")))) +
  geom_col(aes(x = valence, y = Estimate, group = variable, fill = variable, alpha = alpha),
           width = 0.4, position = position_dodge(width = 0.5)) +
  geom_errorbar(aes(x = valence, ymin = Estimate - se, ymax = Estimate + se, group = variable),
                width = 0.1, position = position_dodge(width = 0.5)) +
  geom_text(aes(x = valence, y = (Estimate + (Estimate) / abs(Estimate) * se  + (Estimate) / abs(Estimate) * 0.1), 
                label = sig, group = variable), 
            position = position_dodge(width = 0.5)) +
  scale_alpha_manual(values = c("1" = 1, "0" = 0.5), guide = "none") +
  scale_fill_manual(values = c(vmuColor, noiseColor)) +
  labs(y = "Standardized \u03b2",
       title = "TEPS score ~ ESM variability",
       x = "")+
    ylim(-0.3,0.5)+
  theme(legend.position = "none")
  
p1b <-  ggplot(bars %>% 
         filter(!grepl("Intercept", variable),
                reg == "HPS score") %>% 
         mutate(variable = factor(variable, levels = c("volatility", "noise")),
                valence = factor(valence, levels = c("Positive", "Negative")),
                reg = factor(reg, levels = c("TEPS score", "HPS score", "CESD score")))) +
  geom_col(aes(x = valence, y = Estimate, group = variable, fill = variable, alpha = alpha),
           width = 0.4, position = position_dodge(width = 0.5)) +
  geom_errorbar(aes(x = valence, ymin = Estimate - se, ymax = Estimate + se, group = variable),
                width = 0.1, position = position_dodge(width = 0.5)) +
  geom_text(aes(x = valence, y = (Estimate + (Estimate) / abs(Estimate) * se  + (Estimate) / abs(Estimate) * 0.1), 
                label = sig, group = variable), 
            position = position_dodge(width = 0.5)) +
  scale_alpha_manual(values = c("1" = 1, "0" = 0.5), guide = "none") +
  scale_fill_manual(values = c(vmuColor, noiseColor)) +
  labs(y = "Standardized \u03b2",
       title = "HPS score ~ ESM variability",
       x = "")+
    ylim(-0.3,0.5)+
  theme(legend.position = "none")
  
p1c <-ggplot(bars %>% 
         filter(!grepl("Intercept", variable),
                reg == "CESD score") %>% 
         mutate(variable = factor(variable, levels = c("volatility", "noise")),
                valence = factor(valence, levels = c("Positive", "Negative")),
                reg = factor(reg, levels = c("TEPS score", "HPS score", "CESD score")))) +
  geom_col(aes(x = valence, y = Estimate, group = variable, fill = variable, alpha = alpha),
           width = 0.4, position = position_dodge(width = 0.5)) +
  geom_errorbar(aes(x = valence, ymin = Estimate - se, ymax = Estimate + se, group = variable),
                width = 0.1, position = position_dodge(width = 0.5)) +
  geom_text(aes(x = valence, y = (Estimate + (Estimate) / abs(Estimate) * se  + (Estimate) / abs(Estimate) * 0.1), 
                label = sig, group = variable), 
            position = position_dodge(width = 0.5)) +
  scale_alpha_manual(values = c("1" = 1, "0" = 0.5), guide = "none") +
  scale_fill_manual(values = c(vmuColor, noiseColor)) +
  labs(y = "Standardized \u03b2",
       title = "CESD score ~ ESM variability",
       x = "")+
    ylim(-0.3,0.5)+
  theme(legend.position = "bottom")


```

```{r}
l1c <- lm(scale(TEPS_sum) ~ scale(mean_mu_pos) + scale(mean_mu_neg),df_master_ema)

l2c <- lm(scale(HPS_sum) ~ scale(mean_mu_pos) + scale(mean_mu_neg),df_master_ema)

l3c <- lm(scale(CESD_sum) ~ scale(mean_mu_pos) + scale(mean_mu_neg),df_master_ema)

bars2 <- Reduce(rbind,
       list(as.data.frame(summary(l1c)$coefficients) %>% 
              mutate(reg = "TEPS score"),
            as.data.frame(summary(l2c)$coefficients) %>% 
              mutate(reg = "HPS score"),
            as.data.frame(summary(l3c)$coefficients) %>% 
              mutate(reg = "CESD score"))) %>% 
  rownames_to_column() %>% 
  rename(variable = rowname,
         se = `Std. Error`,
         p_val = `Pr(>|t|)`) %>% 
  mutate(sig = ifelse(p_val < .001, "***",
                      ifelse(p_val < .01, "**",
                             ifelse(p_val < .05,"*",
                                    ifelse(p_val < .1,"†","ns")))))

bars2$valence[grepl("pos",bars2$variable)] <- "Positive"
bars2$valence[grepl("neg",bars2$variable)] <- "Negative"

bars2$variable[grepl("mu",bars2$variable)] <- "mean"

bars2 <- bars2 %>% 
  rowwise() %>% 
  mutate(alpha = ifelse(grepl("\\*\\*", sig), "1","0"))

p2 <- ggplot(bars2 %>% 
         filter(!grepl("Intercept", variable)) %>% 
         mutate(variable = factor(variable, levels = c("volatility", "noise")),
                valence = factor(valence, levels = c("Positive", "Negative")),
                reg = factor(reg, levels = c("TEPS score", "HPS score", "CESD score")))) +
  geom_col(aes(x = valence, y = Estimate, group = valence, fill = valence, alpha = alpha),
           width = 0.4, position = position_dodge(width = 0.5)) +
  geom_errorbar(aes(x = valence, ymin = Estimate - se, ymax = Estimate + se, group = valence),
                width = 0.1, position = position_dodge(width = 0.5)) +
  geom_text(aes(x = valence, y = (Estimate + (Estimate) / abs(Estimate) * se  + (Estimate) / abs(Estimate) * 0.1), 
                label = sig, group = valence), 
            position = position_dodge(width = 0.5)) +
  scale_alpha_manual(values = c("1" = 1, "0" = 0.5), guide = "none") +
  scale_fill_manual(values = c('orange', 'skyblue')) +
  labs(y = "Standardized \u03b2",
       title = "self-reports ~ ESM mean",
       x = "")+
  theme(legend.position = "none")+
  facet_wrap(~reg,nrow = 3)+
  ylim(-0.5,0.7)

```

<!-- ```{r} -->
<!-- design <- " -->
<!-- 11 -->
<!-- 25  -->
<!-- 35  -->
<!-- 45 -->
<!-- " -->

<!-- png("figures/temp.png", width = 533, height = 373) -->
<!-- corrplot::corrplot(as.matrix(corm2[1:3,4:7]),p.mat = p.mat2[1:3,4:7], -->
<!--                    tl.col = "black",method = "square",cl.align.text = "r",addCoef.col = T, -->
<!--                   tl.srt = 0, tl.offset = 5,win.asp = 0.7) #this is not a ggplot object  -->
<!-- dev.off() -->

<!-- p0<-magick::image_read("figures/temp.png") -->

<!-- p0_raster <- as.raster(p0) -->

<!-- p0<- cowplot::ggdraw() + -->
<!--   cowplot::draw_image(p0_raster, scale = 1) -->

<!-- p0+ -->
<!-- p1a+p1b+p1c+p2+ -->
<!--   plot_layout(design = design, -->
<!--               widths = c(2,1), -->
<!--               height = c(3,1,1,1))+ -->
<!--   plot_annotation(tag_levels = "A") -->
<!-- ggsave("./figures/figure_hpsteps.png",width = 7, height = 10) -->
<!-- ``` -->


```{r}
design <- "
14
24 
34
"

p1a+p1b+p1c+p2+
  plot_layout(design = design,
              widths = c(2,1))+
  plot_annotation(tag_levels = "A")
ggsave("./figures/figure_hpsteps.png",width = 7, height = 7)
```
#### the TEPS thing 
```{r}
ppcor::pcor(df_master_ema %>% dplyr::select(TEPS_sum,PA_se,PA_mean,mean5_vmu_pos,mean5_s_pos) %>% 
              drop_na())
```

#### why the divergent results for HPS?

```{r}
chart.Correlation(df_master_ema %>% 
                    dplyr::select(PA_mean,NA_mean
                                  ,PA_se,PA_mssd,NA_se,NA_mssd))

chart.Correlation(df_master_ema %>% 
                    dplyr::select(mean_mu_pos,mean5_vmu_pos,mean5_s_pos))

chart.Correlation(df_master_ema %>% 
                    dplyr::select(PA_se,PA_mssd,mean5_vmu_pos,mean5_s_pos,HPS_sum))

cor(df_master_ema%>% 
                    dplyr::select(PA_mean,PA_se,PA_mssd,mean5_vmu_pos,mean5_s_pos),
            method = "pearson", use = "complete.obs")

cor_pmat(df_master_ema%>% 
                    dplyr::select(PA_mean,PA_se,PA_mssd,mean5_vmu_pos,mean5_s_pos),
            method = "pearson", use = "complete.obs")

ppcor::pcor(df_master_ema %>% dplyr::select(HPS_sum,PA_se,PA_mean))

ppcor::pcor(df_master_ema %>% dplyr::select(HPS_sum,PA_mssd,PA_mean))
```


```{r echo=FALSE}
ppcor::pcor(df_master_ema %>% dplyr::select(HPS_sum,mean_mu_pos,TEPS_sum) %>% drop_na())
ppcor::pcor(df_master_ema %>% dplyr::select(HPS_sum,mean5_vmu_pos,TEPS_sum) %>% drop_na())
ppcor::pcor(df_master_ema %>% dplyr::select(HPS_sum,mean_s_pos,TEPS_sum) %>% drop_na())
ppcor::pcor(df_master_ema %>% dplyr::select(HPS_sum,mean_mu_neg,TEPS_sum) %>% drop_na())
ppcor::pcor(df_master_ema %>% dplyr::select(HPS_sum,mean5_vmu_neg,TEPS_sum) %>% drop_na())
ppcor::pcor(df_master_ema %>% dplyr::select(HPS_sum,mean_s_neg,TEPS_sum) %>% drop_na())
```


```{r}
ppcor::pcor(df_master_ema %>% dplyr::select(HPS_sum,TEPS_sum,CESD_sum,STAI_SA_sum,STAI_TA_sum,PA_mean) %>% drop_na())
ppcor::pcor(df_master_ema %>% dplyr::select(HPS_sum,TEPS_sum,CESD_sum,STAI_SA_sum,STAI_TA_sum,PA_se) %>% drop_na())
ppcor::pcor(df_master_ema %>% dplyr::select(HPS_sum,TEPS_sum,CESD_sum,STAI_SA_sum,STAI_TA_sum,NA_mean) %>% drop_na())
ppcor::pcor(df_master_ema %>% dplyr::select(HPS_sum,TEPS_sum,CESD_sum,STAI_SA_sum,STAI_TA_sum,NA_se) %>% drop_na())
```


### Similar to what we found in 2.2, trait NA is associated with higher NA but not variability.
```{r echo=FALSE}
c1 <- ppcor::pcor(df_master_ema %>% dplyr::select(HPS_sum,TEPS_sum,CESD_sum,STAI_SA_sum,STAI_TA_sum,mean_mu_pos) %>% 
                    drop_na())
c2 <- ppcor::pcor(df_master_ema %>% dplyr::select(HPS_sum,TEPS_sum,CESD_sum,STAI_SA_sum,STAI_TA_sum,mean5_vmu_pos) %>% 
                    drop_na())
c3 <- ppcor::pcor(df_master_ema %>% dplyr::select(HPS_sum,TEPS_sum,CESD_sum,STAI_SA_sum,STAI_TA_sum,mean_s_pos) %>% 
                    drop_na())
c4 <- ppcor::pcor(df_master_ema %>% dplyr::select(HPS_sum,TEPS_sum,CESD_sum,STAI_SA_sum,STAI_TA_sum,mean_mu_neg) %>% 
                    drop_na())
c5 <- ppcor::pcor(df_master_ema %>% dplyr::select(HPS_sum,TEPS_sum,CESD_sum,STAI_SA_sum,STAI_TA_sum,mean5_vmu_neg) %>% 
                    drop_na())
c6 <- ppcor::pcor(df_master_ema %>% dplyr::select(HPS_sum,TEPS_sum,CESD_sum,STAI_SA_sum,STAI_TA_sum,mean_s_neg) %>% 
                    drop_na())
```

```{r }
ggplot(df_master_ema, aes(x = TEPS_sum, y = mean_mu_pos))+
  geom_point(size = 0.5)+
  geom_smooth(method = "lm", fill = muColor, color = muColor) +
  stat_poly_eq(use_label(c("R2","p")))+
  labs(title = "TEPS",
       x = "PA mu",
       y = "TEPS total",
       subtitle = paste0("partial r = ", round(c1$estimate[2,4],2),", p = ",round(c4$p.value[2,4],2)))+

ggplot(df_master_ema, aes(x = TEPS_sum, y = mean_mu_neg))+
  geom_point(size = 0.5)+
  geom_smooth(method = "lm", fill = muColor, color = muColor, linetype = "dashed", alpha = 0.1) +
  stat_poly_eq(use_label(c("R2","p")))+
  labs(x = "NA mu",
       y = "TEPS total",
        subtitle = paste0("partial r = ", round(c4$estimate[2,4],2),", p = .114"))+

ggplot(df_master_ema, aes(x = HPS_sum, y = mean_mu_pos))+
  geom_point(size = 0.5)+
  geom_smooth(method = "lm", fill = muColor, color = muColor) +
  stat_poly_eq(use_label(c("R2","p")))+
  labs(title = "HPS",x = "PA mu",
       y = "HPS total",
       subtitle = paste0("partial r = ", round(c1$estimate[1,4],2),", p < .001"))+

ggplot(df_master_ema, aes(x = HPS_sum, y = mean_mu_neg))+
  geom_point(size = 0.5)+
  geom_smooth(method = "lm", fill = muColor, color = muColor, alpha = 0.1, linetype = "dashed",) +
  stat_poly_eq(use_label(c("R2","p")))+
  labs(x = "NA mu",
       y = "HPS total",
        subtitle = paste0("partial r = ", round(c4$estimate[1,4],2),", p < .001"))+

ggplot(df_master_ema, aes(y = CESD_sum, x = mean_mu_pos))+
  geom_point(size = 0.5)+
  geom_smooth(method = "lm", fill = muColor, color = muColor) +
  stat_poly_eq(use_label(c("R2","p")))+
  labs(title = "Trait NA",
       x = "PA mu",
       y = "CESD",
       subtitle = paste0("partial r = ", round(c1$estimate[3,4],2),", p < .001"))+

ggplot(df_master_ema, aes(y = CESD_sum, x = mean_mu_neg))+
  geom_point(size = 0.5)+
  geom_smooth(method = "lm", fill = muColor, color = muColor, linetype = "dashed", alpha = 0.1) +
  stat_poly_eq(use_label(c("R2","p")))+
  labs(x = "NA mu",
       y = "CESD",
       subtitle = paste0("partial r = ", round(c4$estimate[3,4],2),", p < .001"))+

  plot_layout(nrow = 1)

ggsave("./figures/figure_hpsteps2.png",width = 12, height = 3)
```
```{r fig.width= 12,fig.height= 8}
ggplot(df_master_ema, aes(x = TEPS_sum, y = mean5_vmu_pos))+
  geom_point(size = 0.5)+
  geom_smooth(method = "lm", fill = vmuColor, color = vmuColor) +
  stat_poly_eq(use_label(c("R2","p")))+
  labs(x = "PA volatility",
       y = "TEPS total",
       title = "TEPS",
       subtitle = paste0("partial r = ", round(c2$estimate[2,4],2),", p = .003"))+
ggplot(df_master_ema, aes(x = TEPS_sum, y = mean_s_pos))+
  geom_point(size = 0.5)+
  geom_smooth(method = "lm", fill = 'grey', color = 'grey') +
  stat_poly_eq(use_label(c("R2","p")))+
  labs(x = "PA noise",
       y = "TEPS total",
       subtitle = paste0("partial r = ", round(c3$estimate[2,4],2),", p = .725"))+
ggplot(df_master_ema, aes(x = TEPS_sum, y = mean5_vmu_neg))+
  geom_point(size = 0.5)+
  geom_smooth(method = "lm", fill = 'grey', color = 'grey', linetype = "dashed", alpha = 0.1) +
  stat_poly_eq(use_label(c("R2","p")))+
  labs(x = "NA volatility",
       y = "TEPS total",
       subtitle = paste0("partial r = ", round(c5$estimate[2,4],2),", p = .732"))+
ggplot(df_master_ema, aes(x = TEPS_sum, y = mean_s_neg))+
  geom_point(size = 0.5)+
  geom_smooth(method = "lm", fill = 'grey', color = 'grey', linetype = "dashed", alpha = 0.1) +
  stat_poly_eq(use_label(c("R2","p")))+
  labs(x = "NA noise",
       y = "TEPS total",
       subtitle = paste0("partial r = ", round(c6$estimate[2,4],2),", p = .717"))+
ggplot(df_master_ema, aes(x = HPS_sum, y = mean5_vmu_pos))+
  geom_point(size = 0.5)+
  geom_smooth(method = "lm", fill = 'grey', color = 'grey') +
  stat_poly_eq(use_label(c("R2","p")))+
  labs(x = "PA volatility",
       title = "HPS",
       y = "HPS total",
subtitle = paste0("partial r = ", round(c2$estimate[1,4],2),", p = .354"))+
ggplot(df_master_ema, aes(x = HPS_sum, y = mean_s_pos))+
  geom_point(size = 0.5)+
  geom_smooth(method = "lm", fill = 'grey', color = 'grey') +
  stat_poly_eq(use_label(c("R2","p")))+
  labs(x = "PA noise",
       y = "HPS total",
subtitle = paste0("partial r = ", round(c3$estimate[1,4],2),", p = .133"))+
ggplot(df_master_ema, aes(x = HPS_sum, y = mean5_vmu_neg))+
  geom_point(size = 0.5)+
  geom_smooth(method = "lm", color = 'grey', fill = 'grey', linetype = "dashed", alpha = 0.1) +
  stat_poly_eq(use_label(c("R2","p")))+
  labs(x = "NA volatility",
       y = "HPS total",
        subtitle = paste0("partial r = ", round(c5$estimate[1,4],2),", p = .338"))+
ggplot(df_master_ema, aes(x = HPS_sum, y = mean_s_neg))+
  geom_point(size = 0.5)+
  geom_smooth(method = "lm", color = noiseColor, fill = noiseColor, linetype = "dashed", alpha = 0.1) +
  stat_poly_eq(use_label(c("R2","p")))+
  labs(x = "NA noise",
       y = "HPS total",
       subtitle = paste0("partial r = ", round(c6$estimate[1,4],2),", p < .001"))+

  plot_layout(nrow = 2)

ggsave("./figures/figure_hpsteps3.png",width = 8, height = 6)
```

# Part 3 (SI?): diurnal contributions to the EMA variability



## 3.1 plot example diurnal fit
### PA: Across subjects, the quadratic term is negative and linear term is positive.

```{r}
lm_diurn_pa <- lmer(PA_sum_scaled ~ I(time_index^2) + time_index +(1|Prolific.Id),data=df_PANAS_forlm)

summary(lm_diurn_pa)

df_PANAS_forlm1 <- df_PANAS_forlm %>%
  filter(!is.na(PA_sum_scaled)) 
df_PANAS_forlm1$PA_pred_val = fitted(lm_diurn_pa)

lm_diurn_pa_pred <- ggeffects::ggpredict(lm_diurn_pa, terms = c("time_index[1,2,3,4,5,6]"))

```
### NA: Across subjects, there is no significant diurnal effect.

```{r}
lm_diurn_na <- lmer(NA_sum_scaled ~ I(time_index^2) + time_index +(1|Prolific.Id),data=df_PANAS_forlm)

summary(lm_diurn_na)

df_PANAS_forlm2 <- df_PANAS_forlm %>%
  filter(!is.na(NA_sum_scaled)) 
df_PANAS_forlm2$NA_pred_val = fitted(lm_diurn_na)

lm_diurn_na_pred <- ggeffects::ggpredict(lm_diurn_na, terms = c("time_index[1,2,3,4,5,6]"))

pda <- 
  
ggplot()+
  geom_line(data=lm_diurn_pa_pred, aes(x = x, y = predicted),linewidth = 1, color = "orange")+
  geom_ribbon(data=lm_diurn_pa_pred,aes(x = x, ymin = conf.low, ymax = conf.high),linewidth = 1, fill = "orange",
              alpha = 0.2)+
    geom_line(data=lm_diurn_na_pred, aes(x = x, y = predicted),linewidth = 1, color = "skyblue")+
  geom_ribbon(data=lm_diurn_na_pred,aes(x = x, ymin = conf.low, ymax = conf.high),linewidth = 1, fill = "skyblue",
              alpha = 0.2)+
    labs(title = 'Diurnal Variation Model fit',
         y = 'predicted standardized affect', x = 'time of day')+
   scale_x_continuous(breaks = 1:6,labels = c("9-11AM","11AM-1PM","1-3PM","3-5PM","5-7PM","7-9PM"),
                     guide = guide_axis(angle = 45))+
    theme_classic()+
  annotate("text", x = min(lm_diurn_pa_pred$x)+1, y = lm_diurn_pa_pred$predicted[1], label = "PosAff", color = "orange", vjust = 0.5) +
  annotate("text", x = min(lm_diurn_na_pred$x)+1, y = lm_diurn_na_pred$predicted[1], label = "NegAff", color = "skyblue",  vjust = -2.5)
```
```{r}
pd2 <- ggplot(df_master_ema %>% 
         dplyr::select(`t^2_Estimate_PA`,`t^2_Estimate_NA`,`t_Estimate_PA`,`t_Estimate_NA`) %>% 
           pivot_longer(`t^2_Estimate_PA`:`t_Estimate_NA`,names_to = c("parameter","affect"),
                        names_pattern = "(.*)_Estimate_(.*)") %>% 
         mutate(affect = ifelse(affect == "PA","PosAff","NegAff"),
                parameter = ifelse(parameter == "t^2","quadratic term","linear term"),
                parameter = factor(parameter, levels = c("quadratic term","linear term"))), 
       aes(x = affect, y = value, group = interaction(parameter, affect))) +
  facet_wrap(~parameter, scales = "free_y")+
  geom_violin(aes(color = affect), alpha = 0.5) +
  geom_jitter(aes(color = affect), size = 0.1, alpha = 0.5) +
  stat_summary(geom = "pointrange", fun.data = mean_cl_normal, position = position_dodge(0.9),
               size = 0.2) +
  scale_color_manual(values = c("PosAff" = "orange", "NegAff" = "skyblue")) +
  scale_fill_manual(values = c("PosAff" = "orange", "NegAff" = "skyblue")) +
  geom_hline(yintercept = 0, linetype = "dotted") +
  theme_classic() +
  theme(legend.position = "none")+
  labs(x = "",
       y = "parameter value")

t.test(df_master_ema$`t^2_Estimate_PA`, mu = 0)
t.test(df_master_ema$`t^2_Estimate_NA`, mu = 0)

# pd3 <- ggplot(df_master_ema %>% 
#          dplyr::select(`t_Estimate_PA`,`t_Estimate_NA`) %>% 
#          rename(PosAff = `t_Estimate_PA`,
#                 NegAff = `t_Estimate_NA`) %>% 
#          pivot_longer(PosAff:NegAff,
#                       names_to = "Affect", values_to = "lin_term"), aes(x = Affect, y = lin_term))+
#   geom_violin(aes(color = Affect))+
#   geom_jitter(width = 0.3,size=0.1)+
#   stat_summary(aes(color = Affect),geom = "pointrange")+
#   scale_color_manual(values = c("skyblue","orange"))+
#   geom_hline(yintercept = 0, linetype = "dotted")+
#   theme(legend.position = "none")

t.test(df_master_ema$`t_Estimate_PA`, mu = 0)
t.test(df_master_ema$`t_Estimate_NA`, mu = 0)
```

## 3.2 demonstrate that diurnal variation of PA contributes to noise, but not volatility
```{r}
chart.Correlation(df_master_ema %>% 
                    dplyr::select(PA_mean,PA_se,PA_mssd,mean5_vmu_pos,mean5_s_pos,
                                  `t_Estimate_PA`,`t^2_Estimate_PA`,R2c_PA) %>% 
                    rename(t2 = `t^2_Estimate_PA`,
                           t = `t_Estimate_PA`))

chart.Correlation(df_master_ema %>% 
                    dplyr::select(NA_mean,NA_se,NA_mssd,mean5_vmu_neg,mean5_s_neg,
                                  `t_Estimate_NA`,`t^2_Estimate_NA`,R2c_NA) %>% 
                    rename(t2 = `t^2_Estimate_NA`,
                           t = `t_Estimate_NA`))

summary(lm(scale(PA_se) ~ scale(`t^2_Estimate_PA`) + scale(`t_Estimate_PA`),df_master_ema))
summary(lm(scale(PA_mssd) ~ scale(`t^2_Estimate_PA`) + scale(`t_Estimate_PA`),df_master_ema))
summary(lm(scale(PA_se) ~ scale(R2c_PA),df_master_ema))
summary(lm(scale(PA_mssd) ~ scale(R2c_PA),df_master_ema))
```

```{r}
ps <- ggplot(df_master_ema, aes(x = mean5_vmu_pos, y = `t^2_Estimate_PA`))+
  geom_point(size = 0.5)+
  geom_smooth(method = "lm", color = vmuColor, fill = vmuColor) +
  geom_hline(yintercept = 0, linetype = "dashed")+
  stat_poly_eq(use_label(c("R2","p")),color = vmuColor)+
  labs(title = "Quadratic term",
       x = "PA volatility",
       y = "quadratic term")+
  
  ggplot(df_master_ema, aes(x = mean5_vmu_pos, y = `t_Estimate_PA`))+
  geom_point(size = 0.5)+
  geom_smooth(method = "lm", color = vmuColor, fill = vmuColor) +
  geom_hline(yintercept = 0, linetype = "dashed")+
  stat_poly_eq(use_label(c("R2","p")),color = vmuColor)+
  labs(title = "Linear term",
       x = "PA volatility",
       y = "linear term")+
  
  ggplot(df_master_ema, aes(x = mean5_vmu_pos, y = log(R2c_PA)))+
  geom_point(size = 0.5)+
  geom_smooth(method = "lm", color = vmuColor, fill = vmuColor) +
  geom_hline(yintercept = 0, linetype = "dashed")+
  stat_poly_eq(use_label(c("R2","p")),color = vmuColor)+
  labs(title = "R2",
       x = "PA volatility",
       y = "log R2")+
  
ggplot(df_master_ema, aes(x = mean_s_pos, y = `t^2_Estimate_PA`))+
  geom_point(size = 0.5)+
  geom_smooth(method = "lm", color = noiseColor, fill = noiseColor) +
  geom_hline(yintercept = 0, linetype = "dashed")+
  stat_poly_eq(use_label(c("R2","p")),color = noiseColor)+
  labs(x = "PA noise",
       y = "quadratic term")+


ggplot(df_master_ema, aes(x = mean_s_pos, y = `t_Estimate_PA`))+
  geom_point(size = 0.5)+
  geom_smooth(method = "lm", color = noiseColor, fill = noiseColor) +
  geom_hline(yintercept = 0, linetype = "dashed")+
  stat_poly_eq(use_label(c("R2","p")),color = noiseColor)+
  labs(x = "PA noise",
       y = "linear term") +
  

ggplot(df_master_ema, aes(x = mean_s_pos, y = log(R2c_PA)))+
  geom_point(size = 0.5)+
  geom_smooth(method = "lm", color = noiseColor, fill = noiseColor) +
  geom_hline(yintercept = 0, linetype = "dashed")+
  stat_poly_eq(use_label(c("R2","p")),color = noiseColor)+
  labs(x = "PA noise",
       y = "log R2")
```
```{r}
summary(df_master_ema$mean5_vmu_pos)
summary(df_master_ema$mean5_s_pos)

l3 <- lm(scale(`t^2_Estimate_PA`)~ scale(mean5_vmu_pos) + scale(mean_s_pos),df_master_ema)

l4 <- lm(scale(`t_Estimate_PA`)~ scale(mean5_vmu_pos) + scale(mean_s_pos),df_master_ema)

l5 <- lm(scale(R2c_PA) ~ scale(mean5_vmu_pos) + scale(mean_s_pos),df_master_ema)

summary(lm(scale(R2c_NA) ~ scale(mean5_vmu_neg) + scale(mean_s_neg),df_master_ema))


bars3 <- Reduce(rbind,
       list(as.data.frame(summary(l3)$coefficients) %>% 
              mutate(reg = "quadratic term"),
            as.data.frame(summary(l4)$coefficients) %>% 
              mutate(reg = "linear term"),
            as.data.frame(summary(l5)$coefficients) %>% 
              mutate(reg = "R2"))) %>% 
  rownames_to_column() %>% 
  rename(variable = rowname,
         se = `Std. Error`,
         p_val = `Pr(>|t|)`) %>% 
  mutate(sig = ifelse(p_val < .001, "***",
                      ifelse(p_val < .01, "**",
                             ifelse(p_val < .05,"*",
                                    ifelse(p_val < .1,"†","ns")))))

bars3$variable[grepl("vmu",bars3$variable)] <- "volatility"
bars3$variable[grepl("_s_",bars3$variable)] <- "noise"

bars3 <- bars3 %>% 
  rowwise() %>% 
  mutate(alpha = ifelse(grepl("\\*", sig), "1","0"))

pd1 <- ggplot(bars3 %>% 
         filter(!grepl("Intercept", variable)) %>% 
         mutate(variable = factor(variable, levels = c("volatility", "noise")),
                reg = factor(reg, levels = c("quadratic term", "linear term", "R2")))) +
  geom_col(aes(x = reg, y = Estimate, group = variable, fill = variable, alpha = alpha),
           width = 0.4, position = position_dodge(width = 0.5)) +
  geom_errorbar(aes(x = reg, ymin = Estimate - se, ymax = Estimate + se, group = variable),
                width = 0.1, position = position_dodge(width = 0.5)) +
  geom_text(aes(x = reg, y = (Estimate + (Estimate) / abs(Estimate) * se  + (Estimate) / abs(Estimate) * 0.05), 
                label = sig, group = variable), 
            position = position_dodge(width = 0.5)) +
  scale_alpha_manual(values = c("1" = 1, "0" = 0.5), guide = "none") +
  scale_fill_manual(values = c(vmuColor, noiseColor)) +
  labs(y = "Standardized \u03b2",
       title = "diurnal model ~ PA variability",
       x = "")+
  theme(legend.position = "top")
```

```{r}
l3b <- lm(`t^2_Estimate_PA` ~ mean5_vmu_pos + mean_s_pos,df_master_ema)
l4b <- lm(`t_Estimate_PA` ~ mean5_vmu_pos + mean_s_pos,df_master_ema)

mydf3 <- ggeffects::ggpredict(l3b, terms = c("mean5_vmu_pos[-3.9591,-2.1768]"))
mydf4 <- ggeffects::ggpredict(l4b, terms = c("mean5_vmu_pos[-3.9591,-2.1768]"))

x = 1:6
y = mydf3$predicted[1]*x^2 + mydf4$predicted[1]*x
yl = mydf3$conf.low[1]*x^2 + mydf4$conf.low[1]*x
yh = mydf3$conf.high[1]*x^2 + mydf4$conf.high[1]*x
d <- data.frame(x,y,yl,yh,level = "bottom 25%")

y = mydf3$predicted[2]*x^2 + mydf4$predicted[2]*x
yl = mydf3$conf.low[2]*x^2 + mydf4$conf.low[2]*x
yh = mydf3$conf.high[2]*x^2 + mydf4$conf.high[2]*x
d2 <- data.frame(x,y,yl,yh,level = "top 25%")

d <- rbind(d,d2)
# pv <- 
pv <-  ggplot(data = d,aes(x = x, y = y, alpha = level))+
  geom_line(linewidth = 1, color = vmuColor)+
  ylim(0,1)+
  scale_x_continuous(breaks = 1:6, labels = c("9-11AM","11AM-1PM","1-3PM","3-5PM","5-7PM","7-9PM"),
                     guide = guide_axis(angle = 45))+
  labs(y = "predicted PA (a.u.)",
       x = "time",
       title = "diurnal variation by volatility",
       alpha = "volatility level")+
  scale_alpha_manual(values = c("top 25%" = 1, "bottom 25%" = 0.5))

mydf5 <- ggeffects::ggpredict(l3b, terms = c("mean_s_pos[-1.5564,-0.9052]"))
mydf6 <- ggeffects::ggpredict(l4b, terms = c("mean_s_pos[-1.5564,-0.9052]"))
x = 1:6
y = mydf5$predicted[1]*x^2 + mydf6$predicted[1]*x
d <- data.frame(x,y,level = "bottom 25%")

y = mydf5$predicted[2]*x^2 + mydf6$predicted[2]*x
d2 <- data.frame(x,y,level = "top 25%")

d <- rbind(d,d2)

pn <- ggplot(data = d,aes(x = x, y = y, alpha = level))+
  geom_line(linewidth = 1, color = noiseColor)+
  ylim(0,1)+
  scale_x_continuous(breaks = 1:6, labels = c("9-11AM","11AM-1PM","1-3PM","3-5PM","5-7PM","7-9PM"),
                     guide = guide_axis(angle = 45))+
  labs(y = "predicted PA (a.u.)",
       x = "time",
       title = "diurnal variation by noise",
       alpha = "noise level")+
  scale_alpha_manual(values = c("top 25%" = 1, "bottom 25%" = 0.5))

(pda+pd2)/
ps/(pv+pn)+
  plot_annotation(tag_levels = "A")+
  plot_layout(heights = c(1,2,1))
  

ggsave("./figures/figure_dmv.png",width = 8, height = 10)
```
### diurnal terms and traits
```{r fig.height=10, fig.width=10}
chart.Correlation(df_master_ema %>% 
                    dplyr::select(TEPS_sum,HPS_sum,CESD_sum,PA_se,PA_mssd,
                                  `t_Estimate_PA`,`t^2_Estimate_PA`,R2c_PA,R2c_NA) %>% 
                    rename(t2 = `t^2_Estimate_PA`,
                           t = `t_Estimate_PA`))

summary(lm(TEPS_sum ~ `t^2_Estimate_PA` + `t_Estimate_PA`,df_master_ema))
summary(lm(HPS_sum ~ `t^2_Estimate_PA` + `t_Estimate_PA`,df_master_ema))
summary(lm(CESD_sum ~ `t^2_Estimate_PA` + `t_Estimate_PA`,df_master_ema))
```

# autoregression stuff
### PA and NA AR separately
```{r}
df_corr <- df_master_ema %>% 
                    ungroup() %>% 
                    drop_na() %>% 
                    dplyr::select(TEPS_sum,HPS_sum,CESD_sum,PA_mean,NA_mean,AR_PA_sum,AR_NA_sum,PA_mssd,NA_mssd,
                                  mean5_vmu_pos,mean5_vmu_neg,mean5_s_pos,mean5_s_neg)

corm <- cor(df_corr,
            method = "pearson", use = "complete.obs")

p.mat <- cor_pmat(df_corr,
            method = "pearson", use = "complete.obs")

knitr::kable(corm, digits = 3)
knitr::kable(p.mat, digits = 3)

ggcorrplot::ggcorrplot(corm, 
           p.mat = p.mat, lab = T, insig = "blank", type = "lower",tl.cex = 10,lab_size = 3,
           colors = c("skyblue", "white", "orange"))
```