---
title: "moodVariability"
author: "Ryan Yan"
date: "2025-09-21"
output:
  html_document:
    df_print: paged
  html_notebook:
    code_folding: hide
  pdf_document: default
---

# library b
```{r setup, warning=FALSE,message=FALSE}
rm(list = ls())
setwd("~/Desktop/MoodInstability/moodVariability/")
source(here::here("./scripts/load_library.R"))

#some basic formatting stuff
theme_set(theme_classic()+
          theme(text = element_text(family = "Helvetica", size = 10)))
vmuColor <- "red"
noiseColor <- 'royalblue3'
muColor <- 'forestgreen'

# load and combine data
data_dir <- "~/Desktop/MoodInstability/moodVariability/data/for_share/"

# Simple reads
file_map <- c(
  "df_master"              = "df_master.csv",
  "demo_info"              = "demo_info.csv",
  "df_PANAS"               = "df_PANAS.csv",
  "df_panas_Est_tc"        = "df_panas_Est_tc.csv",
  "df_all"                 = "df_all.csv",
  "df_Xs_scaled_all2_long" = "df_Xs_scaled_all2_long.csv",
  "df_days"                = "df_days.csv",
  "df_reg"                 = "df_reg.csv",
  "df_gor_Est_tc"          = "df_gor_Est_tc.csv",
  "df_Xs_scaled_all_long"  = "df_Xs_scaled_all_long.csv",
  "df_panas_var1"          = "var1model_panas_results.csv",
  "df_task_var1"           = "var1model_task_results.csv",
  "df_reward_sched"        = "reward_sched.csv",
  "df_gor_Est_long"        = "df_gor_Est_long.csv",
  "df_wof"                 = "df_wof.csv",
  "df_Xs_scaled_sum_all_long" = "df_Xs_scaled_sum_all_long.csv",
  "df_wof_react"           = "df_wof_react.csv"
)

for (name in names(file_map)) {
  assign(name, read_csv(paste0(data_dir, file_map[[name]])))
}

# Reads with extra processing
df_PANAS_uniform_response <- read_csv(paste0(data_dir, "df_PANAS_uniform_response.csv")) %>%
  filter(proportion_flatline > 0.3)

df_panas_Est_nocloseresponse <- read_csv(paste0(data_dir, "ema_panas_params_noCloseResponse.csv")) %>%
  rename(subject = id) %>%
  pivot_wider(names_from = "panas_type", values_from = mean_mu:last_vmu)

df_master <- df_master %>% left_join(df_panas_Est_nocloseresponse)
```

# demographics
```{r}
sum(is.na(demo_info$Sex))
summary(demo_info$Sex)
table(demo_info$Sex)

sum(is.na(demo_info$age))
table(demo_info$age)
mean(demo_info$age, na.rm = T)
sd(demo_info$age, na.rm = T)
min(demo_info$age, na.rm = T)
max(demo_info$age, na.rm = T)

table(demo_info$`Country of Birth`)

sum(is.na(demo_info$`First Language`))
table(demo_info$`First Language`)

table(demo_info$`Country of Birth`)

sum(is.na(demo_info$`Current Country of Residence`))
table(demo_info$`Current Country of Residence`)
```

## tally the number of days between two runs of RL tasks
```{r}
table(df_days$day_diff)
median(df_days$day_diff,na.rm = T)
mean(df_days$day_diff,na.rm = T)
sd(df_days$day_diff,na.rm = T)

table(df_days$day_since_enrol)
median(df_days$day_since_enrol,na.rm = T)
mean(df_days$day_since_enrol,na.rm = T)
sd(df_days$day_since_enrol,na.rm = T)
```

## summarise how many PANAS people filled
```{r}
df_PANAS_completion<-df_PANAS %>% 
  filter(subject %in% df_master$subject) %>% 
  group_by(subject) %>% 
  count()

mean(df_PANAS_completion$n)
sd(df_PANAS_completion$n)
```

## summarise the average time between two surveys (excluding night-to-night)
```{r}
df_PANAS_timing <- df_PANAS %>% 
  mutate(duration = Survey.Submitted.Time-Survey.Started.Time) %>% 
  group_by(subject) %>% 
  mutate(last_trigger = lag(Trigger.Index),
         nt_since_last_trigger = Trigger.Index - last_trigger,
    trigger_time_difference = ifelse(time_index > 1 & nt_since_last_trigger == 1,
    Survey.Submitted.Time - lag(Survey.Submitted.Time), 
    NA)) 

df_PANAS_timing %>% filter(trigger_time_difference<0) #examine anomaly cases
#There were two cases where a participant completed the next trigger before the previous trigger, which may be due to a time zone change.
df_PANAS_timing %>% filter(subject == 221,Trigger.Index%in% 85:87)
df_PANAS_timing %>% filter(subject == 283,Trigger.Index%in% 61:63)

df_PANAS_timing %>% 
  filter(trigger_time_difference >= 0) %>% 
  ungroup() %>% 
  mutate(time_hours = as.numeric(trigger_time_difference) / 3600) %>%
  summarise(
    mean_hours  = mean(time_hours, na.rm = TRUE),
    sd_hours    = sd(time_hours, na.rm = TRUE),
    median_hours = median(time_hours, na.rm = TRUE),
    min_hours   = min(time_hours, na.rm = TRUE),
    max_hours   = max(time_hours, na.rm = TRUE),
    iqr_hours   = IQR(time_hours, na.rm = TRUE)
  )

df_PANAS_timing_summary <- df_PANAS_timing %>% 
  filter(trigger_time_difference >= 0) %>% 
  ungroup() %>% 
  group_by(subject) %>% 
  summarise(mean_time_diff = mean(trigger_time_difference,na.rm=T)/3600,
            min_time_diff = min(trigger_time_difference,na.rm=T)/60,
            count_short_response = sum(trigger_time_difference/3600 < 1/6),
            med_time_diff = median(trigger_time_difference)/3600)%>% 
  left_join(df_PANAS_completion %>% rename(nobs=n),by="subject") %>% 
  mutate(count_short_response=count_short_response/nobs)

sum(df_PANAS_timing_summary$count_short_response>0)

ggplot(df_PANAS_timing,aes(x=as.numeric(duration)))+
  geom_histogram()+
  scale_x_log10()+
  # geom_vline(xintercept = median(as.numeric(df_PANAS_timing$duration)))+
  labs(x = "Completion time (s)",
       title = "Completion time")

ggplot(df_PANAS_timing,aes(x=trigger_time_difference/3600))+
  geom_histogram()+
  labs(x = "time since last trigger (hour)",
       title = "Time since last trigger",
       subtitle = "all triggers")+
ggplot(df_PANAS_timing_summary,aes(x=med_time_diff))+
  geom_histogram()+
  labs(title = "Median of time difference",
       x = "Time difference (hour)",
       subtitle = "across participants")+
ggplot(df_PANAS_timing_summary,aes(x=count_short_response))+
  geom_histogram(binwidth = 0.01)+
  labs(x = "% triggers completed \nwithin 10 min since last submission",
       title = "% of back-to-back trigger",
       subtitle = "across participants")+
  plot_layout(nrow = 1)+
  plot_annotation(tag_levels = "A")

ggsave("../figures/figure_s2.png",width = 10, height =3)

summary(df_PANAS_timing_summary$count_short_response)
sum(df_PANAS_timing_summary$count_short_response*df_PANAS_timing_summary$nobs)/sum(df_PANAS_timing_summary$nobs)
```

# write a matrix for doing a sensitivity analysis, excluding those surveys that are too close to the previous one

```{r}
df_PANAS_out <- df_PANAS %>% 
  left_join(df_PANAS_timing) %>% 
  dplyr::select(subject,Trigger.Index:time_index,PAminusNA_sum,trigger_time_difference) %>% 
  mutate(trigger_time_difference = ifelse(is.na(trigger_time_difference),9999,trigger_time_difference)) %>% 
  filter(trigger_time_difference > 1/6*3600) %>% 
  dplyr::select(subject,Trigger.Index,PAminusNA_sum) %>% 
  pivot_wider(id_cols = subject,names_from = Trigger.Index, values_from = PAminusNA_sum) %>% 
  dplyr::select(-subject)

df_PANAS_out_old <- df_PANAS %>% 
  dplyr::select(subject,Trigger.Index,PAminusNA_sum) %>% 
  pivot_wider(id_cols = subject,names_from = Trigger.Index, values_from = PAminusNA_sum) %>% 
  dplyr::select(-subject)

sum(is.na(df_PANAS_out))
sum(is.na(df_PANAS_out_old))

R.matlab::writeMat(
  "../data/raw/raw_mat/PANASPosMinNegFrMod_noCloseResponse.mat",
  df_PANAS_out = as.matrix(df_PANAS_out)
)
```



### show diurnal variable in PANAS ratings
```{r}
df_panas_Est_tc_diur <- df_panas_Est_tc %>% 
  group_by(subject,panas_type) %>% 
  mutate(day_id = floor((trial_id -1) / 6) + 1,
         time_id = trial_id - 6 * (day_id - 1)) %>% 
  mutate(origval = origval - mean(origval,na.rm = T))

df_panas_Est_tc_diur_sum <- df_panas_Est_tc_diur%>% 
  group_by(subject,panas_type,time_id) %>% 
  summarise(origval = mean(origval, na.rm = T))%>% 
  group_by(panas_type,time_id) %>% 
  summarise(mean = mean(origval, na.rm = T),
            se = sd(origval, na.rm = T)/sqrt(n()))

df_panas_Est_tc_diur_indiv <- df_panas_Est_tc_diur %>%
  group_by(subject, panas_type, time_id) %>%
  summarise(origval = mean(origval, na.rm = T), .groups = "drop")

p1 <- 
ggplot(df_panas_Est_tc_diur_sum %>% filter(panas_type == "pos"), aes(x = time_id, y = mean))+
  geom_line(data = df_panas_Est_tc_diur_indiv %>% filter(panas_type == "pos"), aes(x = time_id, y = origval, group = subject), alpha = 0.1, linewidth = 0.25, inherit.aes = FALSE)+
  geom_line(size = 1)+
  ylim(-1,1)+
  labs(title = "PA",
       x = "time (h)",
       y = "affect (mean dev)")+
  scale_x_continuous(breaks = 1:6, labels = c("9~11","11~1","1~3","3~5","5~7","7~9"))+
 geom_ribbon(aes(x = time_id, ymin = mean - se, ymax = mean + se), alpha = 0.4)+
ggplot(df_panas_Est_tc_diur_sum %>% filter(panas_type == "neg"), aes(x = time_id, y = mean))+
  geom_line(data = df_panas_Est_tc_diur_indiv %>% filter(panas_type == "neg"), aes(x = time_id, y = origval, group = subject), alpha = 0.1, linewidth = 0.25, inherit.aes = FALSE)+
  geom_line(size = 1)+
  geom_ribbon(aes(x = time_id, ymin = mean - se, ymax = mean + se), alpha = 0.4)+
  ylim(-1,1)+
  labs(title = "NA",
       x = "time (h)",
       y = "affect (mean dev)")+
  scale_x_continuous(breaks = 1:6, labels = c("9~11","11~1","1~3","3~5","5~7","7~9"))+
  ggplot(df_panas_Est_tc_diur_sum %>% filter(panas_type == "posminusneg"), aes(x = time_id, y = mean))+
  geom_line(data = df_panas_Est_tc_diur_indiv %>% filter(panas_type == "posminusneg"), aes(x = time_id, y = origval, group = subject), alpha = 0.1, linewidth = 0.25, inherit.aes = FALSE)+
  geom_line(size = 1)+
  ylim(-1,1)+
  labs(title = "PA minus NA",
       x = "time (h)",
       y = "affect (mean dev)")+
  scale_x_continuous(breaks = 1:6, labels = c("9~11","11~1","1~3","3~5","5~7","7~9"))+
  geom_ribbon(aes(x = time_id, ymin = mean - se, ymax = mean + se), alpha = 0.4)

p1
```

```{r}
df_panas_Est_tc_day_sum <- df_panas_Est_tc_diur%>% 
  group_by(subject,panas_type,day_id) %>% 
  summarise(origval = mean(origval, na.rm = T))%>% 
  group_by(panas_type,day_id) %>% 
  summarise(mean = mean(origval, na.rm = T),
            se = sd(origval, na.rm = T)/sqrt(n())) %>% 
  mutate(panas_type = ifelse(panas_type == "pos","PA", 
                             ifelse(panas_type == "neg","NA",
                                    ifelse(panas_type == "posminusneg","PA minus NA",panas_type))))

df_panas_Est_tc_day_indiv <- df_panas_Est_tc_diur %>%
  group_by(subject, panas_type, day_id) %>%
  summarise(origval = mean(origval, na.rm = T), .groups = "drop") %>%
  mutate(panas_type = ifelse(panas_type == "pos","PA", 
                             ifelse(panas_type == "neg","NA",
                                    ifelse(panas_type == "posminusneg","PA minus NA",panas_type))))

p1/
ggplot(df_panas_Est_tc_day_sum %>% 
         filter(panas_type != "posminusneg_hr"), aes(x = day_id, y = mean,
                                    group = panas_type,
                                    fill = panas_type))+
  geom_line(data = df_panas_Est_tc_day_indiv %>% filter(panas_type != "posminusneg_hr"), 
            aes(x = day_id, y = origval, group = interaction(subject, panas_type),
                color=panas_type), 
             alpha = 0.1, linewidth = 0.25, inherit.aes = FALSE)+
  labs(x = "day",
       y = "affect (mean dev)")+
  geom_ribbon(aes(x = day_id, ymin = mean - se, ymax = mean + se), alpha = 0.3)+
  geom_line(aes(color = panas_type),size = 1)+
  scale_color_brewer(palette = "Paired")+
  scale_fill_brewer(palette = "Paired")+
  scale_x_continuous(breaks = c(1,5,10,15,20))+
  theme(legend.position = "top")+
  plot_annotation(tag_levels = "A")+
  facet_wrap(~panas_type)

ggsave("../figures/figure_s1.png",width = 8, height = 6)
```

## mean questionnaire scores
```{r}
mean(df_master$CESD_sum)
sd(df_master$CESD_sum)

mean(df_master$HPS_sum)
sd(df_master$HPS_sum)

mean(df_master$STAI_SA_sum)
sd(df_master$STAI_SA_sum)

mean(df_master$STAI_TA_sum)
sd(df_master$STAI_TA_sum)

mean(df_master$TEPS_ant_sum)
sd(df_master$TEPS_ant_sum)

mean(df_master$TEPS_con_sum)
sd(df_master$TEPS_con_sum)
```


# how did people perform, and how effective is the task in inducing affect?
## simulate some participants with a random strategy
```{r}
# simulated agents: random choices and totalmon from df_reward_sched (mag = apples, info = reward presence; 0.25 pts per apple)
set.seed(42)
n_agents <- 100
df_agents <- df_reward_sched %>%
  mutate(tree1info = as.numeric(as.character(tree1info)),
         tree2info = as.numeric(as.character(tree2info)),
         tree1mag = as.numeric(as.character(tree1mag)),
         tree2mag = as.numeric(as.character(tree2mag))) %>%
  slice(rep(1:n(), each = n_agents)) %>%
  mutate(agent_id = rep(1:n_agents, times = nrow(df_reward_sched))) %>%
  group_by(agent_id) %>%
  mutate(treechoicecode = sample(c(1L, 2L), size = n(), replace = TRUE),
         points = if_else(treechoicecode == 1L,
                          tree1info * tree1mag * 0.25,
                          tree2info * tree2mag * 0.25),
         totalmon = cumsum(points)) %>%
  ungroup()
```

```{r}
df_totalmon <- df_all %>% 
  filter(Trial.Index == 120) %>% 
  dplyr::select(subject,day_block,totalmon)

df_rt <-  df_all %>%
  filter(component == "present",
                            day_block %in% c("day1_block1","day2_block1")) %>% 
  dplyr::select(subject,Reaction.Time,Trial.Index,day_block)

df_rt_summary <- df_rt %>% 
  group_by(subject,day_block) %>% 
  summarise(median_rt = median(Reaction.Time),
            proportion_short_rt = sum(Reaction.Time < 100)/120)

# ggplot(df_rt %>% filter(subject > 200, subject < 250), aes(x = Reaction.Time))+
#   geom_histogram()+
#   scale_x_log10()+
#   facet_wrap(~subject,scale = "free_x")+
#   geom_vline(xintercept = 100, color = "red")

ggplot(df_rt_summary, aes(x = median_rt))+
  geom_histogram()+
  scale_x_log10()+
  labs(title = "median RT across participants",
       x = "RT (ms)")

ggsave("../figures/figure_rt.png",width = 4, height =3)

df_prob <- df_all %>%
  filter(component == "choice",
                            day_block %in% c("day1_block1","day2_block1")) %>% 
  group_by(subject,day_block) %>% 
  mutate(roll_mean_prob = rollmean(outcome, k = 10,na.pad = T,
                                   align = "right"),
         day = ifelse(day_block == "day1_block1","day1","day2"))

df_mrange <- df_all %>% 
  filter(day_block %in% c("day1_block1","day2_block1")) %>% 
  group_by(subject,day_block) %>% 
  summarise(max_mood = max(moodrate,na.rm = T),
            min_mood = min(moodrate,na.rm = T),
            span_mood = max_mood-min_mood,
            mean_mood = mean(moodrate,na.rm = T))%>% 
         arrange(desc(span_mood)) %>% 
  ungroup() %>% group_by(day_block) %>% 
  mutate(id = row_number())


df_agents_chance <- df_agents %>%
  group_by(Trial.Index) %>%
  summarise(totalmon = mean(totalmon),
            totalmon_lo = quantile(totalmon, 0.025),
            totalmon_hi = quantile(totalmon, 0.975),
            .groups = "drop")

pp <-ggplot(df_prob, aes(x = Trial.Index,y = totalmon,
                     color = day, group = interaction(day,subject)))+
   geom_line(linewidth = 0.1)+
   geom_line(data = df_agents_chance, aes(x = Trial.Index, y = totalmon),
             inherit.aes = FALSE, linewidth = 1, color = "black", linetype = "dashed")+
   scale_color_brewer(palette = "Set1")+
   labs(y = "cumulative points",
        x = "trial id",
        caption = "Dashed: random choice (chance level)")+
  theme(legend.position = c(0.25,0.8))+
ggplot(df_mrange %>% filter(day_block=="day1_block1") %>% ungroup())+
  geom_segment(aes(x = id,y = min_mood, yend = max_mood),
               color = "pink")+
  labs(x = "participant", y = "mood rating",
       title = "range of rating (day 1)")+
  scale_y_continuous(breaks = 1:9)+
  geom_point(aes(x = id,y = mean_mood),color = "hotpink",size=0.5)+
ggplot(df_mrange %>% filter(day_block=="day2_block1"))+
  geom_segment(aes(x = id,y = min_mood, yend = max_mood),
               color = "pink")+
  labs(x = "participant", y = "mood rating",
       title = "(day 2)")+
  scale_y_continuous(breaks = 1:9)+
  geom_point(aes(x = id,y = mean_mood),color = "hotpink",size=0.5)
  

summary(l1 <- lmer(moodrate  ~ outcome1b + (day_block|subject), df_reg %>% 
                     filter(outcome_magnitude1b %in% c(0,1),
                            day_block %in% c("day1_block1","day2_block1")) %>% 
                     mutate(outcome1b = as.factor(outcome1b))))

summary(l2 <- lmer(moodrate  ~ outcome_magnitude1b + (day_block|subject), df_reg %>% 
                     mutate(outcome_magnitude1b > 0) %>% 
                     filter(day_block %in% c("day1_block1","day2_block1"))))

p1 <- ggplot(df_reg %>%
  filter(day_block %in% c("day1_block1","day2_block1")),
                             aes(x = outcome_magnitude1b,
                                 y = moodrate,
                                 group = subject)) +
  geom_smooth(method = "lm", se = FALSE,
              color = "grey", size = 0.1) +
  geom_smooth(aes(group = 1),
              method = "lm", se = TRUE,
              color = "red", linewidth = 1) +
  labs(x = "reward magnitude",
       y = "mood ratings")+
  scale_y_continuous(breaks = 1:9)+
  scale_x_continuous(breaks = 0:10)

p2 <- ggplot(df_reg, aes(x = moodrate, y = stat(density)))+
  geom_histogram()+
  scale_x_continuous(breaks = 1:9)+
  coord_flip()+
  labs(x = "mood ratings")

p3 <- ggplot(df_reg %>% 
               filter(outcome_magnitude1b > 0), aes(x = outcome_magnitude1b, y = stat(density)))+
  geom_histogram()+
  scale_x_continuous(breaks = 1:10)+
  labs(x = "reward magnitude (when gain)")


pp/(p1+p2+p3)+
  plot_annotation(tag_levels = "A")

ggsave("../figures/figure_s8.png",width = 7, height =5)
```

## look at response styles
```{r}
df_reg_in <- df_reg %>%
  filter(day_block %in% c("day1_block1","day2_block1"))

## ARS or MRS -> should not see response to reward magnitude or outcome
l1 <- lmer(moodrate ~ 1 +(1+outcome1b|subject),df_reg_in)
summary(l1)

# Subject-specific slopes = fixed effect + random effect
slopes_binary <- coef(l1)$subject %>%
  rownames_to_column("subject") %>%
  rename(intercept = `(Intercept)`, slope = outcome1b)

l2 <- lmer(moodrate ~ 1 +(1+outcome_mag1b|subject),df_reg_in)

# Subject-specific slopes = fixed effect + random effect
slopes_magnitude <- coef(l2)$subject %>%
  rownames_to_column("subject") %>%
  rename(intercept = `(Intercept)`, slope = outcome_mag1b)

ggplot(slopes_binary, aes(x = slope)) +
  geom_histogram(bins = 30, fill = "steelblue", alpha = 0.7) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "red") +
  labs(x = "Individual slope (reward outcome effect)", y = "Participant count",
       title = "Affect reactivity to reward outcome") +
  theme_classic()+
ggplot(slopes_magnitude, aes(x = slope)) +
  geom_histogram(bins = 30, fill = "steelblue", alpha = 0.7) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "red") +
  labs(x = "Individual slope (reward magnitude effect)", y = "Participant count",
       title = "Affect reactivity to reward magnitude") +
  theme_classic()

ggsave("../figures/figure_s24.png",width = 7, height = 3)

participants_without_magnitude_modulation <- unique(c(slopes_binary$subject[slopes_binary$slope <= 0],
                                                      slopes_magnitude$subject[slopes_magnitude$slope <= 0]))
length(participants_without_magnitude_modulation)

summary(lm(mean5_vmu_posminusneg~mean5_vmu + mean5_s,
           df_master %>% filter(!subject %in% participants_without_magnitude_modulation)))
summary(lm(mean5_s_posminusneg~mean5_vmu + mean5_s,
           df_master %>% filter(!subject %in% participants_without_magnitude_modulation)))

summary(lm(mean5_vmu~X1+X2+X3,
           df_master %>% filter(!subject %in% participants_without_magnitude_modulation)))
summary(lm(mean5_s~X1+X2+X3,
           df_master %>% filter(!subject %in% participants_without_magnitude_modulation)))

summary(lm(mean5_vmu_posminusneg~X1+X2+X3,
           df_master %>% filter(!subject %in% participants_without_magnitude_modulation)))
summary(lm(mean5_s_posminusneg~X1+X2+X3,
           df_master %>% filter(!subject %in% participants_without_magnitude_modulation)))
```



```{r}
df_response_style <- df_reg_in %>%
  group_by(subject) %>%  
  summarise(
    n_ratings = n(),
    mean_mood = mean(moodrate, na.rm = TRUE),
    sd_mood = sd(moodrate, na.rm = TRUE),
    range_mood = max(moodrate, na.rm = TRUE) - min(moodrate, na.rm = TRUE),
    pct_extreme = mean(moodrate == 1 | moodrate == 9, na.rm = TRUE) * 100,  # ERS
    pct_mid = mean(moodrate == 5, na.rm = TRUE) * 100,       # MRS
    pct_low = mean(moodrate == 1, na.rm = TRUE) * 100,
    pct_high = mean(moodrate == 9, na.rm = TRUE) * 100
  )

p1 <- ggplot(df_response_style, aes(x = mean_mood)) +
  geom_histogram(bins = 25, fill = "steelblue", alpha = 0.7) +
  labs(x = "Mean rating", y = "Participant count", subtitle = "") +
  theme_classic()
p2 <- ggplot(df_response_style, aes(x = pct_extreme)) +
  geom_histogram(bins = 25, fill = "coral", alpha = 0.7) +
  labs(x = "% extreme (1 or 9)", y = "Participant count", subtitle = "ERS") +
  theme_classic()
p3 <- ggplot(df_response_style, aes(x = pct_mid)) +
  geom_histogram(bins = 25, fill = "seagreen", alpha = 0.7) +
  labs(x = "% midscale (5)", y = "Participant count", subtitle = "MRS") +
  theme_classic()
p4 <- ggplot(df_response_style, aes(x = range_mood)) +
  geom_histogram(bins = 25, fill = "gray50", alpha = 0.7) +
  labs(x = "Rating range (max - min)", y = "Participant count", subtitle = "Scale occupancy") +
  theme_classic()
(p1 + p2 + p3 + p4) +
  plot_annotation(title = "Response style across 332 participants",
                  tag_levels = "A")+
  plot_layout(nrow = 1)

ggsave("../figures/figure_r1_2_1.png",width = 10, height = 3)
```

```{r}
df_reg_in %>%
  mutate(rating_cat = cut(moodrate, breaks = seq(0.5, 9.5, 1), labels = 1:9)) %>%
  count(subject, rating_cat, .drop = FALSE) %>%
  group_by(subject) %>%
  mutate(pct = n / sum(n) * 100) %>%
  ungroup() %>%
  mutate(subject = fct_reorder(as.character(subject), pct, .fun = mean)) %>%
  ggplot(aes(x = rating_cat, y = subject, fill = pct)) +
  geom_tile() +
  scale_fill_viridis_c() +
  labs(x = "Rating category", y = "Participant", 
       fill = "% of ratings",
       title = "Rating distribution across participants") +
  theme_minimal() +
  theme(axis.text.y = element_blank(), axis.ticks.y = element_blank())
```


```{r}
# Loop through ERS and MRS thresholds, store lm outputs, visualize
ers_thresholds <- seq(40, 100, by = 10)

df_ers_mrs <- df_reg_in %>%
  group_by(subject) %>%
  summarise(
    pct_extreme = (mean(moodrate %in% c(1, 9), na.rm = TRUE) * 100),
    pct_at_mid = mean(moodrate == 5, na.rm = TRUE) * 100
  )

results_list <- list()
for (ers_t in ers_thresholds) {
    subj_ers <- df_ers_mrs %>% filter(pct_extreme > ers_t) %>% pull(subject)
    subj_mrs <- df_ers_mrs %>% filter(pct_at_mid > ers_t) %>% pull(subject)

    df_filt <- df_master %>%
      filter(!subject %in% participants_without_magnitude_modulation,
             !subject %in% subj_ers,
             !subject %in% subj_mrs)

    fit1 <- lm(scale(mean5_vmu_posminusneg) ~ scale(mean5_vmu) + scale(mean5_s), data = df_filt)
    fit2 <- lm(scale(mean5_s_posminusneg) ~ scale(mean5_vmu) + scale(mean5_s), data = df_filt)

    n_excluded <- length(union(subj_ers, subj_mrs))
    results_list[[length(results_list) + 1]] <- bind_rows(
      broom::tidy(fit1) %>% mutate(model = "mean5_vmu_posminusneg", thresh = ers_t, n_excluded = n_excluded),
      broom::tidy(fit2) %>% mutate(model = "mean5_s_posminusneg", thresh = ers_t, n_excluded = n_excluded)
    )
}

df_results_threshold <- bind_rows(results_list) %>%
  filter(term != "(Intercept)",
         ifelse(term == "scale(mean5_vmu)", model == "mean5_vmu_posminusneg",
                ifelse(term == "scale(mean5_s)", model == "mean5_s_posminusneg", NA))) %>%
  mutate(sig = p.value < 0.05) %>% 
  mutate(term = case_when(
  term == "scale(mean5_vmu)" ~ "volatility",
  term == "scale(mean5_s)"   ~ "noise",
  TRUE                ~ term   # fallback: keep original value
  ))

# Plot: estimate vs threshold, point shape = solid (sig) or hollow (not sig)
ggplot(df_results_threshold, aes(x = thresh, y = estimate, color = factor(term))) +
  geom_line(linewidth = 1, alpha = 0.2) +
  geom_hline(yintercept = 0)+
  geom_point(aes(shape = sig), size = 2) +
  geom_errorbar(aes(ymin = estimate - std.error, ymax = estimate + std.error), width = 2, alpha = 0.6) +
  geom_text(aes(label = n_excluded, y = estimate + std.error), vjust = -0.5, size = 2.5, show.legend = FALSE) +
  scale_shape_manual(values = c("FALSE" = 1, "TRUE" = 16), labels = c("p \u2265 .05", "p < .05")) +
  facet_wrap(~term)+
  labs(x = "Exclusion threshold (%)",
       y = "Estimate",
       color = "Term",
       shape = "Significance") +
  theme(legend.position = "bottom")+
  scale_x_continuous(breaks = seq(30,90,10))+
  scale_color_manual(values = c(noiseColor,vmuColor))

ggsave("../figures/figure_s25.png",width = 7, height = 4)
```

```{r}
# Loop through ERS and MRS thresholds, store lm outputs, visualize
ers_thresholds <- seq(40, 100, by = 10)

df_ers_mrs <- df_reg_in %>%
  group_by(subject) %>%
  summarise(
    pct_extreme = (mean(moodrate %in% c(1, 9), na.rm = TRUE) * 100),
    pct_at_mid = mean(moodrate == 5, na.rm = TRUE) * 100
  )

results_list <- list()
for (ers_t in ers_thresholds) {
    subj_ers <- df_ers_mrs %>% filter(pct_extreme > ers_t) %>% pull(subject)
    subj_mrs <- df_ers_mrs %>% filter(pct_at_mid > ers_t) %>% pull(subject)

    df_filt <- df_master %>%
      filter(!subject %in% participants_without_magnitude_modulation,
             !subject %in% subj_ers,
             !subject %in% subj_mrs)

    fit1 <- lm(scale(mean5_vmu) ~ scale(X1) + scale(X2) + scale(X3), data = df_filt)
    fit2 <- lm(scale(mean5_s) ~ scale(X1) + scale(X2) + scale(X3), data = df_filt)

    n_excluded <- length(union(subj_ers, subj_mrs))
    results_list[[length(results_list) + 1]] <- bind_rows(
      broom::tidy(fit1) %>% mutate(model = "mean5_vmu", thresh = ers_t, n_excluded = n_excluded),
      broom::tidy(fit2) %>% mutate(model = "mean5_s", thresh = ers_t, n_excluded = n_excluded)
    )
}

df_results_threshold <- bind_rows(results_list) %>%
  filter(term != "(Intercept)") %>%
  mutate(sig = p.value < 0.05) %>%
  mutate(term = case_when(
    term == "scale(X1)" ~ "trial -1~3",
    term == "scale(X2)" ~ "trial -4~6",
    term == "scale(X3)" ~ "trial -7~9",
    TRUE ~ term
  )) %>%
  mutate(term = factor(term, levels = c("trial -1~3", "trial -4~6", "trial -7~9")))

# One label per threshold for n_excluded (avoid overlap)
df_n_excluded <- df_results_threshold %>% distinct(thresh, n_excluded, model)

# Plot: color by X1/X2/X3, facet by model
p1<-ggplot(df_results_threshold, aes(x = thresh, y = estimate, color = term, group = term)) +
  geom_line(linewidth = 1) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "gray60") +
  geom_point(aes(shape = sig), size = 2.5) +
  geom_errorbar(aes(ymin = estimate - std.error, ymax = estimate + std.error), width = 2, linewidth = 0.6) +
  scale_shape_manual(values = c("FALSE" = 1, "TRUE" = 16), labels = c("p \u2265 .05", "p < .05")) +
  scale_color_manual(values = c("trial -1~3" = "#4A148C", "trial -4~6" = "#7B1FA2", "trial -7~9" = "#CE93D8")) +
  facet_wrap(~ model, labeller = as_labeller(c(mean5_vmu = "Task volatility ~ Affecitve Impact", mean5_s = "Task noise ~ Affecitve Impact"))) +
  labs(x = "Exclusion threshold (%)",
       y = "Standardized estimate",
       color = "Affective impact",
       shape = "Significance") +
  theme(legend.position = "bottom",
        strip.text = element_text(face = "bold")) +
  scale_x_continuous(breaks = seq(40, 100, 10))

results_list <- list()
for (ers_t in ers_thresholds) {
    subj_ers <- df_ers_mrs %>% filter(pct_extreme > ers_t) %>% pull(subject)
    subj_mrs <- df_ers_mrs %>% filter(pct_at_mid > ers_t) %>% pull(subject)

    df_filt <- df_master %>%
      filter(!subject %in% participants_without_magnitude_modulation,
             !subject %in% subj_ers,
             !subject %in% subj_mrs)

    fit1 <- lm(scale(mean5_vmu_posminusneg) ~ scale(X1) + scale(X2) + scale(X3), data = df_filt)
    fit2 <- lm(scale(mean5_s_posminusneg) ~ scale(X1) + scale(X2) + scale(X3), data = df_filt)

    n_excluded <- length(union(subj_ers, subj_mrs))
    results_list[[length(results_list) + 1]] <- bind_rows(
      broom::tidy(fit1) %>% mutate(model = "mean5_vmu_posminusneg", thresh = ers_t, n_excluded = n_excluded),
      broom::tidy(fit2) %>% mutate(model = "mean5_s_posminusneg", thresh = ers_t, n_excluded = n_excluded)
    )
}

df_results_threshold <- bind_rows(results_list) %>%
  filter(term != "(Intercept)") %>%
  mutate(sig = p.value < 0.05) %>%
  mutate(term = case_when(
    term == "scale(X1)" ~ "trial -1~3",
    term == "scale(X2)" ~ "trial -4~6",
    term == "scale(X3)" ~ "trial -7~9",
    TRUE ~ term
  )) %>%
  mutate(term = factor(term, levels = c("trial -1~3", "trial -4~6", "trial -7~9")))

# One label per threshold for n_excluded (avoid overlap)
df_n_excluded <- df_results_threshold %>% distinct(thresh, n_excluded, model)

# Plot: color by X1/X2/X3, facet by model
p2<-ggplot(df_results_threshold, aes(x = thresh, y = estimate, color = term, group = term)) +
  geom_line(linewidth = 1) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "gray60") +
  geom_point(aes(shape = sig), size = 2.5) +
  geom_errorbar(aes(ymin = estimate - std.error, ymax = estimate + std.error), width = 2, linewidth = 0.6) +
  scale_shape_manual(values = c("FALSE" = 1, "TRUE" = 16), labels = c("p \u2265 .05", "p < .05")) +
  scale_color_manual(values = c("trial -1~3" = "#4A148C", "trial -4~6" = "#7B1FA2", "trial -7~9" = "#CE93D8")) +
  facet_wrap(~ model, labeller = as_labeller(c(mean5_vmu_posminusneg = "ESM volatility ~ Affecitve Impact", mean5_s_posminusneg = "ESM noise ~ Affecitve Impact"))) +
  labs(x = "Exclusion threshold (%)",
       y = "Standardized estimate",
       color = "Affective impact",
       shape = "Significance") +
  theme(legend.position = "bottom",
        strip.text = element_text(face = "bold")) +
  scale_x_continuous(breaks = seq(40, 100, 10))

p1/p2
ggsave("../figures/figure_s26.png", width = 7, height = 8)
```

```{r}
df_response_style_panas <- df_PANAS %>%
  group_by(subject) %>%  
  summarise(
    n_ratings = n(),
    mean_mood = mean(PAminusNA_sum, na.rm = TRUE),
    sd_mood = sd(PAminusNA_sum, na.rm = TRUE),
    range_mood = max(PAminusNA_sum, na.rm = TRUE) - min(PAminusNA_sum, na.rm = TRUE),
    pct_extreme = mean(PAminusNA_sum == -50 | PAminusNA_sum == 50, na.rm = TRUE) * 100,  # ERS
    pct_mid = mean(PAminusNA_sum == 0, na.rm = TRUE) * 100,       # MRS
    pct_low = mean(PAminusNA_sum == -50, na.rm = TRUE) * 100,
    pct_high = mean(PAminusNA_sum == 50, na.rm = TRUE) * 100
  )

p1 <- ggplot(df_response_style_panas, aes(x = mean_mood)) +
  geom_histogram(bins = 25, fill = "steelblue", alpha = 0.7) +
  labs(x = "Mean rating", y = "Participant count", subtitle = "") +
  theme_classic()
p2 <- ggplot(df_response_style_panas, aes(x = pct_extreme)) +
  geom_histogram(bins = 25, fill = "coral", alpha = 0.7) +
  labs(x = "% extreme (1 or 9)", y = "Participant count", subtitle = "ERS") +
  theme_classic()
p3 <- ggplot(df_response_style_panas, aes(x = pct_mid)) +
  geom_histogram(bins = 25, fill = "seagreen", alpha = 0.7) +
  labs(x = "% midscale (5)", y = "Participant count", subtitle = "MRS") +
  theme_classic()
p4 <- ggplot(df_response_style_panas, aes(x = range_mood)) +
  geom_histogram(bins = 25, fill = "gray50", alpha = 0.7) +
  labs(x = "Rating range (max - min)", y = "Participant count", subtitle = "Scale occupancy") +
  theme_classic()
(p1 + p2 + p3 + p4) +
  plot_annotation(title = "PANAS Response style across 332 participants",
                  tag_levels = "A")+
  plot_layout(nrow = 1)
```


## summary statistics of parameter values (for parameter recovery)
```{r}
range(df_gor_Est_tc$vmu)
range(df_gor_Est_tc$s)
range(df_gor_Est_tc$mu)

summary_table <- df_master %>%
  summarise(across(
    c(mean5_mu, mean5_s, mean5_vmu, mean5_kmu,mean5_vs,
      mean5_mu_posminusneg, mean5_s_posminusneg, mean5_vmu_posminusneg,
      mean5_kmu_posminusneg, mean5_vs_posminusneg),
    list(
      Mean = ~mean(.x, na.rm = TRUE),
      SD   = ~sd(.x, na.rm = TRUE),
      Min  = ~min(.x, na.rm = TRUE),
      Max  = ~max(.x, na.rm = TRUE),
      N    = ~sum(!is.na(.x))
    ),
    .names = "{.col}_{.fn}"
  )) %>%
  pivot_longer(
    everything(),
    names_to = c("Variable", "Statistic"),
    names_pattern = "(.+)_(Mean|SD|Min|Max|N)$"
  ) %>%
  pivot_wider(names_from = Statistic, values_from = value)

knitr::kable(summary_table, digits = 3,
             caption = "Descriptive Statistics for df_master")

a <- list(
  
  final5m = as.matrix(
    df_master[, c("mean5_mu_posminusneg",
                  "mean5_mu")]
  ),
  
  final5model = as.matrix(
    df_master[, c("mean5_vmu_posminusneg",
                  "mean5_vmu",
                  "mean5_s_posminusneg",
                  "mean5_s")]
  ),
  
  final5modelhl = as.matrix(
    df_master[, c("mean5_kmu_posminusneg",
                  "mean5_kmu",
                  "mean5_vs_posminusneg",
                  "mean5_vs")]
  )
)

str(a)

R.matlab::writeMat(
  "./parameter_recovery/last5_parameters_from_participants.mat",a = a)
```


```{r}
ggplot(df_gor_Est_tc %>% filter(!is.na(day_block)), aes(x = trial_id, y = s, group = subject))+
   geom_line(alpha = 0.1)+
   facet_wrap(~day_block)+
   labs(title = "sd of low vs people")
```


## reliability of task parameters across 2 days
```{r}
df_master_sum <- df_master %>% 
  dplyr::select(mean5_s_d1r1, mean5_mu_d1r1, mean5_vmu_d1r1,
                mean5_s_d2r1, mean5_mu_d2r1, mean5_vmu_d2r1,
                mean5_s_posminusneg, mean5_mu_posminusneg, mean5_vmu_posminusneg) %>% 
  pivot_longer(everything(), names_to = "parameter", values_to = "value") %>%
  separate(parameter, into = c("prefix", "parameter", "source"), sep = "_",
           extra = "merge") %>%
  mutate(source = case_when(source == "posminusneg" ~ "ESM",
                            source == "d1r1" ~ "task day 1",
                            source == "d2r1" ~ "task day 2",
                            TRUE ~ source)) %>%
  dplyr::select(-prefix)

p1 <- ggplot(df_master_sum %>% filter(parameter == "mu") %>% 
               mutate(source = factor(source, levels = c("task day 1", "task day 2", "ESM"))),
             aes(x = source, y = value))+
  geom_violin(color = muColor)+
  geom_jitter(size = 0.1)+
  stat_summary(geom = "pointrange", size = 0.5, color = muColor)+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  labs(y = "parameter value", x = "", title = "mu")+
  
ggplot(df_master_sum %>% filter(parameter == "vmu") %>% 
               mutate(source = factor(source, levels = c("task day 1", "task day 2", "ESM"))),
             aes(x = source, y = value))+
  geom_violin(color = vmuColor)+
  geom_jitter(size = 0.1)+
  stat_summary(geom = "pointrange", size = 0.5, color = vmuColor)+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  labs(y = "", x = "", title = "vmu")+
  
ggplot(df_master_sum %>% filter(parameter == "s") %>% 
               mutate(source = factor(source, levels = c("task day 1", "task day 2", "ESM"))),
             aes(x = source, y = value))+
  geom_violin(color = noiseColor)+
  geom_jitter(size = 0.1)+
  stat_summary(geom = "pointrange", size = 0.5, color = noiseColor)+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  labs(y = "", x = "", title = "noise")
  
p2 <- ggplot(df_master, aes(x = mean5_vmu_d1r1, y = mean5_vmu_d2r1))+
  geom_point(size = 0.5)+
  geom_smooth(method = "lm", color = vmuColor, fill = vmuColor) +
  stat_poly_eq(use_label(c("R2","p")))+
  labs(title = "reliability of task volatility",
       x = "task day 1", y = "task day 2")+
ggplot(df_master, aes(x = mean5_s_d1r1, y = mean5_s_d2r1))+
  geom_point(size = 0.5)+
  geom_smooth(method = "lm", color = noiseColor, fill = noiseColor) +
  stat_poly_eq(use_label(c("R2","p")))+
  labs(title = "reliability of task noise",
       x = "task day 1", y = "task day 2")+
ggplot(df_master, aes(x = mean5_mu_d1r1, y = mean5_mu_d2r1))+
  geom_point(size = 0.5)+
  geom_smooth(method = "lm", color = muColor, fill = muColor) +
  stat_poly_eq(use_label(c("R2","p")))+
  labs(title = "reliability of task mu",
       x = "task day 1", y = "task day 2")

p2
ggsave("../figures/figure_s4.png",width = 8, height = 3)
```

```{r}
df_gor_Est_tc_sum <- df_gor_Est_tc %>% 
  group_by(subject, run) %>% 
  rename(SD = s) 

df_gor_Est_tc_sum_mean <- df_gor_Est_tc_sum%>% 
  group_by(run,trial_id) %>% 
  summarise_at(vars(mu_orig,vmu,SD), ~mean(.x,na.rm = T)) %>% 
  pivot_longer(c(mu_orig,vmu,SD), names_to = "parameter", values_to = "mean")

df_gor_Est_tc_sum_sd <- df_gor_Est_tc_sum%>% 
  group_by(run,trial_id) %>% 
  summarise_at(vars(mu_orig,vmu,SD), ~sd(.x,na.rm = T)/sqrt(n())) %>% 
  pivot_longer(c(mu_orig,vmu,SD), names_to = "parameter", values_to = "se")

df_gor_Est_tc_sum <- left_join(df_gor_Est_tc_sum_mean,df_gor_Est_tc_sum_sd) %>% 
  mutate(run = ifelse(run == "d1r1","day 1","day 2"),
         trial_id = trial_id - 1)

df_gor_Est_tc_sum$parameter <- factor(df_gor_Est_tc_sum$parameter, levels = c('mu_orig', 'vmu', 'SD'),
                                        labels = c("mu (original space)","vmu",'S'))

df_gor_Est_tc_indiv_mu <- df_gor_Est_tc %>% 
  filter(run %in% c("d1r1","d2r1")) %>%
  mutate(run = ifelse(run == "d1r1","day 1","day 2"), trial_id = trial_id - 1,
         parameter = factor("mu_orig", levels = c("mu_orig", "vmu", "s"), 
                           labels = c("mu (original space)", "vmu", "S")))

df_gor_Est_tc_indiv_var <- df_gor_Est_tc %>% 
  filter(run %in% c("d1r1","d2r1")) %>%
  mutate(run = ifelse(run == "d1r1","day 1","day 2"), trial_id = trial_id - 1) %>%
  pivot_longer(c(vmu, s), names_to = "parameter", values_to = "value") %>%
  mutate(parameter = factor(parameter, levels = c("vmu", "s"), labels = c("vmu", "S")))

p3 <- ggplot(df_gor_Est_tc_sum %>% filter(parameter %in% c("vmu","S")), aes(x = trial_id, y = mean, color = run))+
  geom_line(data = df_gor_Est_tc_indiv_var, aes(x = trial_id, y = value, group = interaction(subject, run),
                                                color = run), 
            alpha = 0.06, linewidth = 0.25, inherit.aes = FALSE)+
  geom_line(linewidth = 1)+
  geom_ribbon(aes(x = trial_id, ymin = mean-se, ymax = mean+se, fill = run),
              alpha = 0.4, color = NA)+
  facet_wrap(~parameter+run,nrow = 2, scales = "free_y")+
  labs(y = "parameter values",
       subtitle = "variability measures")


p3b <- ggplot(data = df_gor_Est_tc_sum %>% filter(parameter == "mu (original space)"), 
               aes(x = trial_id, y = mean, color = run))+
  geom_line(data = df_gor_Est_tc_indiv_mu, aes(x = trial_id, y = mu_orig, group = subject,
                                               color = run), 
            alpha = 0.1, linewidth = 0.25, inherit.aes = FALSE)+
  geom_line(linewidth = 1)+
  geom_ribbon(aes(x = trial_id, ymin = mean-se, ymax = mean+se,fill = run),
              alpha = 0.3, color = NA)+
  labs(title = "task mood rating parameters",
       y = "parameter values")+
  facet_wrap(~parameter+run)+
  theme(legend.position = "none")+
  labs(x = "trial ID",
       subtitle = "mu overlaid on original mood ratings")
```

```{r}
df_panas_Est_tc_sum <- df_panas_Est_tc %>% 
  filter(panas_type %in% c("posminusneg")) %>% 
  rename(SD = s) %>% 
  group_by(subject, panas_type) %>% 
  rowwise() %>% 
  mutate(day = floor((trial_id+5)/6),
         time = (trial_id+5) %% 6)

df_panas_Est_tc_sum_mean <- df_panas_Est_tc_sum%>% 
  group_by(panas_type,trial_id) %>% 
  summarise_at(vars(mu_orig,vmu,SD), ~mean(.x,na.rm = T)) %>% 
  pivot_longer(c(mu_orig,vmu,SD), names_to = "parameter", values_to = "mean")

df_panas_Est_tc_sum_sd <- df_panas_Est_tc_sum%>% 
  group_by(panas_type,trial_id) %>% 
  summarise_at(vars(mu_orig,vmu,SD), ~sd(.x,na.rm = T)/sqrt(n())) %>% 
  pivot_longer(c(mu_orig,vmu,SD), names_to = "parameter", values_to = "se")

df_panas_Est_tc_sum <- left_join(df_panas_Est_tc_sum_mean,df_panas_Est_tc_sum_sd) %>% 
  mutate(trial_id = trial_id - 1)

df_panas_Est_tc_sum$parameter <- factor(df_panas_Est_tc_sum$parameter, levels = c('mu_orig', 'vmu', 'SD'),
                                        labels = c("mu (original space)","vmu",'S'))

df_panas_Est_tc_indiv_mu <- df_panas_Est_tc %>% 
  filter(panas_type == "posminusneg") %>%
  mutate(trial_id = trial_id - 1)

df_panas_Est_tc_indiv_var <- df_panas_Est_tc %>% 
  filter(panas_type == "posminusneg") %>%
  mutate(trial_id = trial_id - 1) %>%
  pivot_longer(c(vmu, s), names_to = "parameter", values_to = "value") %>%
  mutate(parameter = factor(parameter, levels = c("vmu", "s"), labels = c("vmu", "S")))

p4<-ggplot(df_panas_Est_tc_sum %>% filter(parameter %in% c("vmu","S")), aes(x = trial_id, y = mean, color = panas_type))+
  geom_line(data = df_panas_Est_tc_indiv_var, aes(x = trial_id, y = value, group = subject), 
            alpha = 0.1, linewidth = 0.25, color = "gray40", inherit.aes = FALSE)+
  geom_line(linewidth = 1)+
  geom_ribbon(aes(x = trial_id, ymin = mean-se, ymax = mean+se, fill = panas_type),
              alpha = 0.3, color = NA)+
  facet_wrap(~parameter,nrow = 5, scales = "free_y")+
  labs(y = "parameter values",
       subtitle = "variability measures",
       x = "data point")+
  scale_x_continuous(breaks = seq(0,120,12))+
  theme(legend.position = "none")

p4b <- ggplot(data = df_panas_Est_tc_sum %>% filter(parameter == "mu (original space)"), 
               aes(x = trial_id, y = mean, color = panas_type))+
  geom_line(data = df_panas_Est_tc_indiv_mu, aes(x = trial_id, y = mu_orig, group = subject), 
            alpha = 0.1, linewidth = 0.25, color = "gray40", inherit.aes = FALSE)+
  geom_line(linewidth = 1)+
  geom_ribbon(aes(x = trial_id, ymin = mean-se, ymax = mean+se, fill = panas_type),
              alpha = 0.3, color = NA)+
  labs(title = "ESM parameters",
       y = "parameter values")+
  facet_wrap(~parameter)+
  scale_color_manual(values = muColor)+
  scale_fill_manual(values = muColor)+
  scale_x_continuous(breaks = seq(0,120,12))+
  theme(legend.position = "none")+
  labs(x = "data point",
       subtitle = "mu overlaid on original mood ratings")
```

```{r}
((p3b/p3)|(p4b/p4))/p1+
  plot_layout(heights = c(3,1))+
  plot_annotation(tag_levels = "A")
ggsave("../figures/figure_s5.png",width = 8, height = 8)
```

### calculated test-retest reliability here
```{r}
summary(lm(scale(mean5_mu_d1r1)~scale(mean5_mu_d2r1),df_master))
summary(lm(scale(mean5_vmu_d1r1)~scale(mean5_vmu_d2r1),df_master))
summary(lm(scale(mean_vmu_d1r1)~scale(mean_vmu_d2r1),df_master))

summary(lm(scale(mean5_s_d1r1)~scale(mean5_s_d2r1),df_master))

summary(lm(scale(moodrate_mssd_day1_block1)~scale(moodrate_mssd_day2_block1),df_master))
summary(lm(scale(moodrate_sd_day1_block1)~scale(moodrate_sd_day2_block1),df_master))
summary(lm(scale(AR_day1_block1)~scale(AR_day2_block1),df_master))

t.test(df_master$mean5_mu_d1r1, df_master$mean5_mu_d2r1, paired = T)
t.test(df_master$mean5_vmu_d1r1, df_master$mean5_vmu_d2r1, paired = T)
t.test(df_master$mean5_s_d1r1, df_master$mean5_s_d2r1, paired = T)
```

```{r}
r_tt_vmu <- cor.test(df_master$mean5_vmu_d1r1, df_master$mean5_vmu_d2r1,
                     use = "complete.obs")
r_tt_s   <- cor.test(df_master$mean5_s_d1r1,   df_master$mean5_s_d2r1,
                     use = "complete.obs")

cat(sprintf("vmu: r = %.3f, 95%% CI [%.3f, %.3f], p = %.4f\n",
            r_tt_vmu$estimate, r_tt_vmu$conf.int[1], r_tt_vmu$conf.int[2], r_tt_vmu$p.value))
cat(sprintf("s:   r = %.3f, 95%% CI [%.3f, %.3f], p = %.4f\n\n",
            r_tt_s$estimate,   r_tt_s$conf.int[1],   r_tt_s$conf.int[2],   r_tt_s$p.value))

# Spearman-Brown corrected reliability for the 2-day average
# r_sb = 2r / (1 + r)  — effective reliability of mean5_vmu
#if I average two measurements instead of using one, how much does reliability improve?
r_sb_vmu <- (2 * r_tt_vmu$estimate) / (1 + r_tt_vmu$estimate)
r_sb_s   <- (2 * r_tt_s$estimate)   / (1 + r_tt_s$estimate)

cat(sprintf("Spearman-Brown reliability of 2-day average vmu: %.3f (up from %.3f)\n",
            r_sb_vmu, r_tt_vmu$estimate))
cat(sprintf("Spearman-Brown reliability of 2-day average s:   %.3f (up from %.3f)\n\n",
            r_sb_s, r_tt_s$estimate))
```

```{r}
# Disattenuated r = r_obs / sqrt(r_xx)
# Correcting only for predictor unreliability (conservative assumption:
# EMA outcome measured without error). If you have EMA split-half / ICC,
# substitute below as r_yy and use: r_obs / sqrt(r_xx * r_yy).
#
# Key logic: if disattenuated r is similar across Day 1, Day 2, and Average,
# all three tap the same true-score association — observed differences reflect
# measurement noise, not a validity problem. The reviewer's swap-Day-2-for-Day-1
# suggestion would not help; only averaging does.

cat("=== ATTENUATION CORRECTION ===\n\n")

r_obs_d1  <- cor(df_master$mean5_vmu_d1r1, df_master$mean5_vmu_posminusneg, use = "complete.obs")
r_obs_d2  <- cor(df_master$mean5_vmu_d2r1, df_master$mean5_vmu_posminusneg, use = "complete.obs")
r_obs_avg <- cor(df_master$mean5_vmu,      df_master$mean5_vmu_posminusneg, use = "complete.obs")

disattenuate <- function(r_obs, r_xx) r_obs / sqrt(r_xx)

r_dis_d1  <- disattenuate(r_obs_d1,  r_tt_vmu$estimate)  # single-day reliability
r_dis_d2  <- disattenuate(r_obs_d2,  r_tt_vmu$estimate)  # single-day reliability
r_dis_avg <- disattenuate(r_obs_avg, r_sb_vmu)            # SB-corrected for 2-day average

cat("Zero-order correlations with EMA vmu outcome:\n")
cat(sprintf("  Day 1:   observed r = %+.3f  ->  disattenuated r = %+.3f  (r_xx = %.3f)\n",
            r_obs_d1,  r_dis_d1,  r_tt_vmu$estimate))
cat(sprintf("  Day 2:   observed r = %+.3f  ->  disattenuated r = %+.3f  (r_xx = %.3f)\n",
            r_obs_d2,  r_dis_d2,  r_tt_vmu$estimate))
cat(sprintf("  Average: observed r = %+.3f  ->  disattenuated r = %+.3f  (r_xx = %.3f, SB)\n\n",
            r_obs_avg, r_dis_avg, r_sb_vmu))
```


# get ICC of parameters
```{r}
get_icc_manual <- function(model) {
  
  vc <- as.data.frame(VarCorr(model))
  
  subject_var <- vc$vcov[vc$grp == "subject"]
  resid_var   <- vc$vcov[vc$grp == "Residual"]
  
  # If singular or no subject variance
  if (length(subject_var) == 0 || subject_var == 0) {
    return(0)
  }
  
  return(subject_var / (subject_var + resid_var))
}
```

### within-session ICC over time (task and ESM params)
```{r}
icc_list_ema <- NULL

for (var in c("s","vmu","mu")){
  for (i in 0:11){
    
    tt <- (i*10+1):(i*10+10)
    
    df_sub <- df_panas_Est_tc %>% 
      filter(panas_type == "posminusneg",
             trial_id %in% tt)
    
    formula <- as.formula(paste0(var," ~ 1 + (1|subject)"))
    
    m <- lmer(formula, df_sub)
    
    icc_value <- get_icc_manual(m)
    
    icc_list_ema <- rbind(icc_list_ema,
                          c(i, var, icc_value))
  }
}

icc_list_ema <- as.data.frame(icc_list_ema)
names(icc_list_ema) <- c("time_sdg","parameter","ICC")
icc_list_ema <- icc_list_ema %>% 
  mutate(time_sdg = factor(as.numeric(time_sdg)),
         ICC = as.numeric(ICC))

icc_list_task1 <- NULL

for (var in c("s","vmu","mu")){
  for (i in 0:7){
    
    tt <- (i*5+1):(i*5+5)
    
    df_sub <- df_gor_Est_tc %>% 
      filter(day_block == "day1_block1",
             trial_id %in% tt)
    
    formula <- as.formula(paste0(var," ~ 1 + (1|subject)"))
    
    m <- lmer(formula, df_sub)
    
    icc_value <- get_icc_manual(m)
    
    icc_list_task1 <- rbind(icc_list_task1,
                            c(i, var, icc_value))
  }
}

icc_list_task1 <- as.data.frame(icc_list_task1)
names(icc_list_task1) <- c("time_sdg","parameter","ICC")
icc_list_task1 <- icc_list_task1 %>% 
  mutate(time_sdg = factor(as.numeric(time_sdg)),
         ICC = as.numeric(ICC))

icc_list_task2 <- NULL

for (var in c("s","vmu","mu")){
  for (i in 0:7){
    
    tt <- (i*5+1):(i*5+5)
    
    df_sub <- df_gor_Est_tc %>% 
      filter(day_block == "day2_block1",
             trial_id %in% tt)
    
    formula <- as.formula(paste0(var," ~ 1 + (1|subject)"))
    
    m <- lmer(formula, df_sub)
    
    icc_value <- get_icc_manual(m)
    
    icc_list_task2 <- rbind(icc_list_task2,
                            c(i, var, icc_value))
  }
}

icc_list_task2 <- as.data.frame(icc_list_task2)
names(icc_list_task2) <- c("time_sdg","parameter","ICC")
icc_list_task2 <- icc_list_task2 %>% 
  mutate(time_sdg = factor(as.numeric(time_sdg)),
         ICC = as.numeric(ICC))


icc_list_task3 <- NULL

for (var in c("s","vmu","mu")){
  for (i in 0:7){
    
    tt <- (i*5+1):(i*5+5)
    
    df_sub <- df_gor_Est_tc %>% 
      filter(day_block %in% c("day1_block1","day2_block1"),
             trial_id %in% tt) %>% 
      group_by(subject,trial_id) %>% summarise_at(vars(mu,s,vmu,kmu,vs),~mean(.x))
    
    formula <- as.formula(paste0(var," ~ 1 + (1|subject)"))
    m <- lmer(formula, df_sub)
    icc_value <- get_icc_manual(m)
    icc_list_task3 <- rbind(icc_list_task3,
                            c(i, var, icc_value))
  }
}

ggplot(icc_list_task1, aes(x = time_sdg,y = ICC,group=parameter,
                     color=parameter))+
  geom_line(size=1)+
  scale_color_manual(values = c(muColor,noiseColor,vmuColor))+
  ylim(0,1)+
  labs(title = "task rating (1st day)",x="trials")+
  scale_x_discrete(breaks = 0:7,
    labels = c("1-5","6-10","11-15","16-20","21-25","26-30","31-35","41-40"))+
  theme(
    legend.position = "left",
    axis.text.x = element_text(angle = 45, hjust = 1)
  ) +
ggplot(icc_list_task2, aes(x = time_sdg,y = ICC,group=parameter,
                     color=parameter))+
  geom_line(size=1)+
  scale_color_manual(values = c(muColor,noiseColor,vmuColor))+
  ylim(0,1)+
  labs(title = "task rating (2nd day)",x="trials")+
  scale_x_discrete(breaks = 0:7,
    labels = c("1-5","6-10","11-15","16-20","21-25","26-30","31-35","41-40"))+
  theme(
    legend.position = "none",
    axis.text.x = element_text(angle = 45, hjust = 1)
  ) +
ggplot(icc_list_ema, aes(x = time_sdg,y = ICC,group=parameter,
                     color=parameter))+
  geom_line(size=1)+
  scale_color_manual(values = c(muColor,noiseColor,vmuColor))+
  ylim(0,1)+
  labs(title = "EMA rating",x="trials")+
  scale_x_discrete(breaks = 0:11,
    labels = c("1-10","11-20","21-30","31-40","41-50","51-60","61-70","71-80","81-90","91-100",
               "101-110","110-120"))+
  theme(
    legend.position = "none",
    axis.text.x = element_text(angle = 45, hjust = 1)
  )+plot_layout(nrow = 1, width = c(1,1,2))
ggsave("../figures/figure_r0_2_1.png",width = 10, height = 4)
```

## between-session ICC of task params
```{r}
icc_list_task_between <- NULL

for (var in c("s","vmu","mu")){
  for (i in 1:41){
    
    df_sub <- df_gor_Est_tc %>% 
      filter(trial_id == i, day_block %in% c("day1_block1","day2_block1"))
    formula <- as.formula(paste0(var," ~ 1 + (1|subject)"))
    
    m <- lmer(formula, df_sub)
    icc_value <- get_icc_manual(m)
    
    icc_list_task_between <- rbind(icc_list_task_between,
                            c(i, var, icc_value))
  }
}

icc_list_task_between <- as.data.frame(icc_list_task_between)
names(icc_list_task_between) <- c("time_sdg","parameter","ICC")
icc_list_task_between <- icc_list_task_between %>% 
  mutate(time_sdg = factor(as.numeric(time_sdg)),
         ICC = as.numeric(ICC))

ggplot(icc_list_task_between, aes(x = time_sdg,y = ICC,group=parameter,
                     color=parameter))+
  geom_line(size=1)+
  scale_color_manual(values = c(muColor,noiseColor,vmuColor))+
  scale_x_discrete(breaks = seq(1,41,5))+
  ylim(0,1)+
  labs(title = "task rating",x="trials")+
  theme(
    legend.position = "left")
```

### within-session ICC of PANAS score
```{r}
df_PANAS_ <- df_PANAS %>% 
  dplyr::select(subject,Trigger.Index,PAminusNA_sum) %>% 
  left_join(df_panas_Est_tc %>% 
              filter(panas_type == "posminusneg") %>% 
              rename(Trigger.Index=trial_id) %>% 
              dplyr::select(subject,Trigger.Index,mu_orig)) %>% 
  rowwise() %>% 
  mutate(PAminusNA_sum_demean = PAminusNA_sum - mu_orig)

icc_list_panas <- NULL

for (var in c("PAminusNA_sum","PAminusNA_sum_demean")){
  for (i in 0:11){
    
    tt <- (i*10+1):(i*10+10)
    
    df_sub <- df_PANAS_ %>% 
      filter(Trigger.Index %in% tt)
    
    formula <- as.formula(paste0(var," ~ 1 + (1|subject)"))
    
    m <- lmer(formula, df_sub)
    
    icc_value <- 1-get_icc_manual(m) #within variance = 1 - between variance
    
    icc_list_panas <- rbind(icc_list_panas,
                          c(i, var, icc_value))
  }
}

icc_list_panas <- as.data.frame(icc_list_panas)
names(icc_list_panas) <- c("time_sdg","parameter","ICC")
icc_list_panas <- icc_list_panas %>% 
  mutate(time_sdg = factor(as.numeric(time_sdg)),
         ICC = as.numeric(ICC))

icc_panas_all = c(1-get_icc_manual(lmer(PAminusNA_sum~1+(1|subject), df_PANAS_)),
                  1-get_icc_manual(lmer(PAminusNA_sum_demean~1+(1|subject), df_PANAS_)))

icc_panas_all

ggplot(icc_list_panas, aes(x = time_sdg,y = ICC,group=parameter,
                     color=parameter))+
  geom_line(size=1)+
  ylim(0,1)+
  labs(title = "ESM rating",x="time points")+
    scale_x_discrete(breaks = 0:11,
    labels = c("1-10","11-20","21-30","31-40","41-50","51-60","61-70","71-80","81-90","91-100",
               "101-110","110-120"))+
  theme(
    legend.position = "left")
```



# 2. mechanism: dependency of affective variability parameters on in-task reward events
```{r}
chart.Correlation(df_master %>% 
                    dplyr::select(X1,X2,X3))
```

### in-task affective variability ~ reward events
```{r}
l1 <- lmer(value ~ regression_coef + (1|subject),df_Xs_scaled_all_long %>% 
            mutate(regression_coef = factor(regression_coef,levels = c("X1","X2","X3"),labels = c("trial -1~3","trial -4~6","trial -7~9"))))

pw<-emmeans::emmeans(l1, pairwise ~ regression_coef, adjust = "tukey")
pw
confint( pairs(pw, adjust = "tukey"), level = 0.95)

l <- as.data.frame(effects::Effect(c("regression_coef"),l1))

p0 <-ggplot(data=l, aes(x = regression_coef, y = fit))+
  geom_jitter(data = df_Xs_scaled_all_long%>% 
            mutate(regression_coef = factor(regression_coef,levels = c("X1","X2","X3"),
                                            labels = c("trial -1~3","trial -4~6","trial -7~9"))),
                   aes(x = regression_coef, y = value), size = 0.3,color = 'pink',alpha = 0.5)+
   geom_point()+
  geom_errorbar(data=l, aes(x = regression_coef, ymin = lower, ymax = upper),
                width = 0.2)+
  labs(x = "Time of affective impact",
       y = expression("Affective impact" ~ beta),
       title = "")+
  geom_hline(yintercept = 0, linetype = "dashed")

#get reg coefs from stepwise approach

s1a <- summary(l1a<-lm(scale(mean5_mu) ~ scale(X1), df_master))
round(confint(l1a, level=0.95),3)
df_master$residuals1[!is.na(df_master$X1)] <- as.vector(residuals(s1a))
s1bb <- summary(l1b<-lm(scale(residuals1) ~ scale(X2), df_master))
round(confint(l1b, level=0.95),3)
df_master$residuals2[!is.na(df_master$X2)] <- as.vector(residuals(s1bb))
s1cc <- summary(l1c<-lm(scale(residuals2) ~ scale(X3), df_master))
round(confint(l1c, level=0.95),3)

s2a <- summary(l2a<-lm(scale(mean5_vmu) ~ scale(X1), df_master))
round(confint(l2a, level=0.95),3)
df_master$residuals1[!is.na(df_master$X1)] <- as.vector(residuals(s2a))
s2bb <- summary(l2b<-lm(scale(residuals1) ~ scale(X2), df_master))
round(confint(l2b, level=0.95),3)
df_master$residuals2[!is.na(df_master$X2)] <- as.vector(residuals(s2bb))
s2cc <- summary(l2c<-lm(scale(residuals2) ~ scale(X3), df_master))
round(confint(l2c, level=0.95),3)

s3a <- summary(l3a<-lm(scale(mean5_s) ~ scale(X1), df_master))
round(confint(l3a, level=0.95),3)
df_master$residuals1[!is.na(df_master$X1)] <- as.vector(residuals(s3a))
s3bb <- summary(l3b<-lm(scale(residuals1) ~ scale(X2), df_master))
round(confint(l3b, level=0.95),3)
df_master$residuals2[!is.na(df_master$X2)] <- as.vector(residuals(s3bb))
s3cc <- summary(l3c<-lm(scale(residuals2) ~ scale(X3), df_master))
round(confint(l3c, level=0.95),3)

bars <- Reduce(rbind,
       list(as.data.frame(rbind(s1a$coefficients[2,],
                                s1bb$coefficients[2,],
                                s1cc$coefficients[2,]))
                          %>% 
              mutate(reg = "task mean"),
            as.data.frame(rbind(s2a$coefficients[2,],
                                s2bb$coefficients[2,],
                                s2cc$coefficients[2,])) %>% 
              mutate(reg = "task volatility"),
            as.data.frame(rbind(s3a$coefficients[2,],
                                s3bb$coefficients[2,],
                                s3cc$coefficients[2,])) %>% 
              mutate(reg = "task noise"))) %>% 
  rownames_to_column() %>% 
  rename(variable = rowname,
         se = `Std. Error`,
         p_val = `Pr(>|t|)`) %>% 
  mutate(sig = ifelse(p_val < .001, "***",
                      ifelse(p_val < .01, "**",
                             ifelse(p_val < .05,"*",
                                    ifelse(p_val < .1,"†","ns")))))

bars$variable <- rep(c("trial -1~3","trial -4~6","trial -7~9"),3)

p1 <- ggplot(bars %>% 
         filter(!grepl("Intercept",variable)) %>% 
         mutate(variable = factor(variable, levels = c("trial -1~3","trial -4~6","trial -7~9")),
                reg = factor(reg,levels = c("task mean","task volatility","task noise") )) %>% 
           filter(reg != "task mean"))+
  geom_col(aes(x = variable, y = Estimate, fill = reg),
           width = 0.5)+
  geom_errorbar(aes(x = variable, ymin = Estimate - se, ymax = Estimate + se),
                width = 0.1)+
  facet_wrap(~reg)+
  scale_fill_manual(values = c(vmuColor,noiseColor))+
  scale_alpha_manual(values = c("1" = 1, "0" = 0.5), guide = "none")+
  labs(y = "Standardized regression weights",
       x = "Time of affective impact")+
  geom_text(aes(x = variable, y = (Estimate + (Estimate) / abs(Estimate) * se  
                                   + (Estimate) / abs(Estimate) * 0.05), label = sig))+
  theme(legend.position = "none")+
  ylim(-0.35,0.9)

p1_mu <- ggplot(bars %>% 
         filter(!grepl("Intercept",variable)) %>% 
         mutate(variable = factor(variable, levels = c("trial -1~3","trial -4~6","trial -7~9")),
                reg = factor(reg,levels = c("task mean","task volatility","task noise") )) %>% 
           filter(reg == "task mean"))+
  geom_col(aes(x = variable, y = Estimate, fill = reg),
           width = 0.5)+
  geom_errorbar(aes(x = variable, ymin = Estimate - se, ymax = Estimate + se),
                width = 0.1)+
  facet_wrap(~reg)+
  scale_fill_manual(values = muColor)+
  scale_alpha_manual(values = c("1" = 1, "0" = 0.5), guide = "none")+
  labs(y = "Standardized regression weights",
       x = "Time of affective impact")+
  geom_text(aes(x = variable, y = (Estimate + (Estimate) / abs(Estimate) * se  
                                   + (Estimate) / abs(Estimate) * 0.05), label = sig))+
  theme(legend.position = "none")+
  ylim(-0.35,0.9)
```

### ESM affective variability ~ reward events
```{r}
s1a <- summary(lm(scale(mean5_mu_posminusneg) ~ scale(X1), df_master))
df_master$residuals1[!is.na(df_master$X1)] <- as.vector(residuals(s1a))
s1bb <- summary(lm(scale(residuals1) ~ scale(X2), df_master))
df_master$residuals2[!is.na(df_master$X2)] <- as.vector(residuals(s1bb))
s1cc <- summary(lm(scale(residuals2) ~ scale(X3), df_master))

s2a <- summary(lm(scale(mean5_vmu_posminusneg) ~ scale(X1), df_master))
df_master$residuals1[!is.na(df_master$X1)] <- as.vector(residuals(s2a))
s2bb <- summary(lm(scale(residuals1) ~ scale(X2), df_master))
df_master$residuals2[!is.na(df_master$X2)] <- as.vector(residuals(s2bb))
s2cc <- summary(lm(scale(residuals2) ~ scale(X3), df_master))
round(confint(lm(scale(residuals2) ~ scale(X3), df_master), level=0.95),3)

s3a <- summary(lm(scale(mean5_s_posminusneg) ~ scale(X1), df_master))
round(confint(lm(scale(mean5_s_posminusneg) ~ scale(X1), df_master), level=0.95),3)
df_master$residuals1[!is.na(df_master$X1)] <- as.vector(residuals(s3a))
s3bb <- summary(lm(scale(residuals1) ~ scale(X2), df_master))
df_master$residuals2[!is.na(df_master$X2)] <- as.vector(residuals(s3bb))
s3cc <- summary(lm(scale(residuals2) ~ scale(X3), df_master))

bars <- Reduce(rbind,
       list(as.data.frame(rbind(s1a$coefficients[2,],
                                s1bb$coefficients[2,],
                                s1cc$coefficients[2,]))
                          %>% 
              mutate(reg = "ESM mean"),
            as.data.frame(rbind(s2a$coefficients[2,],
                                s2bb$coefficients[2,],
                                s2cc$coefficients[2,])) %>% 
              mutate(reg = "ESM volatility"),
            as.data.frame(rbind(s3a$coefficients[2,],
                                s3bb$coefficients[2,],
                                s3cc$coefficients[2,])) %>% 
              mutate(reg = "ESM noise"))) %>% 
  rownames_to_column() %>% 
  rename(variable = rowname,
         se = `Std. Error`,
         p_val = `Pr(>|t|)`) %>% 
  mutate(sig = ifelse(p_val < .001, "***",
                      ifelse(p_val < .01, "**",
                             ifelse(p_val < .05,"*",
                                    ifelse(p_val < .1,"†","ns")))))

bars$variable <- rep(c("trial -1~3","trial -4~6","trial -7~9"),3)

p2 <- ggplot(bars %>% 
         filter(!grepl("Intercept",variable)) %>% 
         mutate(variable = factor(variable, levels = c("trial -1~3","trial -4~6","trial -7~9")),
                reg = factor(reg,levels = c("ESM mean","ESM volatility","ESM noise") )) %>% 
           filter(reg != "ESM mean"))+
  geom_col(aes(x = variable, y = Estimate, fill = reg),
           width = 0.5)+
  geom_errorbar(aes(x = variable, ymin = Estimate - se, ymax = Estimate + se),
                width = 0.1)+
  facet_wrap(~reg)+
  scale_fill_manual(values = c(vmuColor,noiseColor))+
  scale_alpha_manual(values = c("1" = 1, "0" = 0.5), guide = "none")+
  labs(y = "Standardized regression weights",
       x = "Time of affective impact")+
  geom_text(aes(x = variable, 
                y = (Estimate + (Estimate) / abs(Estimate) * se  + (Estimate) / abs(Estimate) * 0.05), label = sig))+
  theme(legend.position = "none")+
  ylim(-0.35,0.85)

p2_mu <- ggplot(bars %>% 
         filter(!grepl("Intercept",variable)) %>% 
         mutate(variable = factor(variable, levels = c("trial -1~3","trial -4~6","trial -7~9")),
                reg = factor(reg,levels = c("ESM mean","ESM volatility","ESM noise") )) %>% 
           filter(reg == "ESM mean"))+
  geom_col(aes(x = variable, y = Estimate, fill = reg),
           width = 0.5)+
  geom_errorbar(aes(x = variable, ymin = Estimate - se, ymax = Estimate + se),
                width = 0.1)+
  facet_wrap(~reg)+
  scale_fill_manual(values = muColor)+
  scale_alpha_manual(values = c("1" = 1, "0" = 0.5), guide = "none")+
  labs(y = "Standardized regression weights",
       x = "Time of affective impact")+
  geom_text(aes(x = variable, 
                y = (Estimate + (Estimate) / abs(Estimate) * se  + (Estimate) / abs(Estimate) * 0.05), label = sig))+
  theme(legend.position = "none")+
  ylim(-0.35,0.85)

p0+(p1/p2)+
  plot_annotation(tag_levels = "A")+
  plot_layout(width = c(1,2))

ggsave("../figures/figure_4.png",width = 7, height = 5)
ggsave("../figures/figure_4.pdf", width = 7, height = 5, dpi = 300)
```

### also plot how mu relates to affective impact
```{r}
p1_mu+p2_mu

#ggsave("../figures/figure_4_s.png",width = 7, height = 3)
```

### additional test required by reviewer (additional test of summing 3 rewards)
```{r}
cor(df_Xs_scaled_sum_all_long$value,df_Xs_scaled_all_long$value,use = "complete.obs")
pcor<-df_master %>%
  pivot_longer(
    cols = c(X1, X2, X3),
    names_to = "coef_type",
    values_to = "value_separate"
  ) %>%
  mutate(
    value_summed = case_when(
      coef_type == "X1" ~ X1_sum,
      coef_type == "X2" ~ X2_sum,
      coef_type == "X3" ~ X3_sum
    ),
    coef_type = factor(coef_type, levels = c("X1", "X2", "X3"),
                       labels = c("trial -1~3", "trial -4~6", "trial -7~9"))
  ) %>%
  ggplot(aes(x = value_summed, y = value_separate)) +
  geom_point() +
  geom_smooth(method = "lm", se = TRUE) +
  stat_cor(aes(label = after_stat(r.label)), 
         label.x.npc = 0.5, label.y.npc = 0.95)+
  facet_wrap(~ coef_type) +
  labs(
    x = expression(beta ~ "(summed reward outcome)"),
    y = expression(beta ~ "(separate reward outcome)"),
    title = "Different calculation of affective impact"
  )

```

```{r}
l1 <- lmer(value ~ regression_coef + (1|subject),df_Xs_scaled_sum_all_long %>% 
            mutate(regression_coef = factor(regression_coef,levels = c("X1_sum","X2_sum","X3_sum"),labels = c("trial -1~3","trial -4~6","trial -7~9"))))

l <- as.data.frame(effects::Effect(c("regression_coef"),l1))

p0 <-ggplot(data=l, aes(x = regression_coef, y = fit))+
  geom_jitter(data = df_Xs_scaled_sum_all_long%>% 
            mutate(regression_coef = factor(regression_coef,levels = c("X1_sum","X2_sum","X3_sum"),
                                            labels = c("trial -1~3","trial -4~6","trial -7~9"))),
                   aes(x = regression_coef, y = value), size = 0.3,color = 'pink',alpha = 0.5)+
   geom_point()+
  geom_errorbar(data=l, aes(x = regression_coef, ymin = lower, ymax = upper),
                width = 0.2)+
  labs(x = "Time of affective impact",
       y = expression("Affective impact" ~ beta),
       title = "")+
  geom_hline(yintercept = 0, linetype = "dashed")

#get reg coefs from stepwise approach

s1a <- summary(l1a<-lm(scale(mean5_mu) ~ scale(X1_sum), df_master))
round(confint(l1a, level=0.95),3)
df_master$residuals1[!is.na(df_master$X1_sum)] <- as.vector(residuals(s1a))
s1bb <- summary(l1b<-lm(scale(residuals1) ~ scale(X2_sum), df_master))
round(confint(l1b, level=0.95),3)
df_master$residuals2[!is.na(df_master$X2_sum)] <- as.vector(residuals(s1bb))
s1cc <- summary(l1c<-lm(scale(residuals2) ~ scale(X3_sum), df_master))
round(confint(l1c, level=0.95),3)

s2a <- summary(l2a<-lm(scale(mean5_vmu) ~ scale(X1_sum), df_master))
round(confint(l2a, level=0.95),3)
df_master$residuals1[!is.na(df_master$X1_sum)] <- as.vector(residuals(s2a))
s2bb <- summary(l2b<-lm(scale(residuals1) ~ scale(X2_sum), df_master))
round(confint(l2b, level=0.95),3)
df_master$residuals2[!is.na(df_master$X2_sum)] <- as.vector(residuals(s2bb))
s2cc <- summary(l2c<-lm(scale(residuals2) ~ scale(X3_sum), df_master))
round(confint(l2c, level=0.95),3)

s3a <- summary(l3a<-lm(scale(mean5_s) ~ scale(X1_sum), df_master))
round(confint(l3a, level=0.95),3)
df_master$residuals1[!is.na(df_master$X1_sum)] <- as.vector(residuals(s3a))
s3bb <- summary(l3b<-lm(scale(residuals1) ~ scale(X2_sum), df_master))
round(confint(l3b, level=0.95),3)
df_master$residuals2[!is.na(df_master$X2_sum)] <- as.vector(residuals(s3bb))
s3cc <- summary(l3c<-lm(scale(residuals2) ~ scale(X3_sum), df_master))
round(confint(l3c, level=0.95),3)

bars <- Reduce(rbind,
       list(as.data.frame(rbind(s1a$coefficients[2,],
                                s1bb$coefficients[2,],
                                s1cc$coefficients[2,]))
                          %>% 
              mutate(reg = "task mean"),
            as.data.frame(rbind(s2a$coefficients[2,],
                                s2bb$coefficients[2,],
                                s2cc$coefficients[2,])) %>% 
              mutate(reg = "task volatility"),
            as.data.frame(rbind(s3a$coefficients[2,],
                                s3bb$coefficients[2,],
                                s3cc$coefficients[2,])) %>% 
              mutate(reg = "task noise"))) %>% 
  rownames_to_column() %>% 
  rename(variable = rowname,
         se = `Std. Error`,
         p_val = `Pr(>|t|)`) %>% 
  mutate(sig = ifelse(p_val < .001, "***",
                      ifelse(p_val < .01, "**",
                             ifelse(p_val < .05,"*",
                                    ifelse(p_val < .1,"†","ns")))))

bars$variable <- rep(c("trial -1~3","trial -4~6","trial -7~9"),3)

p1 <- ggplot(bars %>% 
         filter(!grepl("Intercept",variable)) %>% 
         mutate(variable = factor(variable, levels = c("trial -1~3","trial -4~6","trial -7~9")),
                reg = factor(reg,levels = c("task mean","task volatility","task noise") )) %>% 
           filter(reg != "task mean"))+
  geom_col(aes(x = variable, y = Estimate, fill = reg),
           width = 0.5)+
  geom_errorbar(aes(x = variable, ymin = Estimate - se, ymax = Estimate + se),
                width = 0.1)+
  facet_wrap(~reg)+
  scale_fill_manual(values = c(vmuColor,noiseColor))+
  scale_alpha_manual(values = c("1" = 1, "0" = 0.5), guide = "none")+
  labs(y = "Standardized regression weights",
       x = "Time of affective impact")+
  geom_text(aes(x = variable, y = (Estimate + (Estimate) / abs(Estimate) * se  
                                   + (Estimate) / abs(Estimate) * 0.05), label = sig))+
  theme(legend.position = "none")+
  ylim(-0.35,0.9)

p1_mu <- ggplot(bars %>% 
         filter(!grepl("Intercept",variable)) %>% 
         mutate(variable = factor(variable, levels = c("trial -1~3","trial -4~6","trial -7~9")),
                reg = factor(reg,levels = c("task mean","task volatility","task noise") )) %>% 
           filter(reg == "task mean"))+
  geom_col(aes(x = variable, y = Estimate, fill = reg),
           width = 0.5)+
  geom_errorbar(aes(x = variable, ymin = Estimate - se, ymax = Estimate + se),
                width = 0.1)+
  facet_wrap(~reg)+
  scale_fill_manual(values = muColor)+
  scale_alpha_manual(values = c("1" = 1, "0" = 0.5), guide = "none")+
  labs(y = "Standardized regression weights",
       x = "Time of affective impact")+
  geom_text(aes(x = variable, y = (Estimate + (Estimate) / abs(Estimate) * se  
                                   + (Estimate) / abs(Estimate) * 0.05), label = sig))+
  theme(legend.position = "none")+
  ylim(-0.35,0.9)
```

### ESM affective variability ~ reward events (additional test of summing 3 rewards)
```{r}
s1a <- summary(lm(scale(mean5_mu_posminusneg) ~ scale(X1_sum), df_master))
df_master$residuals1[!is.na(df_master$X1_sum)] <- as.vector(residuals(s1a))
s1bb <- summary(lm(scale(residuals1) ~ scale(X2_sum), df_master))
df_master$residuals2[!is.na(df_master$X2_sum)] <- as.vector(residuals(s1bb))
s1cc <- summary(lm(scale(residuals2) ~ scale(X3_sum), df_master))

s2a <- summary(lm(scale(mean5_vmu_posminusneg) ~ scale(X1_sum), df_master))
df_master$residuals1[!is.na(df_master$X1_sum)] <- as.vector(residuals(s2a))
s2bb <- summary(lm(scale(residuals1) ~ scale(X2_sum), df_master))
df_master$residuals2[!is.na(df_master$X2_sum)] <- as.vector(residuals(s2bb))
s2cc <- summary(lm(scale(residuals2) ~ scale(X3_sum), df_master))
round(confint(lm(scale(residuals2) ~ scale(X3_sum), df_master), level=0.95),3)

s3a <- summary(lm(scale(mean5_s_posminusneg) ~ scale(X1_sum), df_master))
round(confint(lm(scale(mean5_s_posminusneg) ~ scale(X1_sum), df_master), level=0.95),3)
df_master$residuals1[!is.na(df_master$X1_sum)] <- as.vector(residuals(s3a))
s3bb <- summary(lm(scale(residuals1) ~ scale(X2_sum), df_master))
df_master$residuals2[!is.na(df_master$X2_sum)] <- as.vector(residuals(s3bb))
s3cc <- summary(lm(scale(residuals2) ~ scale(X3_sum), df_master))

bars <- Reduce(rbind,
       list(as.data.frame(rbind(s1a$coefficients[2,],
                                s1bb$coefficients[2,],
                                s1cc$coefficients[2,]))
                          %>% 
              mutate(reg = "ESM mean"),
            as.data.frame(rbind(s2a$coefficients[2,],
                                s2bb$coefficients[2,],
                                s2cc$coefficients[2,])) %>% 
              mutate(reg = "ESM volatility"),
            as.data.frame(rbind(s3a$coefficients[2,],
                                s3bb$coefficients[2,],
                                s3cc$coefficients[2,])) %>% 
              mutate(reg = "ESM noise"))) %>% 
  rownames_to_column() %>% 
  rename(variable = rowname,
         se = `Std. Error`,
         p_val = `Pr(>|t|)`) %>% 
  mutate(sig = ifelse(p_val < .001, "***",
                      ifelse(p_val < .01, "**",
                             ifelse(p_val < .05,"*",
                                    ifelse(p_val < .1,"†","ns")))))

bars$variable <- rep(c("trial -1~3","trial -4~6","trial -7~9"),3)

p2 <- ggplot(bars %>% 
         filter(!grepl("Intercept",variable)) %>% 
         mutate(variable = factor(variable, levels = c("trial -1~3","trial -4~6","trial -7~9")),
                reg = factor(reg,levels = c("ESM mean","ESM volatility","ESM noise") )) %>% 
           filter(reg != "ESM mean"))+
  geom_col(aes(x = variable, y = Estimate, fill = reg),
           width = 0.5)+
  geom_errorbar(aes(x = variable, ymin = Estimate - se, ymax = Estimate + se),
                width = 0.1)+
  facet_wrap(~reg)+
  scale_fill_manual(values = c(vmuColor,noiseColor))+
  scale_alpha_manual(values = c("1" = 1, "0" = 0.5), guide = "none")+
  labs(y = "Standardized regression weights",
       x = "Time of affective impact")+
  geom_text(aes(x = variable, 
                y = (Estimate + (Estimate) / abs(Estimate) * se  + (Estimate) / abs(Estimate) * 0.05), label = sig))+
  theme(legend.position = "none")+
  ylim(-0.35,0.85)

p2_mu <- ggplot(bars %>% 
         filter(!grepl("Intercept",variable)) %>% 
         mutate(variable = factor(variable, levels = c("trial -1~3","trial -4~6","trial -7~9")),
                reg = factor(reg,levels = c("ESM mean","ESM volatility","ESM noise") )) %>% 
           filter(reg == "ESM mean"))+
  geom_col(aes(x = variable, y = Estimate, fill = reg),
           width = 0.5)+
  geom_errorbar(aes(x = variable, ymin = Estimate - se, ymax = Estimate + se),
                width = 0.1)+
  facet_wrap(~reg)+
  scale_fill_manual(values = muColor)+
  scale_alpha_manual(values = c("1" = 1, "0" = 0.5), guide = "none")+
  labs(y = "Standardized regression weights",
       x = "Time of affective impact")+
  geom_text(aes(x = variable, 
                y = (Estimate + (Estimate) / abs(Estimate) * se  + (Estimate) / abs(Estimate) * 0.05), label = sig))+
  theme(legend.position = "none")+
  ylim(-0.35,0.85)

pcor/
(p0+(p1/p2)+
  plot_layout(width = c(1,2)))+
  plot_layout(heights = c(1,2))+
  plot_annotation(tag_levels = "A")

ggsave("../figures/figure_r1_9_1.png",width = 7, height = 7)
```
### each beta separately
```{r}
s1a <- summary(lm(scale(mean5_mu) ~ scale(X1), df_master))
s1b <- summary(lm(scale(mean5_mu) ~ scale(X2), df_master))
s1c <- summary(lm(scale(mean5_mu) ~ scale(X3), df_master))

s2a <- summary(lm(scale(mean5_vmu) ~ scale(X1), df_master))
s2b <- summary(lm(scale(mean5_vmu) ~ scale(X2), df_master))
s2c <- summary(lm(scale(mean5_vmu) ~ scale(X3), df_master))

s3a <- summary(lm(scale(mean5_s) ~ scale(X1), df_master))
s3b <- summary(lm(scale(mean5_s) ~ scale(X2), df_master))
s3c <- summary(lm(scale(mean5_s) ~ scale(X3), df_master))


bars <- Reduce(rbind,
       list(as.data.frame(s1a$coefficients) %>% 
              mutate(reg = "task mean"),
            as.data.frame(s1b$coefficients) %>% 
              mutate(reg = "task mean"),
            as.data.frame(s1c$coefficients) %>% 
              mutate(reg = "task mean"),
            as.data.frame(s2a$coefficients) %>% 
              mutate(reg = "task volatility"),
            as.data.frame(s2b$coefficients) %>% 
              mutate(reg = "task volatility"),
            as.data.frame(s2c$coefficients) %>% 
              mutate(reg = "task volatility"),
            as.data.frame(s3a$coefficients) %>% 
              mutate(reg = "task noise"),
            as.data.frame(s3b$coefficients) %>% 
              mutate(reg = "task noise"),
            as.data.frame(s3c$coefficients) %>% 
              mutate(reg = "task noise"))) %>% 
  rownames_to_column() %>% 
  rename(variable = rowname,
         se = `Std. Error`,
         p_val = `Pr(>|t|)`) %>% 
  mutate(sig = ifelse(p_val < .001, "***",
                      ifelse(p_val < .01, "**",
                             ifelse(p_val < .05,"*",
                                    ifelse(p_val < .1,"†","ns")))))

bars$variable[grepl("X1",bars$variable)] <- "trial -1~3"
bars$variable[grepl("X2",bars$variable)] <- "trial -4~6"
bars$variable[grepl("X3",bars$variable)] <- "trial -7~9"

p1 <- ggplot(bars %>% 
         filter(!grepl("Intercept",variable)) %>% 
         mutate(variable = factor(variable, levels = c("trial -1~3","trial -4~6","trial -7~9")),
                reg = factor(reg,levels = c("task mean","task volatility","task noise") )) %>% 
           filter(reg != "task mean"))+
  geom_col(aes(x = variable, y = Estimate, fill = reg),
           width = 0.5)+
  geom_errorbar(aes(x = variable, ymin = Estimate - se, ymax = Estimate + se),
                width = 0.1)+
  facet_wrap(~reg)+
  scale_fill_manual(values = c(vmuColor,noiseColor))+
  scale_alpha_manual(values = c("1" = 1, "0" = 0.5), guide = "none")+
  labs(y = "Standardized regression weights",
       x = "Time of affective impact",
       title = "Separate regression models")+
  geom_text(aes(x = variable, y = (Estimate + (Estimate) / abs(Estimate) * se  
                                   + (Estimate) / abs(Estimate) * 0.05), label = sig))+
  theme(legend.position = "none")+
  ylim(-0.4,0.85)

s1a <- summary(lm(scale(mean5_mu_posminusneg) ~ scale(X1), df_master))
s1b <- summary(lm(scale(mean5_mu_posminusneg) ~ scale(X2), df_master))
s1c <- summary(lm(scale(mean5_mu_posminusneg) ~ scale(X3), df_master))

s2a <- summary(lm(scale(mean5_vmu_posminusneg) ~ scale(X1), df_master))
s2b <- summary(lm(scale(mean5_vmu_posminusneg) ~ scale(X2), df_master))
s2c <- summary(lm(scale(mean5_vmu_posminusneg) ~ scale(X3), df_master))

s3a <- summary(lm(scale(mean5_s_posminusneg) ~ scale(X1), df_master))
s3b <- summary(lm(scale(mean5_s_posminusneg) ~ scale(X2), df_master))
s3c <- summary(lm(scale(mean5_s_posminusneg) ~ scale(X3), df_master))

bars <- Reduce(rbind,
       list(as.data.frame(s1a$coefficients) %>% 
              mutate(reg = "ESM mean"),
            as.data.frame(s1b$coefficients) %>% 
              mutate(reg = "ESM mean"),
            as.data.frame(s1c$coefficients) %>% 
              mutate(reg = "ESM mean"),
            as.data.frame(s2a$coefficients) %>% 
              mutate(reg = "ESM volatility"),
            as.data.frame(s2b$coefficients) %>% 
              mutate(reg = "ESM volatility"),
            as.data.frame(s2c$coefficients) %>% 
              mutate(reg = "ESM volatility"),
            as.data.frame(s3a$coefficients) %>% 
              mutate(reg = "ESM noise"),
            as.data.frame(s3b$coefficients) %>% 
              mutate(reg = "ESM noise"),
            as.data.frame(s3c$coefficients) %>% 
              mutate(reg = "ESM noise"))) %>% 
  rownames_to_column() %>% 
  rename(variable = rowname,
         se = `Std. Error`,
         p_val = `Pr(>|t|)`) %>% 
  mutate(sig = ifelse(p_val < .001, "***",
                      ifelse(p_val < .01, "**",
                             ifelse(p_val < .05,"*",
                                    ifelse(p_val < .1,"†","ns")))))

bars$variable[grepl("X1",bars$variable)] <- "trial -1~3"
bars$variable[grepl("X2",bars$variable)] <- "trial -4~6"
bars$variable[grepl("X3",bars$variable)] <- "trial -7~9"

p2 <- ggplot(bars %>% 
         filter(!grepl("Intercept",variable)) %>% 
         mutate(variable = factor(variable, levels = c("trial -1~3","trial -4~6","trial -7~9")),
                reg = factor(reg,levels = c("ESM mean","ESM volatility","ESM noise") )) %>% 
           filter(reg != "ESM mean"))+
  geom_col(aes(x = variable, y = Estimate, fill = reg),
           width = 0.5)+
  geom_errorbar(aes(x = variable, ymin = Estimate - se, ymax = Estimate + se),
                width = 0.1)+
  facet_wrap(~reg)+
  scale_fill_manual(values = c(vmuColor,noiseColor))+
  scale_alpha_manual(values = c("1" = 1, "0" = 0.5), guide = "none")+
  labs(y = "Standardized regression weights",
       x = "Time of affective impact",
       title = "Separate regression models")+
  geom_text(aes(x = variable, 
                y = (Estimate + (Estimate) / abs(Estimate) * se  + (Estimate) / abs(Estimate) * 0.05), label = sig))+
  theme(legend.position = "none")+
  ylim(-0.4,0.8)

(p1/p2)+
  plot_annotation(tag_levels = "A")

ggsave("../figures/figure_s15.png",width = 6, height = 7)
```

### same analysis, while also considering magnitude (supplementary)
```{r}
l1 <- lmer(value ~ regression_coef + (1|subject),df_Xs_scaled_all2_long %>% 
            mutate(regression_coef = factor(regression_coef,levels = c("X1mo","X2mo","X3mo"),labels = c("trial -1~3","trial -4~6","trial -7~9"))) %>% 
             filter(!is.na(regression_coef)))

summary(l1)


l2 <- lmer(value ~ regression_coef + (1|subject),df_Xs_scaled_all2_long %>% 
            mutate(regression_coef = factor(regression_coef,levels = c("X1o","X2o","X3o"),labels = c("trial -1~3","trial -4~6","trial -7~9"))) %>% 
             filter(!is.na(regression_coef)))

summary(l2)

l <- as.data.frame(effects::Effect(c("regression_coef"),l1))
l_ <- as.data.frame(effects::Effect(c("regression_coef"),l2))
p0 <-ggplot(data=l, aes(x = regression_coef, y = fit))+
  geom_jitter(data = df_Xs_scaled_all2_long%>% 
            mutate(regression_coef = factor(regression_coef,levels = c("X1mo","X2mo","X3mo"),labels = c("trial -1~3","trial -4~6","trial -7~9"))) %>% 
                     filter(!is.na(regression_coef)),
                   aes(x = regression_coef, y = value), size = 0.3,color = 'pink',alpha = 0.5)+
   geom_point()+
  geom_errorbar(data=l, aes(x = regression_coef, ymin = lower, ymax = upper),
                width = 0.2)+
  labs(x = "Time of affective impact",
       title = "Reward magnitude (-4~5)")+
  geom_hline(yintercept = 0, linetype = "dashed")+
ggplot(data=l_, aes(x = regression_coef, y = fit))+
  geom_jitter(data = df_Xs_scaled_all2_long%>% 
            mutate(regression_coef = factor(regression_coef,levels = c("X1o","X2o","X3o"),labels = c("trial -1~3","trial -4~6","trial -7~9")))%>% 
                     filter(!is.na(regression_coef)),
                   aes(x = regression_coef, y = value), size = 0.3,color = 'pink',alpha = 0.5)+
   geom_point()+
  geom_errorbar(data=l_, aes(x = regression_coef, ymin = lower, ymax = upper),
                width = 0.2)+
  labs(x = "Time of affective impact",
       title = "Binary reward outcome (0 or 1)")+
  geom_hline(yintercept = 0, linetype = "dashed")

s1a <- summary(lm(scale(mean5_mu) ~ scale(X1mo), df_master))
s2a <- summary(lm(scale(mean5_vmu) ~ scale(X1mo), df_master))
s3a <- summary(lm(scale(mean5_s) ~ scale(X1mo), df_master))


df_master$residuals1[!is.na(df_master$X1mo)] <- as.vector(residuals(s1a))
s1bb <- summary(lm(scale(residuals1) ~ scale(X2mo), df_master))
df_master$residuals2[!is.na(df_master$X2mo)] <- as.vector(residuals(s1bb))
s1cc <- summary(lm(scale(residuals2) ~ scale(X3mo), df_master))

df_master$residuals1[!is.na(df_master$X1mo)] <- as.vector(residuals(s2a))
s2bb <- summary(lm(scale(residuals1) ~ scale(X2mo), df_master))
df_master$residuals2[!is.na(df_master$X2mo)] <- as.vector(residuals(s2bb))
s2cc <- summary(lm(scale(residuals2) ~ scale(X3mo), df_master))

df_master$residuals1[!is.na(df_master$X1mo)] <- as.vector(residuals(s3a))
s3bb <- summary(lm(scale(residuals1) ~ scale(X2mo), df_master))
df_master$residuals2[!is.na(df_master$X2mo)] <- as.vector(residuals(s3bb))
s3cc <- summary(lm(scale(residuals2) ~ scale(X3mo), df_master))

bars <- Reduce(rbind,
       list(as.data.frame(rbind(s1a$coefficients[2,],
                                s1bb$coefficients[2,],
                                s1cc$coefficients[2,]))
                          %>% 
              mutate(reg = "task mean"),
            as.data.frame(rbind(s2a$coefficients[2,],
                                s2bb$coefficients[2,],
                                s2cc$coefficients[2,])) %>% 
              mutate(reg = "task volatility"),
            as.data.frame(rbind(s3a$coefficients[2,],
                                s3bb$coefficients[2,],
                                s3cc$coefficients[2,])) %>% 
              mutate(reg = "task noise"))) %>% 
  rownames_to_column() %>% 
  rename(variable = rowname,
         se = `Std. Error`,
         p_val = `Pr(>|t|)`) %>% 
  mutate(sig = ifelse(p_val < .001, "***",
                      ifelse(p_val < .01, "**",
                             ifelse(p_val < .05,"*",
                                    ifelse(p_val < .1,"†","ns")))))

bars$variable <- rep(c("trial -1~3","trial -4~6","trial -7~9"),3)

p1mo <- ggplot(bars %>% 
         filter(!grepl("Intercept",variable)) %>% 
         mutate(variable = factor(variable, levels = c("trial -1~3","trial -4~6","trial -7~9")),
                reg = factor(reg,levels = c("task mean","task volatility","task noise") )) %>% 
           filter(reg != "task mean"))+
  geom_col(aes(x = variable, y = Estimate, fill = reg),
           width = 0.5)+
  geom_errorbar(aes(x = variable, ymin = Estimate - se, ymax = Estimate + se),
                width = 0.1)+
  facet_wrap(~reg)+
  scale_fill_manual(values = c(vmuColor,noiseColor))+
  scale_alpha_manual(values = c("1" = 1, "0" = 0.5), guide = "none")+
  labs(y = "Standardized regression weights",
       x = "Time of affective impact",
       title = "Reward magnitude")+
  geom_text(aes(x = variable, y = (Estimate + (Estimate) / abs(Estimate) * se  
                                   + (Estimate) / abs(Estimate) * 0.05), label = sig))+
  theme(legend.position = "none")+
  ylim(-0.35,0.85)+ 
  theme(axis.text.x = element_text(angle = 45))

s1a <- summary(lm(scale(mean5_mu_posminusneg) ~ scale(X1mo), df_master))
s2a <- summary(lm(scale(mean5_vmu_posminusneg) ~ scale(X1mo), df_master))
s3a <- summary(lm(scale(mean5_s_posminusneg) ~ scale(X1mo), df_master))


df_master$residuals1[!is.na(df_master$X1mo)] <- as.vector(residuals(s1a))
s1bb <- summary(lm(scale(residuals1) ~ scale(X2mo), df_master))
df_master$residuals2[!is.na(df_master$X2mo)] <- as.vector(residuals(s1bb))
s1cc <- summary(lm(scale(residuals2) ~ scale(X3mo), df_master))

df_master$residuals1[!is.na(df_master$X1mo)] <- as.vector(residuals(s2a))
s2bb <- summary(lm(scale(residuals1) ~ scale(X2mo), df_master))
df_master$residuals2[!is.na(df_master$X2mo)] <- as.vector(residuals(s2bb))
s2cc <- summary(lm(scale(residuals2) ~ scale(X3mo), df_master))

df_master$residuals1[!is.na(df_master$X1mo)] <- as.vector(residuals(s3a))
s3bb <- summary(lm(scale(residuals1) ~ scale(X2mo), df_master))
df_master$residuals2[!is.na(df_master$X2mo)] <- as.vector(residuals(s3bb))
s3cc <- summary(lm(scale(residuals2) ~ scale(X3mo), df_master))

bars <- Reduce(rbind,
       list(as.data.frame(rbind(s1a$coefficients[2,],
                                s1bb$coefficients[2,],
                                s1cc$coefficients[2,]))
                          %>% 
              mutate(reg = "ESM mean"),
            as.data.frame(rbind(s2a$coefficients[2,],
                                s2bb$coefficients[2,],
                                s2cc$coefficients[2,])) %>% 
              mutate(reg = "ESM volatility"),
            as.data.frame(rbind(s3a$coefficients[2,],
                                s3bb$coefficients[2,],
                                s3cc$coefficients[2,])) %>% 
              mutate(reg = "ESM noise"))) %>% 
  rownames_to_column() %>% 
  rename(variable = rowname,
         se = `Std. Error`,
         p_val = `Pr(>|t|)`) %>% 
  mutate(sig = ifelse(p_val < .001, "***",
                      ifelse(p_val < .01, "**",
                             ifelse(p_val < .05,"*",
                                    ifelse(p_val < .1,"†","ns")))))

bars$variable <- rep(c("trial -1~3","trial -4~6","trial -7~9"),3)

p2mo <- ggplot(bars %>% 
         filter(!grepl("Intercept",variable)) %>% 
         mutate(variable = factor(variable, levels = c("trial -1~3","trial -4~6","trial -7~9")),
                reg = factor(reg,levels = c("ESM mean","ESM volatility","ESM noise") )) %>% 
           filter(reg != "ESM mean"))+
  geom_col(aes(x = variable, y = Estimate, fill = reg),
           width = 0.5)+
  geom_errorbar(aes(x = variable, ymin = Estimate - se, ymax = Estimate + se),
                width = 0.1)+
  facet_wrap(~reg)+
  scale_fill_manual(values = c(vmuColor,noiseColor))+
  scale_alpha_manual(values = c("1" = 1, "0" = 0.5), guide = "none")+
  labs(y = "Standardized regression weights",
       x = "Time of affective impact",
       title = "Reward magnitude")+
  geom_text(aes(x = variable, y = (Estimate + (Estimate) / abs(Estimate) * se  
                                   + (Estimate) / abs(Estimate) * 0.05), label = sig))+
  theme(legend.position = "none")+
  ylim(-0.35,0.85)+ 
  theme(axis.text.x = element_text(angle = 45))

p0
ggsave("../figures/figure_s16.png",width = 6, height = 3)
```


```{r}
l1 <- lmer(value ~ regression_coef + (1|subject),df_Xs_scaled_all2_long %>% 
            mutate(regression_coef = factor(regression_coef,levels = c("X1o","X2o","X3o"),labels = c("trial -1~3","trial -4~6","trial -7~9"))) %>% 
             filter(!is.na(regression_coef)))

summary(l1)

p0 <- plot_model(l1, "pred",terms = "regression_coef",
           show.data = T, jitter = T, dot.size = 0.7,ci.style = "bar")+
  labs(x = "Time of affective impact",
       title = "binary outcome")+
  geom_hline(yintercept = 0, linetype = "dashed")

s1a <- summary(lm(scale(mean5_mu) ~ scale(X1o), df_master))
s2a <- summary(lm(scale(mean5_vmu) ~ scale(X1o), df_master))
s3a <- summary(lm(scale(mean5_s) ~ scale(X1o), df_master))

df_master$residuals1[!is.na(df_master$X1o)] <- as.vector(residuals(s1a))
s1bb <- summary(lm(scale(residuals1) ~ scale(X2o), df_master))
df_master$residuals2[!is.na(df_master$X2o)] <- as.vector(residuals(s1bb))
s1cc <- summary(lm(scale(residuals2) ~ scale(X3o), df_master))

df_master$residuals1[!is.na(df_master$X1o)] <- as.vector(residuals(s2a))
s2bb <- summary(lm(scale(residuals1) ~ scale(X2o), df_master))
df_master$residuals2[!is.na(df_master$X2o)] <- as.vector(residuals(s2bb))
s2cc <- summary(lm(scale(residuals2) ~ scale(X3o), df_master))

df_master$residuals1[!is.na(df_master$X1o)] <- as.vector(residuals(s3a))
s3bb <- summary(lm(scale(residuals1) ~ scale(X2o), df_master))
df_master$residuals2[!is.na(df_master$X2o)] <- as.vector(residuals(s3bb))
s3cc <- summary(lm(scale(residuals2) ~ scale(X3o), df_master))

bars <- Reduce(rbind,
       list(as.data.frame(rbind(s1a$coefficients[2,],
                                s1bb$coefficients[2,],
                                s1cc$coefficients[2,]))
                          %>% 
              mutate(reg = "task mean"),
            as.data.frame(rbind(s2a$coefficients[2,],
                                s2bb$coefficients[2,],
                                s2cc$coefficients[2,])) %>% 
              mutate(reg = "task volatility"),
            as.data.frame(rbind(s3a$coefficients[2,],
                                s3bb$coefficients[2,],
                                s3cc$coefficients[2,])) %>% 
              mutate(reg = "task noise"))) %>% 
  rownames_to_column() %>% 
  rename(variable = rowname,
         se = `Std. Error`,
         p_val = `Pr(>|t|)`) %>% 
  mutate(sig = ifelse(p_val < .001, "***",
                      ifelse(p_val < .01, "**",
                             ifelse(p_val < .05,"*",
                                    ifelse(p_val < .1,"†","ns")))))

bars$variable <- rep(c("trial -1~3","trial -4~6","trial -7~9"),3)

p1o <- ggplot(bars %>% 
         filter(!grepl("Intercept",variable)) %>% 
         mutate(variable = factor(variable, levels = c("trial -1~3","trial -4~6","trial -7~9")),
                reg = factor(reg,levels = c("task mean","task volatility","task noise") )) %>% 
           filter(reg != "task mean"))+
  geom_col(aes(x = variable, y = Estimate, fill = reg),
           width = 0.5)+
  geom_errorbar(aes(x = variable, ymin = Estimate - se, ymax = Estimate + se),
                width = 0.1)+
  facet_wrap(~reg)+
  scale_fill_manual(values = c(vmuColor,noiseColor))+
  scale_alpha_manual(values = c("1" = 1, "0" = 0.5), guide = "none")+
  labs(y = "Standardized regression weights",
       x = "Time of affective impact",
       title = "Reward outcome")+
  geom_text(aes(x = variable, y = (Estimate + (Estimate) / abs(Estimate) * se  
                                   + (Estimate) / abs(Estimate) * 0.05), label = sig))+
  theme(legend.position = "none")+
  ylim(-0.35,0.85)+ 
  theme(axis.text.x = element_text(angle = 45))

p1o_mu<-ggplot(bars %>% 
         filter(!grepl("Intercept",variable)) %>% 
         mutate(variable = factor(variable, levels = c("trial -1~3","trial -4~6","trial -7~9")),
                reg = factor(reg,levels = c("task mean","task volatility","task noise") )) %>% 
           filter(reg == "task mean"))+
  geom_col(aes(x = variable, y = Estimate, fill = reg),
           width = 0.5)+
  geom_errorbar(aes(x = variable, ymin = Estimate - se, ymax = Estimate + se),
                width = 0.1)+
  facet_wrap(~reg)+
  scale_fill_manual(values = muColor)+
  scale_alpha_manual(values = c("1" = 1, "0" = 0.5), guide = "none")+
  labs(y = "Standardized regression weights",
       x = "Time of affective impact",
       title = "Reward outcome")+
  geom_text(aes(x = variable, y = (Estimate + (Estimate) / abs(Estimate) * se  
                                   + (Estimate) / abs(Estimate) * 0.05), label = sig))+
  theme(legend.position = "none")+
  ylim(-0.35,0.85)+ 
  theme(axis.text.x = element_text(angle = 45))


s1a <- summary(lm(scale(mean5_mu_posminusneg) ~ scale(X1o), df_master))
s2a <- summary(lm(scale(mean5_vmu_posminusneg) ~ scale(X1o), df_master))
s3a <- summary(lm(scale(mean5_s_posminusneg) ~ scale(X1o), df_master))

df_master$residuals1[!is.na(df_master$X1o)] <- as.vector(residuals(s1a))
s1bb <- summary(lm(scale(residuals1) ~ scale(X2o), df_master))
df_master$residuals2[!is.na(df_master$X2o)] <- as.vector(residuals(s1bb))
s1cc <- summary(lm(scale(residuals2) ~ scale(X3o), df_master))

df_master$residuals1[!is.na(df_master$X1o)] <- as.vector(residuals(s2a))
s2bb <- summary(lm(scale(residuals1) ~ scale(X2o), df_master))
df_master$residuals2[!is.na(df_master$X2o)] <- as.vector(residuals(s2bb))
s2cc <- summary(lm(scale(residuals2) ~ scale(X3o), df_master))

df_master$residuals1[!is.na(df_master$X1o)] <- as.vector(residuals(s3a))
s3bb <- summary(lm(scale(residuals1) ~ scale(X2o), df_master))
df_master$residuals2[!is.na(df_master$X2o)] <- as.vector(residuals(s3bb))
s3cc <- summary(lm(scale(residuals2) ~ scale(X3o), df_master))

bars <- Reduce(rbind,
       list(as.data.frame(rbind(s1a$coefficients[2,],
                                s1bb$coefficients[2,],
                                s1cc$coefficients[2,]))
                          %>% 
              mutate(reg = "ESM mean"),
            as.data.frame(rbind(s2a$coefficients[2,],
                                s2bb$coefficients[2,],
                                s2cc$coefficients[2,])) %>% 
              mutate(reg = "ESM volatility"),
            as.data.frame(rbind(s3a$coefficients[2,],
                                s3bb$coefficients[2,],
                                s3cc$coefficients[2,])) %>% 
              mutate(reg = "ESM noise"))) %>% 
  rownames_to_column() %>% 
  rename(variable = rowname,
         se = `Std. Error`,
         p_val = `Pr(>|t|)`) %>% 
  mutate(sig = ifelse(p_val < .001, "***",
                      ifelse(p_val < .01, "**",
                             ifelse(p_val < .05,"*",
                                    ifelse(p_val < .1,"†","ns")))))

bars$variable <- rep(c("trial -1~3","trial -4~6","trial -7~9"),3)

p2o <- ggplot(bars %>% 
         filter(!grepl("Intercept",variable)) %>% 
         mutate(variable = factor(variable, levels = c("trial -1~3","trial -4~6","trial -7~9")),
                reg = factor(reg,levels = c("ESM mean","ESM volatility","ESM noise") )) %>% 
           filter(reg != "ESM mean"))+
  geom_col(aes(x = variable, y = Estimate, fill = reg),
           width = 0.5)+
  geom_errorbar(aes(x = variable, ymin = Estimate - se, ymax = Estimate + se),
                width = 0.1)+
  facet_wrap(~reg)+
  scale_fill_manual(values = c(vmuColor,noiseColor))+
  scale_alpha_manual(values = c("1" = 1, "0" = 0.5), guide = "none")+
  labs(y = "Standardized regression weights",
       x = "Time of affective impact",
       title = "Reward outcome")+
  geom_text(aes(x = variable, y = (Estimate + (Estimate) / abs(Estimate) * se  
                                   + (Estimate) / abs(Estimate) * 0.05), label = sig))+
  theme(legend.position = "none")+
  ylim(-0.35,0.85)+ 
  theme(axis.text.x = element_text(angle = 45))

p2o_mu <- ggplot(bars %>% 
         filter(!grepl("Intercept",variable)) %>% 
         mutate(variable = factor(variable, levels = c("trial -1~3","trial -4~6","trial -7~9")),
                reg = factor(reg,levels = c("ESM mean","ESM volatility","ESM noise") )) %>% 
           filter(reg == "ESM mean"))+
  geom_col(aes(x = variable, y = Estimate, fill = reg),
           width = 0.5)+
  geom_errorbar(aes(x = variable, ymin = Estimate - se, ymax = Estimate + se),
                width = 0.1)+
  facet_wrap(~reg)+
  scale_fill_manual(values = muColor)+
  scale_alpha_manual(values = c("1" = 1, "0" = 0.5), guide = "none")+
  labs(y = "Standardized regression weights",
       x = "Time of affective impact",
       title = "Reward outcome")+
  geom_text(aes(x = variable, y = (Estimate + (Estimate) / abs(Estimate) * se  
                                   + (Estimate) / abs(Estimate) * 0.05), label = sig))+
  theme(legend.position = "none")+
  ylim(-0.35,0.85)+ 
  theme(axis.text.x = element_text(angle = 45))

p1o/p2o
(p1o+p1mo+p2o+p2mo)+
  plot_annotation(tag_levels = "A")+
  plot_layout(nrow = 2)

ggsave("../figures/figure_s17.png",width = 8, height = 7)
```

```{r}
p1o_mu+p2o_mu
#ggsave("../figures/figure_s9b.png",width = 5, height = 4)
```



### additional affective variability parameters (SD, AR, RMSSD) with affective impact

```{r}
s1a <- summary(lm(scale(moodrate_sd) ~ scale(X1), df_master))
s1b <- summary(lm(scale(moodrate_sd) ~ scale(X1) + scale(X2), df_master))
s1c <- summary(lm(scale(moodrate_sd) ~ scale(X1) + scale(X2) + scale(X3), df_master))

s2a <- summary(lm(scale(AR_task) ~ scale(X1), df_master))
s2b <- summary(lm(scale(AR_task)  ~ scale(X1) + scale(X2), df_master))
s2c <- summary(lm(scale(AR_task) ~ scale(X1) + scale(X2) + scale(X3), df_master))

s3a <- summary(lm(scale(moodrate_mssd) ~ scale(X1), df_master))
s3b <- summary(lm(scale(moodrate_mssd)  ~ scale(X1) + scale(X2), df_master))
s3c <- summary(lm(scale(moodrate_mssd) ~ scale(X1) + scale(X2) + scale(X3), df_master))


df_master$residuals1[!is.na(df_master$X1)] <- as.vector(residuals(s1a))
s1bb <- summary(lm(scale(residuals1) ~ scale(X2), df_master))
df_master$residuals2[!is.na(df_master$X2)] <- as.vector(residuals(s1bb))
s1cc <- summary(lm(scale(residuals2) ~ scale(X3), df_master))

df_master$residuals1[!is.na(df_master$X1)] <- as.vector(residuals(s2a))
s2bb <- summary(lm(scale(residuals1) ~ scale(X2), df_master))
df_master$residuals2[!is.na(df_master$X2)] <- as.vector(residuals(s2bb))
s2cc <- summary(lm(scale(residuals2) ~ scale(X3), df_master))

df_master$residuals1[!is.na(df_master$X1)] <- as.vector(residuals(s3a))
s3bb <- summary(lm(scale(residuals1) ~ scale(X2), df_master))
df_master$residuals2[!is.na(df_master$X2)] <- as.vector(residuals(s3bb))
s3cc <- summary(lm(scale(residuals2) ~ scale(X3), df_master))

bars <- Reduce(rbind,
       list(as.data.frame(rbind(s1a$coefficients[2,],
                                s1bb$coefficients[2,],
                                s1cc$coefficients[2,]))
                          %>% 
              mutate(reg = "task SD"),
            as.data.frame(rbind(s2a$coefficients[2,],
                                s2bb$coefficients[2,],
                                s2cc$coefficients[2,])) %>% 
              mutate(reg = "task AR"),
            as.data.frame(rbind(s3a$coefficients[2,],
                                s3bb$coefficients[2,],
                                s3cc$coefficients[2,])) %>% 
              mutate(reg = "task RMSSD"))) %>% 
  rownames_to_column() %>% 
  rename(variable = rowname,
         se = `Std. Error`,
         p_val = `Pr(>|t|)`) %>% 
  mutate(sig = ifelse(p_val < .001, "***",
                      ifelse(p_val < .01, "**",
                             ifelse(p_val < .05,"*",
                                    ifelse(p_val < .1,"†","ns")))))

bars$variable <- rep(c("trial -1~3","trial -4~6","trial -7~9"),3)

p1 <- ggplot(bars %>% 
         filter(!grepl("Intercept",variable)) %>% 
         mutate(variable = factor(variable, levels = c("trial -1~3","trial -4~6","trial -7~9")),
                reg = factor(reg,levels = c("task SD","task RMSSD","task AR") )))+
  geom_col(aes(x = variable, y = Estimate, fill = reg),
           width = 0.5)+
  geom_errorbar(aes(x = variable, ymin = Estimate - se, ymax = Estimate + se),
                width = 0.1)+
  facet_wrap(~reg)+
  scale_fill_brewer(palette = "Set2")+
  # scale_fill_manual(values = c(muColor,vmuColor,noiseColor))+
  scale_alpha_manual(values = c("1" = 1, "0" = 0.5), guide = "none")+
  labs(y = "Standardized regression weights",
       x = "Time of affective impact",
       title = "Reward outcome")+
  geom_text(aes(x = variable, y = (Estimate + (Estimate) / abs(Estimate) * se  
                                   + (Estimate) / abs(Estimate) * 0.05), label = sig))+
  theme(legend.position = "none")+
  ylim(-0.55,1)+ 
  theme(axis.text.x = element_text(angle = 45,hjust=1))


s1a <- summary(lm(scale(PAminusNA_sd) ~ scale(X1), df_master))
s1b <- summary(lm(scale(PAminusNA_sd) ~ scale(X1) + scale(X2), df_master))
s1c <- summary(lm(scale(PAminusNA_sd) ~ scale(X1) + scale(X2) + scale(X3), df_master))

s2a <- summary(lm(scale(AR_PAminusNA_sum) ~ scale(X1), df_master))
s2b <- summary(lm(scale(AR_PAminusNA_sum)  ~ scale(X1) + scale(X2), df_master))
s2c <- summary(lm(scale(AR_PAminusNA_sum) ~ scale(X1) + scale(X2) + scale(X3), df_master))

s3a <- summary(lm(scale(PAminusNA_mssd) ~ scale(X1), df_master))
s3b <- summary(lm(scale(PAminusNA_mssd)  ~ scale(X1) + scale(X2), df_master))
s3c <- summary(lm(scale(PAminusNA_mssd) ~ scale(X1) + scale(X2) + scale(X3), df_master))


df_master$residuals1[!is.na(df_master$X1)] <- as.vector(residuals(s1a))
s1bb <- summary(lm(scale(residuals1) ~ scale(X2), df_master))
df_master$residuals2[!is.na(df_master$X2)] <- as.vector(residuals(s1bb))
s1cc <- summary(lm(scale(residuals2) ~ scale(X3), df_master))

df_master$residuals1[!is.na(df_master$X1)] <- as.vector(residuals(s2a))
s2bb <- summary(lm(scale(residuals1) ~ scale(X2), df_master))
df_master$residuals2[!is.na(df_master$X2)] <- as.vector(residuals(s2bb))
s2cc <- summary(lm(scale(residuals2) ~ scale(X3), df_master))

df_master$residuals1[!is.na(df_master$X1)] <- as.vector(residuals(s3a))
s3bb <- summary(lm(scale(residuals1) ~ scale(X2), df_master))
df_master$residuals2[!is.na(df_master$X2)] <- as.vector(residuals(s3bb))
s3cc <- summary(lm(scale(residuals2) ~ scale(X3), df_master))

bars <- Reduce(rbind,
       list(as.data.frame(rbind(s1a$coefficients[2,],
                                s1bb$coefficients[2,],
                                s1cc$coefficients[2,]))
                          %>% 
              mutate(reg = "ESM SD"),
            as.data.frame(rbind(s2a$coefficients[2,],
                                s2bb$coefficients[2,],
                                s2cc$coefficients[2,])) %>% 
              mutate(reg = "ESM AR"),
            as.data.frame(rbind(s3a$coefficients[2,],
                                s3bb$coefficients[2,],
                                s3cc$coefficients[2,])) %>% 
              mutate(reg = "ESM RMSSD"))) %>% 
  rownames_to_column() %>% 
  rename(variable = rowname,
         se = `Std. Error`,
         p_val = `Pr(>|t|)`) %>% 
  mutate(sig = ifelse(p_val < .001, "***",
                      ifelse(p_val < .01, "**",
                             ifelse(p_val < .05,"*",
                                    ifelse(p_val < .1,"†","ns")))))

bars$variable <- rep(c("trial -1~3","trial -4~6","trial -7~9"),3)

p2 <- ggplot(bars %>% 
         filter(!grepl("Intercept",variable)) %>% 
         mutate(variable = factor(variable, levels = c("trial -1~3","trial -4~6","trial -7~9")),
                reg = factor(reg,levels = c("ESM SD","ESM RMSSD","ESM AR") )))+
  geom_col(aes(x = variable, y = Estimate, fill = reg),
           width = 0.5)+
  geom_errorbar(aes(x = variable, ymin = Estimate - se, ymax = Estimate + se),
                width = 0.1)+
  facet_wrap(~reg)+
    ylim(-0.55,1)+ 
  scale_fill_brewer(palette = "Set2")+
  # scale_fill_manual(values = c(muColor,vmuColor,noiseColor))+
  scale_alpha_manual(values = c("1" = 1, "0" = 0.5), guide = "none")+
  labs(y = "Standardized regression weights",
       x = "Time of affective impact",
       title = "Reward outcome")+
  geom_text(aes(x = variable, y = (Estimate + (Estimate) / abs(Estimate) * se  
                                   + (Estimate) / abs(Estimate) * 0.05), label = sig))+
  theme(legend.position = "none")+
  theme(axis.text.x = element_text(angle = 45,hjust=1))

p1/p2

ggsave("../figures/figure_s18.png",width = 6, height = 7)
```


## we can take the impact of WoF as an independent exam of the affective responsivity

```{r}
df_wof_react_long <- df_wof_react %>% 
  dplyr::select(subject,wof_order,winday_X1:loseday_X3) %>% 
  pivot_longer(winday_X1:loseday_X3,names_to = c("day","var"), values_to = "X_val",names_sep = "_")

l1 <- lmer(X_val ~ day * var + (1|subject) + (1|wof_order),df_wof_react_long)
summary(l1)

plot_model(l1, type = "pred", terms = c("var","day"))+
  geom_hline(yintercept = 0)


df_wof_Xs_long <- df_master %>% 
  dplyr::select(subject,wof_order,winday_X1:winday_X3) %>% 
  pivot_longer(winday_X1:winday_X3,names_to = "var", values_to = "X_val",names_prefix = "winday_")

l1 <- lmer(X_val ~ var + (1|subject) + (1|wof_order),df_wof_Xs_long)
summary(l1)

plot_model(l1, type = "pred", terms = c("var"))+
  geom_hline(yintercept = 0)

summary(lm(winday_X1 ~ X1+X2+X3, df_master))
summary(lm(winday_X2 ~ X1+X2+X3, df_master))

summary(lm(mean_mu ~ winday_X1 + winday_X2, df_master))
summary(lm(mean5_vmu ~ winday_X1 + winday_X2, df_master))
summary(lm(mean5_s ~ winday_X1 + winday_X2, df_master))

summary(lm(mean_mu_posminusneg ~ wof_X1, df_master))
summary(lm(mean5_vmu_posminusneg ~ wof_X1, df_master))
summary(lm(mean5_vmu_posminusneg ~ wof_X2, df_master))
summary(lm(mean5_s_posminusneg ~ wof_X1, df_master))
summary(lm(mean5_s_posminusneg ~ wof_X2, df_master))
```

```{r warning =F}
l1 <- lmer(X_val ~ var + (1|subject),df_wof_Xs_long %>% 
            mutate(var = factor(var,levels = c("X1","X2","X3"),labels = c("trial 1~3","trial 4~6","trial 7~9"))))

summary(l1)
summary(lmer(X_val ~ var + (1|subject),df_wof_Xs_long %>% 
            mutate(var = factor(var,levels = c("X2","X3","X1")))))

p00 <- plot_model(l1,type = "pred",terms = "var",
           show.data = T, jitter = T, dot.size = 0.7,ci.style = "bar")+
  labs(x = "Time of affective impact",
       title = "",
       y = "value")+
  geom_hline(yintercept = 0, linetype = "dashed")

s1a <- summary(lm(scale(winday_X1) ~ scale(X1), df_master))
df_master$residuals1[!is.na(df_master$X1)] <- as.vector(residuals(s1a))
s1bb <- summary(l1b<-lm(scale(residuals1) ~ scale(X2), df_master))
round(confint(l1b, level=0.95),3)
df_master$residuals2[!is.na(df_master$X2)] <- as.vector(residuals(s1bb))
s1cc <- summary(l1c<-lm(scale(residuals2) ~ scale(X3), df_master))
round(confint(l1c, level=0.95),3)

s2a <-summary(lm(scale(winday_X2) ~ scale(X1), df_master))
df_master$residuals1[!is.na(df_master$X1)] <- as.vector(residuals(s2a))
s2bb <- summary(l2b<-lm(scale(residuals1) ~ scale(X2), df_master))
round(confint(l2b, level=0.95),3)
df_master$residuals2[!is.na(df_master$X2)] <- as.vector(residuals(s2bb))
s2cc <- summary(l2c<-lm(scale(residuals2) ~ scale(X3), df_master))
round(confint(l2c, level=0.95),3)

bars <- Reduce(rbind,
       list(as.data.frame(rbind(s1a$coefficients[2,],
                                s1bb$coefficients[2,],
                                s1cc$coefficients[2,]))
                          %>% 
              mutate(reg = "wof: initial response"),
            as.data.frame(rbind(s2a$coefficients[2,],
                                s2bb$coefficients[2,],
                                s2cc$coefficients[2,])) %>% 
              mutate(reg = "wof: after 3 trials"))) %>% 
  rownames_to_column() %>% 
  rename(variable = rowname,
         se = `Std. Error`,
         p_val = `Pr(>|t|)`) %>% 
  mutate(sig = ifelse(p_val < .001, "***",
                      ifelse(p_val < .01, "**",
                             ifelse(p_val < .05,"*",
                                    ifelse(p_val < .1,"†","ns")))))


bars$variable <- rep(c("trial -1~3","trial -4~6","trial -7~9"),2)

p0 <- ggplot(bars %>% 
         filter(!grepl("Intercept",variable)) %>% 
         mutate(variable = factor(variable, levels = c("trial -1~3","trial -4~6","trial -7~9")),
                reg = factor(reg,levels = c("wof: initial response","wof: after 3 trials") )))+
  geom_col(aes(x = variable, y = Estimate, fill = reg),
           width = 0.5)+
  geom_errorbar(aes(x = variable, ymin = Estimate - se, ymax = Estimate + se),
                width = 0.1)+
  facet_wrap(~reg)+
  scale_fill_brewer(palette = "Greys")+
  scale_alpha_manual(values = c("1" = 1, "0" = 0.5), guide = "none")+
  labs(y = "Standardized regression weights",
       x = "Time of affective impact")+
  geom_text(aes(x = variable, y = (Estimate + (Estimate) / abs(Estimate) * se  
                                   + (Estimate) / abs(Estimate) * 0.05), label = sig))+
  theme(legend.position = "none")+
  ylim(-0.4,0.5)

s1a <- summary(lm(scale(mean_mu) ~ scale(winday_X1), df_master))
df_master$residuals1[!is.na(df_master$winday_X1)] <- as.vector(residuals(s1a))
s1bb <- summary(lm(scale(residuals1) ~ scale(winday_X2), df_master))

s2a <- summary(lm(scale(mean5_vmu) ~ scale(winday_X1), df_master))
df_master$residuals1[!is.na(df_master$winday_X1)] <- as.vector(residuals(s2a))
s2bb <- summary(lm(scale(residuals1) ~ scale(winday_X2), df_master))

s3a <- summary(lm(scale(mean5_s) ~ scale(winday_X1), df_master))
df_master$residuals1[!is.na(df_master$winday_X1)] <- as.vector(residuals(s3a))
s3bb <- summary(lm(scale(residuals1) ~ scale(winday_X2), df_master))

bars <- Reduce(rbind,
       list(as.data.frame(rbind(s1a$coefficients[2,],
                                s1bb$coefficients[2,])) %>% 
              mutate(reg = "task mean"),
            as.data.frame(rbind(s2a$coefficients[2,],
                                s2bb$coefficients[2,])) %>% 
              mutate(reg = "task volatility"),
            as.data.frame(rbind(s3a$coefficients[2,],
                                s3bb$coefficients[2,])) %>% 
              mutate(reg = "task noise"))) %>% 
  rownames_to_column() %>% 
  rename(variable = rowname,
         se = `Std. Error`,
         p_val = `Pr(>|t|)`) %>% 
  mutate(sig = ifelse(p_val < .001, "***",
                      ifelse(p_val < .01, "**",
                             ifelse(p_val < .05,"*",
                                    ifelse(p_val < .1,"†","ns")))))

bars$variable[grepl("X1",bars$variable)] <- "wof: initial response"
bars$variable[grepl("X2",bars$variable)] <- "wof: after 3 trials"
bars$variable <- rep(c("wof: initial response","wof: after 3 trials"),3)


p1 <- ggplot(bars %>% 
         filter(!grepl("Intercept",variable)) %>% 
           mutate(reg = factor(reg,levels = c("task mean","task volatility","task noise")),
                variable = factor(variable,levels = c("wof: initial response","wof: after 3 trials") )) %>% 
           filter(reg != "task mean"))+
  geom_col(aes(x = variable, y = Estimate, fill = reg),
           width = 0.5)+
  geom_errorbar(aes(x = variable, ymin = Estimate - se, ymax = Estimate + se),
                width = 0.1)+
  facet_wrap(~reg)+
  scale_fill_manual(values = c(vmuColor,noiseColor))+
  scale_alpha_manual(values = c("1" = 1, "0" = 0.5), guide = "none")+
  labs(y = "Standardized regression weights",
       x = "Time of affective impact")+
  geom_text(aes(x = variable, y = (Estimate + (Estimate) / abs(Estimate) * se  
                                   + (Estimate) / abs(Estimate) * 0.05), label = sig))+
  theme(legend.position = "none")+
  ylim(-0.4,0.4)+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

s1a <- summary(lm(scale(mean_mu_posminusneg) ~ scale(winday_X1), df_master))
df_master$residuals1[!is.na(df_master$winday_X1)] <- as.vector(residuals(s1a))
s1bb <- summary(lm(scale(residuals1) ~ scale(winday_X2), df_master))

s2a <- summary(lm(scale(mean5_vmu_posminusneg) ~ scale(winday_X1), df_master))
df_master$residuals1[!is.na(df_master$winday_X1)] <- as.vector(residuals(s2a))
s2bb <- summary(lm(scale(residuals1) ~ scale(winday_X2), df_master))

s3a <- summary(lm(scale(mean5_s_posminusneg) ~ scale(winday_X1), df_master))
df_master$residuals1[!is.na(df_master$winday_X1)] <- as.vector(residuals(s3a))
s3bb <- summary(lm(scale(residuals1) ~ scale(winday_X2), df_master))

bars <- Reduce(rbind,
       list(as.data.frame(rbind(s1a$coefficients[2,],
                                s1bb$coefficients[2,])) %>% 
              mutate(reg = "ESM mean"),
            as.data.frame(rbind(s2a$coefficients[2,],
                                s2bb$coefficients[2,])) %>% 
              mutate(reg = "ESM volatility"),
            as.data.frame(rbind(s3a$coefficients[2,],
                                s3bb$coefficients[2,])) %>% 
              mutate(reg = "ESM noise"))) %>% 
  rownames_to_column() %>% 
  rename(variable = rowname,
         se = `Std. Error`,
         p_val = `Pr(>|t|)`) %>% 
  mutate(sig = ifelse(p_val < .001, "***",
                      ifelse(p_val < .01, "**",
                             ifelse(p_val < .05,"*",
                                    ifelse(p_val < .1,"†","ns")))))
bars$variable <- rep(c("wof: initial response","wof: after 3 trials"),3)

p2 <- ggplot(bars %>% 
         filter(!grepl("Intercept",variable)) %>% 
         mutate(reg = factor(reg,levels = c("ESM mean","ESM volatility","ESM noise")),
                variable = factor(variable,levels = c("wof: initial response","wof: after 3 trials") )) %>% 
           filter(reg != "ESM mean"))+
  geom_col(aes(x = variable, y = Estimate, fill = reg),
           width = 0.5)+
  geom_errorbar(aes(x = variable, ymin = Estimate - se, ymax = Estimate + se),
                width = 0.1)+
  facet_wrap(~reg)+
  scale_fill_manual(values = c(vmuColor,noiseColor))+
  scale_alpha_manual(values = c("1" = 1, "0" = 0.5), guide = "none")+
  labs(y = "",
       x = "Time of affective impact")+
  geom_text(aes(x = variable, 
                y = (Estimate + (Estimate) / abs(Estimate) * se  + (Estimate) / abs(Estimate) * 0.05), label = sig))+
  theme(legend.position = "none")+
  ylim(-0.4,0.4)+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))


(p0+p1/p2)+
  plot_annotation(tag_levels = "A")

ggsave("../figures/figure_s20.png",width = 8, height = 6)
```

# 1. ecological validity: dependency of EMA params on task params

## look at how mu, vmu and SD correlates among them
```{r}
mean(df_master$mean5_mu)
mean(df_master$moodrate_mean)

#how mu correlate with var
summary(lm(scale(mean5_mu) ~ scale(mean5_s)+scale(mean5_vmu), df_master))
summary(lm(scale(mean5_mu_posminusneg) ~ scale(mean5_s_posminusneg)+scale(mean5_vmu_posminusneg), df_master))

summary(lm(scale(mean5_s) ~ scale(mean5_vmu), df_master))


summary(lm(scale(mean_s_posminusneg) ~ scale(PA_mean)+scale(NA_mean), df_master))
summary(lm(scale(mean5_vmu_posminusneg) ~ scale(PA_mean)+scale(NA_mean), df_master))
```

## ESM affective variability ~ task affective variability
```{r}
summary(lm(scale(mean5_vmu_posminusneg) ~  scale(mean5_vmu) + scale(mean5_s), df_master))
brm_ecoval_vmu <- brm(scale(mean5_vmu_posminusneg) ~  scale(mean5_vmu) + scale(mean5_s), df_master)
brm_ecoval_s<- brm(scale(mean5_s_posminusneg) ~  scale(mean5_vmu) + scale(mean5_s), df_master)

summary(lm(scale(mean5_vmu_posminusneg) ~  scale(mean5_vmu_d1r1) + scale(mean5_s_d1r1), df_master))
summary(lm(scale(mean5_vmu_posminusneg) ~  scale(mean5_vmu_d2r1) + scale(mean5_s_d2r1), df_master))

summary(lm(mean5_vmu_posminusneg ~  mean5_vmu + mean5_s, df_master %>% 
             filter(!subject %in% df_PANAS_uniform_response$subject)))

summary(lm(mean5_s_posminusneg ~  mean5_vmu + mean5_s, df_master))
summary(lm(mean5_s_posminusneg ~  mean5_vmu + mean5_s, df_master %>% 
             filter(!subject %in% df_PANAS_uniform_response$subject)))
```

```{r}
l2 <- lm(scale(mean5_vmu_posminusneg) ~ scale(mean5_vmu) + scale(mean5_s), df_master) #scale(mean5_mu) + 
s2 <- summary(l2)
s2
round(confint(l2, level=0.95),3)

l3 <- lm(scale(mean5_s_posminusneg) ~ scale(mean5_s) + scale(mean5_vmu), df_master)
s3 <- summary(l3)
s3
round(confint(l3, level=0.95),3)

bars <- Reduce(rbind,
       list(
         # as.data.frame(s1$coefficients) %>% 
         #      mutate(reg = "ESM mean"),
            as.data.frame(s2$coefficients) %>% 
              mutate(reg = "ESM volatility"),
            as.data.frame(s3$coefficients) %>% 
              mutate(reg = "ESM noise"))) %>% 
  rownames_to_column() %>% 
  rename(variable = rowname,
         se = `Std. Error`,
         p_val = `Pr(>|t|)`) %>% 
  mutate(sig = ifelse(p_val < .001, "***",
                      ifelse(p_val < .01, "**",
                             ifelse(p_val < .05,"*",
                                    ifelse(p_val < .1,"†","ns")))))

bars$variable[grepl("mean5_vmu",bars$variable)] <- "task volatility"
bars$variable[grepl("mean5_s",bars$variable)] <- "task noise"
bars$variable[grepl("mean5_mu",bars$variable)] <- "task mean"

bars <- bars %>% 
  mutate(alpha = ifelse(grepl("noise", variable) & grepl("noise", reg), "1", 
                        ifelse(grepl("volatility", variable) & grepl("volatility", reg), "1",
                               ifelse(grepl("mean", variable) & grepl("mean", reg), "1" ,"0"))))

p1b <- ggplot(bars %>% 
         filter(reg == "ESM volatility") %>% 
         filter(!grepl("Intercept",variable)) %>% 
         mutate(variable = factor(variable, levels = c("task mean","task volatility","task noise")),
                reg = factor(reg,levels = c("ESM mean","ESM volatility","ESM noise"))))+
  geom_col(aes(x = variable, y = Estimate, fill = variable, alpha = alpha),
           width = 0.2)+
  geom_errorbar(aes(x = variable, ymin = Estimate - se, ymax = Estimate + se),
                width = 0.1)+
  facet_wrap(~reg)+
  scale_x_discrete(name="",c("task mean","task volatility","task noise"))+
  scale_fill_manual(values = c(vmuColor,noiseColor))+
  scale_alpha_manual(values = c("1" = 1, "0" = 0.3), guide = "none")+
  geom_text(aes(x = variable, y = (Estimate + (Estimate) / abs(Estimate) * se  + (Estimate) / abs(Estimate) * 0.05), label = sig))+
  theme(legend.position = "none")+
  ylim(-0.2,0.5)+
    labs(y = "Standardized beta")

p1c <- ggplot(bars %>% 
         filter(reg == "ESM noise") %>% 
         filter(!grepl("Intercept",variable)) %>% 
         mutate(variable = factor(variable, levels = c("task mean","task volatility","task noise")),
                reg = factor(reg,levels = c("ESM mean","ESM volatility","ESM noise"))))+
  geom_col(aes(x = variable, y = Estimate, fill = variable, alpha = alpha),
           width = 0.2)+
  geom_errorbar(aes(x = variable, ymin = Estimate - se, ymax = Estimate + se),
                width = 0.1)+
  facet_wrap(~reg)+
  scale_x_discrete(name="",c("task mean","task volatility","task noise"))+
  scale_fill_manual(values = c(vmuColor,noiseColor))+
  scale_alpha_manual(values = c("1" = 1, "0" = 0.3), guide = "none")+
  labs(y = "Standardized beta",
       title = "", x = "")+
  geom_text(aes(x = variable, y = (Estimate + (Estimate) / abs(Estimate) * se  + (Estimate) / abs(Estimate) * 0.05), label = sig))+
  theme(legend.position = "none")+
  ylim(-0.2,0.5)
```

### the scatterplots
```{r}
p2b <-plot_model(lm(mean5_vmu_posminusneg ~  mean5_vmu + mean5_s, df_master), type = "pred", terms = "mean5_vmu",show.data = T,
           color = vmuColor, fill = vmuColor, dot.size = 0.5)+
  labs(x = "task volatility",
       y = "ESM volatility",
       title = "")

p2c <- plot_model(lm(mean5_s_posminusneg ~  mean5_vmu + mean5_s, df_master), type = "pred", terms = "mean5_s",show.data = T,
           color = noiseColor, fill = noiseColor, dot.size = 0.5)+
  labs(x = "task noise",
       y = "ESM noise",
       title = "")
```

```{r}
(p1b+p2b+p1c+p2c)+
  plot_annotation(tag_levels = "A")+
  plot_layout(nrow = 2,width = c(2,1))

ggsave("../figures/figure_3.png",width = 6, height = 6)
ggsave("../figures/figure_3.pdf", width = 6, height = 6, dpi = 300)
```

### supplementary analysis controlling for mu
```{r}
l1 <- lm(scale(mean5_mu_posminusneg) ~ scale(mean5_vmu) + scale(mean5_s) + scale(mean5_mu), df_master) #scale(mean5_mu) + 
s1 <- summary(l1)
s1
round(confint(l1, level=0.95),3)

l2 <- lm(scale(mean5_vmu_posminusneg) ~ scale(mean5_vmu) + scale(mean5_s) + scale(mean5_mu), df_master) #scale(mean5_mu) + 
s2 <- summary(l2)
round(confint(l2, level=0.95),3)

l3 <- lm(scale(mean5_s_posminusneg) ~  scale(mean5_vmu) + scale(mean5_s) + scale(mean5_mu), df_master)
s3 <- summary(l3)
round(confint(l3, level=0.95),3)

bars <- Reduce(rbind,
       list(
         as.data.frame(s1$coefficients) %>%
              mutate(reg = "ESM mean"),
            as.data.frame(s2$coefficients) %>% 
              mutate(reg = "ESM volatility"),
            as.data.frame(s3$coefficients) %>% 
              mutate(reg = "ESM noise"))) %>% 
  rownames_to_column() %>% 
  rename(variable = rowname,
         se = `Std. Error`,
         p_val = `Pr(>|t|)`) %>% 
  mutate(sig = ifelse(p_val < .001, "***",
                      ifelse(p_val < .01, "**",
                             ifelse(p_val < .05,"*",
                                    ifelse(p_val < .1,"†","ns")))))

bars$variable[grepl("mean5_vmu",bars$variable)] <- "task volatility"
bars$variable[grepl("mean5_s",bars$variable)] <- "task noise"
bars$variable[grepl("mean5_mu",bars$variable)] <- "task mean"

bars <- bars %>% 
  mutate(alpha = ifelse(grepl("noise", variable) & grepl("noise", reg), "1", 
                        ifelse(grepl("volatility", variable) & grepl("volatility", reg), "1",
                               ifelse(grepl("mean", variable) & grepl("mean", reg), "1" ,"0"))))

p1a <- ggplot(bars %>% 
         filter(reg == "ESM mean") %>% 
         filter(!grepl("Intercept",variable)) %>% 
         mutate(variable = factor(variable, levels = c("task mean","task volatility","task noise")),
                reg = factor(reg,levels = c("ESM mean","ESM volatility","ESM noise"))))+
  geom_col(aes(x = variable, y = Estimate, fill = variable, alpha = alpha),
           width = 0.2)+
  geom_errorbar(aes(x = variable, ymin = Estimate - se, ymax = Estimate + se),
                width = 0.1)+
  facet_wrap(~reg)+
  scale_x_discrete(name="",c("task mean","task volatility","task noise"))+
  scale_fill_manual(values = c(muColor,vmuColor,noiseColor))+
  scale_alpha_manual(values = c("1" = 1, "0" = 0.3), guide = "none")+
  geom_text(aes(x = variable, y = (Estimate + (Estimate) / abs(Estimate) * se  + (Estimate) / abs(Estimate) * 0.05), label = sig))+
  theme(legend.position = "none")+
  ylim(-0.2,0.5)+
    labs(y = "Standardized beta")

p1b <- ggplot(bars %>% 
         filter(reg == "ESM volatility") %>% 
         filter(!grepl("Intercept",variable)) %>% 
         mutate(variable = factor(variable, levels = c("task mean","task volatility","task noise")),
                reg = factor(reg,levels = c("ESM mean","ESM volatility","ESM noise"))))+
  geom_col(aes(x = variable, y = Estimate, fill = variable, alpha = alpha),
           width = 0.2)+
  geom_errorbar(aes(x = variable, ymin = Estimate - se, ymax = Estimate + se),
                width = 0.1)+
  facet_wrap(~reg)+
  scale_x_discrete(name="",c("task mean","task volatility","task noise"))+
  scale_fill_manual(values = c(muColor,vmuColor,noiseColor))+
  scale_alpha_manual(values = c("1" = 1, "0" = 0.3), guide = "none")+
  geom_text(aes(x = variable, y = (Estimate + (Estimate) / abs(Estimate) * se  + (Estimate) / abs(Estimate) * 0.05), label = sig))+
  theme(legend.position = "none")+
  ylim(-0.2,0.5)+
    labs(y = "Standardized beta")

p1c <- ggplot(bars %>% 
         filter(reg == "ESM noise") %>% 
         filter(!grepl("Intercept",variable)) %>% 
         mutate(variable = factor(variable, levels = c("task mean","task volatility","task noise")),
                reg = factor(reg,levels = c("ESM mean","ESM volatility","ESM noise"))))+
  geom_col(aes(x = variable, y = Estimate, fill = variable, alpha = alpha),
           width = 0.2)+
  geom_errorbar(aes(x = variable, ymin = Estimate - se, ymax = Estimate + se),
                width = 0.1)+
  facet_wrap(~reg)+
  scale_x_discrete(name="",c("task mean","task volatility","task noise"))+
  scale_fill_manual(values = c(muColor,vmuColor,noiseColor))+
  scale_alpha_manual(values = c("1" = 1, "0" = 0.3), guide = "none")+
  labs(y = "Standardized beta",
       title = "", x = "")+
  geom_text(aes(x = variable, y = (Estimate + (Estimate) / abs(Estimate) * se  + (Estimate) / abs(Estimate) * 0.05), label = sig))+
  theme(legend.position = "none")+
  ylim(-0.2,0.5)

p1a+p1b+p1c
ggsave("../figures/figure_s9.png",width = 8, height = 3)
```

## supplementary analyses for other variables (SD, AR, RMSSD)
```{r}
RColorBrewer::brewer.pal(n=8,"Set2")
s1 <- summary(lm(scale(PAminusNA_mssd) ~ scale(moodrate_mssd)+ scale(AR_task), df_master))
s2 <- summary(lm(scale(AR_PAminusNA_sum) ~ scale(moodrate_mssd)+ scale(AR_task), df_master))

bars2 <- Reduce(rbind,
       list(as.data.frame(s1$coefficients) %>% 
              mutate(reg = "ESM RMSSD"),
            as.data.frame(s2$coefficients) %>% 
              mutate(reg = "ESM AR"))) %>% 
  rownames_to_column() %>% 
  rename(variable = rowname,
         se = `Std. Error`,
         p_val = `Pr(>|t|)`) %>% 
  mutate(sig = ifelse(p_val < .001, "***",
                      ifelse(p_val < .01, "**",
                             ifelse(p_val < .05,"*",
                                    ifelse(p_val < .1,"†","ns")))))

bars2$variable[grepl("moodrate_mssd",bars2$variable)] <- "task RMSSD"
bars2$variable[grepl("AR_task",bars2$variable)] <- "task AR"

bars2 <- bars2 %>% 
  mutate(alpha = ifelse(grepl("sd", variable) & grepl("sd", reg), "1", 
                        ifelse(grepl("RMSSD", variable) & grepl("RMSSD", reg), "1" ,
                               ifelse(grepl("AR", variable) & grepl("AR", reg), "1" ,"0"))))


p1 <- ggplot(bars2 %>% 
         filter(!grepl("Intercept",variable)) %>% 
         mutate(variable = factor(variable, levels = c("task RMSSD","task AR")),
                reg = factor(reg,levels = c("ESM RMSSD","ESM AR") )))+
  geom_col(aes(x = variable, y = Estimate, fill = variable, alpha = alpha),
           width = 0.5)+
  geom_errorbar(aes(x = variable, ymin = Estimate - se, ymax = Estimate + se),
                width = 0.1)+
  facet_wrap(~reg)+
  scale_fill_manual(values = c("#FC8D62","#8DA0CB"))+
  scale_alpha_manual(values = c("1" = 1, "0" = 0.5), guide = "none")+
  labs(y = "Standardized beta",
       title = "Regression weights (multiple regression)",
       x = "")+
  geom_text(aes(x = variable, y = (Estimate + (Estimate) / abs(Estimate) * se  + (Estimate) / abs(Estimate) * 0.05), label = sig))+
  ylim(-0.35,0.8)+
  theme(legend.position = "none")

s1 <- summary(lm(scale(PAminusNA_sd) ~ scale(moodrate_sd)+ scale(AR_task), df_master))
s2 <- summary(lm(scale(AR_PAminusNA_sum) ~ scale(moodrate_sd)+ scale(AR_task), df_master))

bars2 <- Reduce(rbind,
       list(as.data.frame(s1$coefficients) %>% 
              mutate(reg = "ESM SD"),
            as.data.frame(s2$coefficients) %>% 
              mutate(reg = "ESM AR"))) %>% 
  rownames_to_column() %>% 
  rename(variable = rowname,
         se = `Std. Error`,
         p_val = `Pr(>|t|)`) %>% 
  mutate(sig = ifelse(p_val < .001, "***",
                      ifelse(p_val < .01, "**",
                             ifelse(p_val < .05,"*",
                                    ifelse(p_val < .1,"†","ns")))))

bars2$variable[grepl("moodrate_sd",bars2$variable)] <- "task SD"
bars2$variable[grepl("AR_task",bars2$variable)] <- "task AR"

bars2 <- bars2 %>% 
  mutate(alpha = ifelse(grepl("sd", variable) & grepl("sd", reg), "1", 
                        ifelse(grepl("RMSSD", variable) & grepl("RMSSD", reg), "1" ,
                               ifelse(grepl("AR", variable) & grepl("AR", reg), "1" ,"0"))))


p1b <- ggplot(bars2 %>% 
         filter(!grepl("Intercept",variable)) %>% 
         mutate(variable = factor(variable, levels = c("task SD","task AR")),
                reg = factor(reg,levels = c("ESM SD","ESM AR") )))+
  geom_col(aes(x = variable, y = Estimate, fill = variable, alpha = alpha),
           width = 0.5)+
  geom_errorbar(aes(x = variable, ymin = Estimate - se, ymax = Estimate + se),
                width = 0.1)+
  facet_wrap(~reg)+
  scale_fill_manual(values = c("#66C2A5","#8DA0CB"))+
  scale_alpha_manual(values = c("1" = 1, "0" = 0.5), guide = "none")+
  labs(y = "Standardized beta",
       title = "Regression weights (multiple regression)",
       x = "")+
  geom_text(aes(x = variable, y = (Estimate + (Estimate) / abs(Estimate) * se  + (Estimate) / abs(Estimate) * 0.05), label = sig))+
  ylim(-0.35,0.8)+
  theme(legend.position = "none")

s1 <- summary(lm(scale(PAminusNA_sd) ~ scale(moodrate_sd) + scale(moodrate_mssd)+ scale(AR_task), df_master))
s2 <- summary(lm(scale(PAminusNA_mssd) ~ scale(moodrate_sd) + scale(moodrate_mssd)+ scale(AR_task), df_master))
s3 <- summary(lm(scale(AR_PAminusNA_sum) ~ scale(moodrate_sd) + scale(moodrate_mssd)+ scale(AR_task), df_master))

bars2 <- Reduce(rbind,
       list(as.data.frame(s1$coefficients) %>% 
              mutate(reg = "ESM SD"),
            as.data.frame(s2$coefficients) %>% 
              mutate(reg = "ESM RMSSD"),
            as.data.frame(s3$coefficients) %>% 
              mutate(reg = "ESM AR"))) %>% 
  rownames_to_column() %>% 
  rename(variable = rowname,
         se = `Std. Error`,
         p_val = `Pr(>|t|)`) %>% 
  mutate(sig = ifelse(p_val < .001, "***",
                      ifelse(p_val < .01, "**",
                             ifelse(p_val < .05,"*",
                                    ifelse(p_val < .1,"†","ns")))))

bars2$variable[grepl("moodrate_sd",bars2$variable)] <- "task SD"
bars2$variable[grepl("moodrate_mssd",bars2$variable)] <- "task RMSSD"
bars2$variable[grepl("AR_task",bars2$variable)] <- "task AR"

bars2 <- bars2 %>% 
  mutate(alpha = ifelse(grepl("sd", variable) & grepl("sd", reg), "1", 
                        ifelse(grepl("RMSSD", variable) & grepl("RMSSD", reg), "1" ,
                               ifelse(grepl("AR", variable) & grepl("AR", reg), "1" ,"0"))))


p2 <- ggplot(bars2 %>% 
         filter(!grepl("Intercept",variable)) %>% 
         mutate(variable = factor(variable, levels = c("task SD","task RMSSD","task AR")),
                reg = factor(reg,levels = c("ESM SD","ESM RMSSD","ESM AR") )))+
  geom_col(aes(x = variable, y = Estimate, fill = variable, alpha = alpha),
           width = 0.5)+
  geom_errorbar(aes(x = variable, ymin = Estimate - se, ymax = Estimate + se),
                width = 0.1)+
  facet_wrap(~reg)+
  scale_fill_brewer(palette = "Set2")+
  scale_alpha_manual(values = c("1" = 1, "0" = 0.5), guide = "none")+
  labs(y = "Standardized beta",
       title = "Regression weights (multiple regression)",
       x = "")+
  geom_text(aes(x = variable, y = (Estimate + (Estimate) / abs(Estimate) * se  + (Estimate) / abs(Estimate) * 0.05), label = sig))+ 
  theme(axis.text.x = element_text(angle = 45))+
  theme(legend.position = "none")
  # ylim(-0.75,1)

s1 <- summary(lm(scale(PAminusNA_sd) ~ scale(moodrate_sd) , df_master))
s2 <- summary(lm(scale(PAminusNA_mssd) ~ scale(moodrate_mssd), df_master))
s3 <- summary(lm(scale(AR_PAminusNA_sum) ~ scale(AR_task), df_master))

bars2 <- Reduce(rbind,
       list(as.data.frame(s1$coefficients) %>% 
              mutate(reg = "ESM SD"),
            as.data.frame(s2$coefficients) %>% 
              mutate(reg = "ESM RMSSD"),
            as.data.frame(s3$coefficients) %>% 
              mutate(reg = "ESM AR"))) %>% 
  rownames_to_column() %>% 
  rename(variable = rowname,
         se = `Std. Error`,
         p_val = `Pr(>|t|)`) %>% 
  mutate(sig = ifelse(p_val < .001, "***",
                      ifelse(p_val < .01, "**",
                             ifelse(p_val < .05,"*",
                                    ifelse(p_val < .1,"†","ns")))))

bars2$variable[grepl("moodrate_sd",bars2$variable)] <- "task SD"
bars2$variable[grepl("moodrate_mssd",bars2$variable)] <- "task RMSSD"
bars2$variable[grepl("AR_task",bars2$variable)] <- "task AR"

bars2 <- bars2 %>% 
  mutate(alpha = ifelse(grepl("SD", variable) & grepl("SD", reg), "1", 
                        ifelse(grepl("RMSSD", variable) & grepl("RMSSD", reg), "1" ,
                               ifelse(grepl("AR", variable) & grepl("AR", reg), "1" ,"0"))))


p3 <- ggplot(bars2 %>% 
         filter(!grepl("Intercept",variable)) %>% 
         mutate(variable = factor(variable, levels = c("task SD","task RMSSD","task AR")),
                reg = factor(reg,levels = c("ESM SD","ESM RMSSD","ESM AR") )))+
  geom_col(aes(x = variable, y = Estimate, fill = variable, alpha = alpha),
           width = 0.5)+
  geom_errorbar(aes(x = variable, ymin = Estimate - se, ymax = Estimate + se),
                width = 0.1)+
  facet_wrap(~reg,scales = "free_x")+
  scale_fill_brewer(palette = "Set2")+
  scale_alpha_manual(values = c("1" = 1, "0" = 0.5), guide = "none")+
  labs(y = "Standardized beta",
       title = "(simple regression)",
       x = "")+
  geom_text(aes(x = variable, y = (Estimate + (Estimate) / abs(Estimate) * se  + (Estimate) / abs(Estimate) * 0.05), label = sig))+
  theme(legend.position = "none")

design <- "
  1112
  3344
"
(p2+p3+p1+p1b)+
  plot_annotation(tag_levels = "A")+
  plot_layout(design = design)
ggsave("../figures/figure_s18.png",width = 10, height = 7)
```

## how are RMSSD, SD and AR related to vmu and s?
```{r}
summary(l1<-lm(scale(moodrate_mean) ~ scale(mean5_mu) + scale(mean5_vmu) + scale(mean_s),df_master))
summary(l2<-lm(scale(PAminusNA_mean) ~ scale(mean5_mu_posminusneg) + scale(mean5_vmu_posminusneg) + scale(mean_s_posminusneg),df_master))

summary(l3<-lm(scale(moodrate_mssd) ~ scale(mean5_mu) + scale(mean5_vmu) + scale(mean_s),df_master))
summary(l4<-lm(scale(PAminusNA_mssd) ~ scale(mean5_mu_posminusneg) + scale(mean5_vmu_posminusneg) + scale(mean_s_posminusneg),df_master))

summary(l5<-lm(scale(moodrate_sd) ~ scale(mean5_mu) + scale(mean5_vmu) + scale(mean_s),df_master))
summary(l6<-lm(scale(PAminusNA_sd) ~ scale(mean5_mu_posminusneg) + scale(mean5_vmu_posminusneg) + scale(mean_s_posminusneg),df_master))

summary(l7<-lm(scale(AR_task) ~ scale(mean5_mu) + scale(mean5_vmu) + scale(mean_s),df_master))
summary(l8<-lm(scale(AR_PAminusNA_sum) ~ scale(mean5_mu_posminusneg) + scale(mean5_vmu_posminusneg) + scale(mean_s_posminusneg),df_master))

plot_model(l1)+plot_model(l2)
plot_model(l3)+plot_model(l4)
plot_model(l5)+plot_model(l6)
plot_model(l7)+plot_model(l8)
```


## how does state affect affect the parameters?
```{r}
df_gor_Est_long_long <- df_gor_Est_long %>% 
  left_join(df_wof)  %>% 
  mutate(wof_result = ifelse(wofoutcome1 == 1 & grepl("d1",run), "win",
                             ifelse(wofoutcome2 == 1 & grepl("d2",run), "win","loss"))) %>% 
  pivot_longer( mean5_mu:last_vmu, names_to = "measure",
               values_to = "value")%>% 
  mutate(group = ifelse(grepl("r1",run),"baseline",wof_result)) %>% 
  mutate(parameter = ifelse(grepl("_mu",measure),"mu",
                            ifelse(grepl("_vmu",measure),"vmu",
                                   ifelse(grepl("_s",measure),"s",NA))))

df_gor_Est_long_long$wof_result <- factor(df_gor_Est_long_long$wof_result,
                                          levels = c("baseline","win","loss"))

summary(l1<-lmer(value~group+(1|subject),df_gor_Est_long_long %>% filter(measure=="mean5_mu")))

summary(l2<-lmer(value~group+(1|subject),df_gor_Est_long_long %>% filter(measure=="mean5_vmu")))

summary(l3<-lmer(value~group+(1|subject),df_gor_Est_long_long %>% filter(measure=="mean5_s")))

plot_model(l1, type = "pred", terms = "group")+
  plot_model(l2, type = "pred", terms = "group")+
  plot_model(l3, type = "pred", terms = "group")

performance::icc(lmer(value~1+(1|subject),df_gor_Est_long_long %>% filter(measure=="mean5_vmu")))

performance::icc(lmer(value~1+(1|subject),df_gor_Est_long_long %>% filter(measure=="mean5_vmu",
                                                                          group%in% c("win","loss"))))

performance::icc(lmer(value~1+(1|subject),df_gor_Est_long_long %>% filter(measure=="mean5_vmu",
                                                                          group%in% c("baseline"))))

performance::icc(lmer(value~1+(1|subject),df_gor_Est_long_long %>% filter(measure=="mean5_s",
                                                                          group%in% c("win","loss"))))
performance::icc(lmer(value~1+(1|subject),df_gor_Est_long_long %>% filter(measure=="mean5_s",
                                                                          group%in% c("baseline"))))
```
## stability of the two-factor strucutre of PANAS across people
```{r eval=F}
library(lavaan)

model_2factor <- '
  level: 1  # within-person
    PA_w =~ Interested + Excited + Strong + Enthusiastic + Proud + 
            Alert + Inspired + Determined + Attentive + Active
    NA_w =~ Distressed + Upset + Guilty + Scared + Hostile + 
            Irritable + Ashamed + Nervous + Jittery + Afraid

  level: 2  # between-person
    PA_b =~ Interested + Excited + Strong + Enthusiastic + Proud + 
            Alert + Inspired + Determined + Attentive + Active
    NA_b =~ Distressed + Upset + Guilty + Scared + Hostile + 
            Irritable + Ashamed + Nervous + Jittery + Afraid
'

fit_2factor <- cfa(model_2factor,
                   data = df_PANAS,
                   cluster = "subject",
                   estimator = "MLR")

summary(fit_2factor, fit.measures = TRUE, standardized = TRUE)

# One-factor within-person comparison
model_1factor <- '
  level: 1
    Affect_w =~ Interested + Excited + Strong + Enthusiastic + Proud + 
                Alert + Inspired + Determined + Attentive + Active +
                Distressed + Upset + Guilty + Scared + Hostile + 
                Irritable + Ashamed + Nervous + Jittery + Afraid

  level: 2
    PA_b =~ Interested + Excited + Strong + Enthusiastic + Proud + 
            Alert + Inspired + Determined + Attentive + Active
    NA_b =~ Distressed + Upset + Guilty + Scared + Hostile + 
            Irritable + Ashamed + Nervous + Jittery + Afraid
'

fit_1factor <- cfa(model_1factor,
                   data = df_PANAS,
                   cluster = "subject",
                   estimator = "MLR")

lavTestLRT(fit_2factor, fit_1factor)
#PA and NA are clearly distinguishable even at the within-person level. 
```

### plot within-person fit of PA/NA
```{r eval=F}
# Avoid ncpus detection issues in some environments (e.g. Rscript, clusters)
lavOptions(ncpus = 1L)

# PANAS item names for complete-case filtering
panas_items <- c("Interested", "Excited", "Strong", "Enthusiastic", "Proud",
                 "Alert", "Inspired", "Determined", "Attentive", "Active",
                 "Distressed", "Upset", "Guilty", "Scared", "Hostile",
                 "Irritable", "Ashamed", "Nervous", "Jittery", "Afraid")

model_2f <- '
  PA =~ Interested + Excited + Strong + Enthusiastic + Proud + 
        Alert + Inspired + Determined + Attentive + Active
  NA_ =~ Distressed + Upset + Guilty + Scared + Hostile + 
         Irritable + Ashamed + Nervous + Jittery + Afraid
'

model_1f <- '
  Affect =~ Interested + Excited + Strong + Enthusiastic + Proud + 
            Alert + Inspired + Determined + Attentive + Active +
            Distressed + Upset + Guilty + Scared + Hostile + 
            Irritable + Ashamed + Nervous + Jittery + Afraid
'

# Helper: return NA row when fit fails (with reason for diagnostics)
na_row <- function(subj, reason = "error") {
  tibble(subject = subj, cfi_2f = NA_real_, cfi_1f = NA_real_,
         rmsea_2f = NA_real_, rmsea_1f = NA_real_, aic_2f = NA_real_, aic_1f = NA_real_,
         delta_cfi = NA_real_, delta_rmsea = NA_real_, delta_aic = NA_real_,
         pa_na_cor = NA_real_, fail_reason = reason)
}

results <- df_PANAS %>%
  dplyr::select(subject, all_of(panas_items)) %>%
  group_by(subject) %>%
  group_map(~ {
    dat <- .x %>% filter(complete.cases(across(all_of(panas_items))))
    subj <- .y$subject
    
    # Need sufficient observations for CFA (rule of thumb: ~5 per parameter; 2-factor 20-item model has ~40 params)
    if (nrow(dat) < 30) return(na_row(subj, "n < 30"))
    
    tryCatch({
      fit2 <- cfa(model_2f, data = dat, estimator = "ML", warn = FALSE)
      fit1 <- cfa(model_1f, data = dat, estimator = "ML", warn = FALSE)
      
      # Only use fit measures if both models converged
      if (!lavInspect(fit2, "converged") || !lavInspect(fit1, "converged")) {
        return(na_row(subj, "non-converged"))
      }
      
      cfi2  <- as.numeric(fitMeasures(fit2, "cfi"))
      cfi1  <- as.numeric(fitMeasures(fit1, "cfi"))
      rm2   <- as.numeric(fitMeasures(fit2, "rmsea"))
      rm1   <- as.numeric(fitMeasures(fit1, "rmsea"))
      a2    <- as.numeric(fitMeasures(fit2, "aic"))
      a1    <- as.numeric(fitMeasures(fit1, "aic"))
      
      # Guard against NA fit indices (can occur with non-PD cov matrices)
      if (any(is.na(c(cfi2, cfi1, rm2, rm1, a2, a1)))) return(na_row(subj, "NA fit indices"))
      
      # Within-person PA-NA latent correlation from 2-factor model
      std <- standardizedSolution(fit2)
      pa_na <- std %>% filter((lhs == "PA" & rhs == "NA_") | (lhs == "NA_" & rhs == "PA"),
                             op == "~~") %>% pull(est.std)
      pa_na_cor <- if (length(pa_na) > 0) as.numeric(pa_na[1]) else NA_real_
      
      tibble(
        subject = subj,
        cfi_2f = cfi2, cfi_1f = cfi1,
        rmsea_2f = rm2, rmsea_1f = rm1,
        aic_2f = a2, aic_1f = a1,
        delta_cfi = cfi2 - cfi1,
        delta_rmsea = rm1 - rm2,
        delta_aic = a1 - a2,
        pa_na_cor = pa_na_cor,
        fail_reason = NA_character_
      )
    }, error = function(e) na_row(subj, "error"))
  }) %>%
  bind_rows()

# Summary of convergence and failure breakdown
n_ok <- sum(!is.na(results$cfi_2f))
n_fail <- sum(is.na(results$cfi_2f))
message(sprintf("Person-level CFA: %d converged, %d failed", n_ok, n_fail))
if (n_fail > 0) {
  fail_breakdown <- results %>% filter(is.na(cfi_2f)) %>% count(fail_reason, name = "n")
  message("Failure breakdown:")
  print(fail_breakdown)
}

# Use only converged fits for plotting (exclude NA)
results_plot <- results %>% filter(!is.na(delta_cfi))

# Delta CFI: how much better is 2-factor per person?
p1 <- ggplot(results_plot, aes(x = reorder(subject, delta_cfi), y = delta_cfi)) +
  geom_point(aes(color = delta_cfi > 0), size = 1.5) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  scale_color_manual(values = c("red", "steelblue"),
                     labels = c("1-factor better", "2-factor better")) +
  labs(x = "Participant", y = "ΔCFI (2f - 1f)", 
       title = "Per-person improvement in CFI: 2-factor vs 1-factor",
       color = NULL) +
  theme(axis.text.x = element_blank())

# Delta AIC
p2 <- ggplot(results_plot, aes(x = reorder(subject, delta_aic), y = delta_aic)) +
  geom_point(aes(color = delta_aic > 0), size = 1.5) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  scale_color_manual(values = c("red", "steelblue"),
                     labels = c("1-factor better", "2-factor better")) +
  labs(x = "Participant", y = "ΔAIC (1f - 2f)",
       title = "Per-person AIC difference: positive = 2-factor better",
       color = NULL) +
  theme(axis.text.x = element_blank())

# Within-person PA-NA latent correlation per participant
p3_data <- results_plot %>% filter(!is.na(pa_na_cor))
p3 <- ggplot(p3_data, aes(x = pa_na_cor)) +
  geom_histogram(fill = "steelblue", alpha = 0.7, color = "white") +
  geom_vline(xintercept = mean(p3_data$pa_na_cor), linetype = "dashed", linewidth = 1) +
  labs(x = "PA–NA correlation (within-person)", y = "Count",
       title = "Within-person PA-NA latent correlation per participant") +
  theme_minimal()
p1 / p2 / p3

mean(p3_data$pa_na_cor[abs(p3_data$pa_na_cor) < 1])
```

### show that excluding close responses in panas does not erase its correlation with task params
```{r eval=F}
p_vol <- ggplot(df_master,aes(x = mean5_vmu_posminusneg,y = mean5_vmu_posminusneg_noCloseResponse))+
  geom_point()+
  geom_smooth(method = "lm")+
  stat_poly_eq(use_label(c("R2","p")))+
  labs(x = "volatility (original)",
       y = "volatility (excluding close responses)",
       title = "volatility")

p_noise <- ggplot(df_master,aes(x = mean5_s_posminusneg,y = mean5_s_posminusneg_noCloseResponse))+
  geom_point()+
  geom_smooth(method = "lm")+
  stat_poly_eq(use_label(c("R2","p")))+
  labs(x = "noise (original)",
       y = "noise (excluding close responses)",
       title = "noise")

p_vol | p_noise
ggsave("../figures/figure_r1_7_2.png", width = 6, height = 3.5)

summary(lm(scale(mean5_vmu_posminusneg_noCloseResponse) ~ scale(mean5_vmu) + scale(mean5_s),df_master))
summary(lm(scale(mean5_s_posminusneg_noCloseResponse) ~ scale(mean5_vmu) + scale(mean5_s),df_master))
```


# robustness of parameter derivation
## first, show how these different derivations were related

## how are they correlated across days and runs? (d1r1 vs. d2r1 is the test-retest)
```{r}
df_gor_Est_all <- df_gor_Est_long %>% 
  dplyr::select(-subj_day_block) %>% 
  pivot_wider(names_from = run, values_from = mean_mu:last_vmu)
# Helper: correlation + SD of estimates (mean of SD from d1r1 and d2r1)
cor_sd <- function(x1, x2) {
  n <- sum(complete.cases(x1, x2))
  r <- cor(x1, x2, use = "complete.obs")
  sd_est <- mean(c(sd(x1, na.rm = TRUE), sd(x2, na.rm = TRUE)))
  list(r = r, sd_est = sd_est, n = n)
}

#mu
mu_retest <- tibble(
  calc = factor(c("all", "10_last", "5_last", "1_last"), levels = c("all", "10_last", "5_last", "1_last"))
) %>%
  mutate(
    res = list(
      cor_sd(df_gor_Est_all$mean_mu_d1r1, df_gor_Est_all$mean_mu_d2r1),
      cor_sd(df_gor_Est_all$mean10_mu_d1r1, df_gor_Est_all$mean10_mu_d2r1),
      cor_sd(df_gor_Est_all$mean5_mu_d1r1, df_gor_Est_all$mean5_mu_d2r1),
      cor_sd(df_gor_Est_all$last_mu_d1r1, df_gor_Est_all$last_mu_d2r1)
    ),
    value = map_dbl(res, "r"),
    sd_est = map_dbl(res, "sd_est")
  ) %>% dplyr::select(-res)

#vmu
vmu_retest <- tibble(
  calc = factor(c("all", "10_last", "5_last", "1_last"), levels = c("all", "10_last", "5_last", "1_last"))
) %>%
  mutate(
    res = list(
      cor_sd(df_gor_Est_all$mean_vmu_d1r1, df_gor_Est_all$mean_vmu_d2r1),
      cor_sd(df_gor_Est_all$mean10_vmu_d1r1, df_gor_Est_all$mean10_vmu_d2r1),
      cor_sd(df_gor_Est_all$mean5_vmu_d1r1, df_gor_Est_all$mean5_vmu_d2r1),
      cor_sd(df_gor_Est_all$last_vmu_d1r1, df_gor_Est_all$last_vmu_d2r1)
    ),
    value = map_dbl(res, "r"),
    sd_est = map_dbl(res, "sd_est")
  ) %>% dplyr::select(-res)

#s
s_retest <- tibble(
  calc = factor(c("all", "10_last", "5_last", "1_last"), levels = c("all", "10_last", "5_last", "1_last"))
) %>%
  mutate(
    res = list(
      cor_sd(df_gor_Est_all$mean_s_d1r1, df_gor_Est_all$mean_s_d2r1),
      cor_sd(df_gor_Est_all$mean10_s_d1r1, df_gor_Est_all$mean10_s_d2r1),
      cor_sd(df_gor_Est_all$mean5_s_d1r1, df_gor_Est_all$mean5_s_d2r1),
      cor_sd(df_gor_Est_all$last_s_d1r1, df_gor_Est_all$last_s_d2r1)
    ),
    value = map_dbl(res, "r"),
    sd_est = map_dbl(res, "sd_est")
  ) %>% dplyr::select(-res)

# Plot - SD of parameter estimates as error bars
# For the point with the largest SD, the error bar length is fixed at ±0.12 on the y-axis.
# For other points, the bar length is proportional to their SD relative to that maximum.
sd_scale <- 0.12 / max(c(mu_retest$sd_est, vmu_retest$sd_est, s_retest$sd_est))
ggplot(mu_retest, aes(x = calc, y = value)) +
  geom_errorbar(aes(ymin = value - sd_est * sd_scale, ymax = value + sd_est * sd_scale), width = 0.2, linewidth = 0.8, color = muColor) +
  geom_point(size = 3, color = muColor) +
  labs(x = "averaging window", y = "Test-retest reliability",
       title = "task mu")+
  ylim(0, 1)+
ggplot(vmu_retest, aes(x = calc, y = value)) +
  geom_errorbar(aes(ymin = value - sd_est * sd_scale, ymax = value + sd_est * sd_scale), width = 0.2, linewidth = 0.8, color = vmuColor) +
  geom_point(size = 3, color = vmuColor) +
  ylim(0, 1)+
  labs(x = "averaging window", y = "Test-retest reliability",
       title = "task volatility")+
ggplot(s_retest, aes(x = calc, y = value)) +
  geom_errorbar(aes(ymin = value - sd_est * sd_scale, ymax = value + sd_est * sd_scale), width = 0.2, linewidth = 0.8, color = noiseColor) +
  geom_point(size = 3, color = noiseColor) +
  ylim(0, 1)+
  labs(x = "averaging window", y = "Test-retest reliability",
       title = "task noise")+
  plot_annotation(title = "Test-retest reliability across parameterization")


ggsave("../figures/figure_s21.png",width = 7, height = 3)
```



## actually show that the key results were not biased significantly by choice of calculation


## show regression results across parameterization
```{r}
run_model <- function(prefix, outcome_type){

  # outcome_type = "vmu" or "s"
  
  outcome <- paste0(prefix, "_", outcome_type, "_posminusneg")
  pred_vmu <- paste0(prefix, "_vmu")
  pred_s   <- paste0(prefix, "_s")
  
  form <- as.formula(
    paste0("scale(", outcome, ") ~ scale(", pred_vmu, ") + scale(", pred_s, ")")
  )
  
  mod <- lm(form, data = df_master)
  
  broom::tidy(mod, conf.int = TRUE) %>%
    filter(term != "(Intercept)") %>%
    mutate(
      prefix = prefix,
      outcome = outcome_type,
      predictor = case_when(
        str_detect(term, "vmu") ~ "task volatility",
        str_detect(term, "_s")  ~ "task noise"
      )
    )
}

prefixes <- c("last", "mean5", "mean10", "mean")

results <- expand_grid(prefix = prefixes,
                       outcome = c("vmu", "s")) %>%
  pmap_dfr(~ run_model(..1, ..2))

results_clean <- results %>%
  mutate(
    reg = case_when(
      outcome == "vmu" ~ "ESM volatility",
      outcome == "s"   ~ "ESM noise"
    ),
    sig = case_when(
      p.value < .001 ~ "***",
      p.value < .01  ~ "**",
      p.value < .05  ~ "*",
      p.value < .1   ~ "†",
      TRUE ~ "ns"
    ),
    alpha = ifelse(
      (reg == "ESM volatility" & predictor == "task volatility") |
      (reg == "ESM noise" & predictor == "task noise"),
      1, .3)) %>% 
  mutate(calculation = case_when(prefix == "mean"~"all",
                                 prefix == "mean10"~"10_last",
                                 prefix == "mean5"~"5_last",
                                 prefix == "last"~"1_last",
                                 TRUE~NA),
         calculation = factor(calculation, levels = c("all","10_last","5_last","1_last")))

ggplot(results_clean,
       aes(x = calculation,
           y = estimate,
           fill = predictor)) +
  geom_col(aes(alpha = alpha),position = position_dodge(width = .5),
           width = .4) +
  geom_errorbar(aes(ymin = estimate- std.error,
                    ymax = estimate+ std.error),
                position = position_dodge(width = .5),
                width = .15) +
  
  geom_text(aes(label = sig,
                y = estimate + sign(estimate)*.15),
            position = position_dodge(width = .5),
            size = 4) +
  facet_wrap(~reg, nrow = 2) +
  scale_alpha(range = c(.3, 1), guide = "none") +
  scale_fill_manual(values = c( noiseColor,vmuColor)) +
  labs(y = "Standardized beta",
       x = "Averaging window",
       title = "Stability of Task-to-EMA Associations Across Parameterizations") +
  
  theme_classic() +
  theme(
    legend.position = "none",
    axis.text.x = element_text(angle = 45, hjust = 1))+
  ylim(-0.3,0.35)

ggsave("../figures/figure_s22.png",width = 6, height = 6)
```

### vmu corrplot
```{r}
df1<-df_master %>% 
                    dplyr::select(last_vmu_posminusneg,mean5_vmu_posminusneg,mean10_vmu_posminusneg,mean_vmu_posminusneg,
                           last_vmu,mean5_vmu,mean10_vmu,mean_vmu)

names <-expand_grid(c("EMA_","task_"),c("last","mean5","mean10","mean"))
for (i in 1:ncol(df1)){
  names(df1)[i]=paste0(names[i,1],names[i,2])
}
# Compute correlation matrix
cormat <- cor(df1, use = "pairwise.complete.obs")
corpmat <- cor_pmat(df1)
# Plot
p1<-ggcorrplot::ggcorrplot(cormat,p.mat = corpmat,type = "upper",
                      lab=T,pch.col="brown")+
  geom_rect(aes(xmin = 1 - 0.5, xmax = 1 + 0.5, ymin = 4 - 0.5, ymax = 4 + 0.5),
            fill = NA, color = "black", linewidth = 1, inherit.aes = FALSE)+
  geom_rect(aes(xmin = 2 - 0.5, xmax = 2 + 0.5, ymin = 5 - 0.5, ymax = 5 + 0.5),
            fill = NA, color = "black", linewidth = 1, inherit.aes = FALSE)+
  geom_rect(aes(xmin = 3 - 0.5, xmax = 3 + 0.5, ymin = 6 - 0.5, ymax = 6 + 0.5),
            fill = NA, color = "black", linewidth = 1, inherit.aes = FALSE)+
  geom_rect(aes(xmin = 4 - 0.5, xmax = 4 + 0.5, ymin = 7 - 0.5, ymax = 7 + 0.5),
            fill = NA, color = "black", linewidth = 1, inherit.aes = FALSE)+
  labs(title = "Volatility")+
  theme(axis.text = element_text(size = 2),
        axis.text.x = element_text(angle = 45, hjust = 1),
        plot.title = element_text(size = 14))
```

### s corrplot
```{r}
df1<-df_master %>% 
                    dplyr::select(last_s_posminusneg,mean5_s_posminusneg,mean10_s_posminusneg,mean_s_posminusneg,
                           last_s,mean5_s,mean10_s,mean_s)

names <-expand_grid(c("EMA_","task_"),c("last","mean5","mean10","mean"))
for (i in 1:ncol(df1)){
  names(df1)[i]=paste0(names[i,1],names[i,2])
}
# Compute correlation matrix
cormat <- cor(df1, use = "pairwise.complete.obs")
corpmat <- cor_pmat(df1)
# Plot
p2<-ggcorrplot::ggcorrplot(cormat,p.mat = corpmat,type = "upper",
                      lab=T,pch.col="brown")+
  geom_rect(aes(xmin = 1 - 0.5, xmax = 1 + 0.5, ymin = 4 - 0.5, ymax = 4 + 0.5),
            fill = NA, color = "black", linewidth = 1, inherit.aes = FALSE)+
  geom_rect(aes(xmin = 2 - 0.5, xmax = 2 + 0.5, ymin = 5 - 0.5, ymax = 5 + 0.5),
            fill = NA, color = "black", linewidth = 1, inherit.aes = FALSE)+
  geom_rect(aes(xmin = 3 - 0.5, xmax = 3 + 0.5, ymin = 6 - 0.5, ymax = 6 + 0.5),
            fill = NA, color = "black", linewidth = 1, inherit.aes = FALSE)+
  geom_rect(aes(xmin = 4 - 0.5, xmax = 4 + 0.5, ymin = 7 - 0.5, ymax = 7 + 0.5),
            fill = NA, color = "black", linewidth = 1, inherit.aes = FALSE)+
  labs(title = "Noise")+
  theme(axis.text = element_text(size = 2),
        axis.text.x = element_text(angle = 45, hjust = 1),
        plot.title = element_text(size = 14))
```

```{r}
p1+p2
ggsave("../figures/figure_s23.png",width = 10, height = 4)
```


# PANAS VAR1 model with innovation term

```{r}

cormat = cor(df_master %>% dplyr::select(mean5_vmu_posminusneg,mean5_s_posminusneg,
                           PANAS_AR1,PANAS_LOGVAR,
                           mean5_vmu,mean5_s,
                           TASK_AR1,TASK_LOGVAR) %>% 
               rename(EMA_vmu = mean5_vmu_posminusneg,
                      EMA_s = mean5_s_posminusneg,
                      TASK_vmu = mean5_vmu, TASK_s=mean5_s,
                      `ESM model AR1` = PANAS_AR1,
                      `ESM model innovation` = PANAS_LOGVAR,
                      `task model AR1` = TASK_AR1,
                      `task model innovation` = TASK_LOGVAR,
                      `ESM vmu` = mean5_vmu_posminusneg, `ESM S` = mean5_s_posminusneg,
                      `task vmu` = mean5_vmu, `task S` = mean5_s
         ),
             use = "complete.obs")

corpmat = cor_pmat(df_master %>% dplyr::select(mean5_vmu_posminusneg,mean5_s_posminusneg,
                           PANAS_AR1,PANAS_LOGVAR,
                           mean5_vmu,mean5_s,
                           TASK_AR1,TASK_LOGVAR) %>% 
               rename(EMA_vmu = mean5_vmu_posminusneg,
                      EMA_s = mean5_s_posminusneg,
                      TASK_vmu = mean5_vmu, TASK_s=mean5_s,
                      `ESM model AR1` = PANAS_AR1,
                      `ESM model innovation` = PANAS_LOGVAR,
                      `task model AR1` = TASK_AR1,
                      `task model innovation` = TASK_LOGVAR,
                      `ESM vmu` = mean5_vmu_posminusneg, `ESM S` = mean5_s_posminusneg,
                      `task vmu` = mean5_vmu, `task S` = mean5_s
         ),
             use = "complete.obs")

# Create individual plots with R²
p1 <- ggplot(df_master, aes(x = mean5_s, y = TASK_LOGVAR)) +
  geom_point(size=0.5,alpha=0.5) +
  geom_smooth(method = "lm", se = TRUE,color=noiseColor) +
  labs(x = "task noise", y = "task log innovation variance") +
  annotate("text", 
           x = Inf, y = Inf, 
           label = paste("R² =", round(summary(lm(TASK_LOGVAR ~ mean5_s, data = df_master))$r.squared, 3)),
           hjust = 1.1, vjust = 10.5, size = 4)

p2 <- ggplot(df_master, aes(x = mean5_vmu, y = TASK_AR1)) +
  geom_point(size=0.5,alpha=0.5) +
  geom_smooth(method = "lm", se = TRUE,color=vmuColor) +
  labs(x = "task volatility", y = "task AR1") +
  annotate("text", 
           x = Inf, y = Inf, 
           label = paste("R² =", round(summary(lm(TASK_AR1 ~ mean5_vmu, data = df_master))$r.squared, 3)),
           hjust = 1.1, vjust = 1.5, size = 4)

p3 <- ggplot(df_master, aes(x = mean5_s_posminusneg, y = PANAS_LOGVAR)) +
geom_point(size=0.5,alpha=0.5) +
  geom_smooth(method = "lm", se = TRUE,color=noiseColor) +
  labs(x = "ESM noise", y = "ESM log innovation variance") +
  annotate("text", 
           x = Inf, y = Inf, 
           label = paste("R² =", round(summary(lm(PANAS_LOGVAR ~ mean5_s_posminusneg, data = df_master))$r.squared, 3)),
           hjust = 1.1, vjust = 1.5, size = 4)

p4 <- ggplot(df_master, aes(x = mean5_vmu_posminusneg, y = PANAS_AR1)) +
geom_point(size=0.5,alpha=0.5) +
  geom_smooth(method = "lm", se = TRUE,color=vmuColor) +
  labs(x = "ESM volatility", y = "task AR1") +
  annotate("text", 
           x = Inf, y = Inf, 
           label = paste("R² =", round(summary(lm(PANAS_AR1 ~ mean5_vmu_posminusneg, data = df_master))$r.squared, 3)),
           hjust = 1.1, vjust = 1.5, size = 4)

# Create the correlation plot
p5 <- ggcorrplot::ggcorrplot(cormat, p.mat = corpmat, type = "upper",
                             lab = TRUE, pch.col = "brown") +
  labs(title = "Comparison with VAR1 model",
       caption = "black box = task~ESM associations; green box = Bayesian Filter~AR1 model associations") +
  theme(axis.text = element_text(size = 8),  # Increased from 2 for readability
        axis.text.x = element_text(angle = 45, hjust = 1),
        plot.title = element_text(size = 14))+
  geom_rect(aes(xmin = 1 - 0.5, xmax = 1 + 0.5, ymin = 2 - 0.5, ymax = 2 + 0.5),
            fill = NA, color = "green", linewidth = 1, inherit.aes = FALSE)+
  geom_rect(aes(xmin = 2 - 0.5, xmax = 2 + 0.5, ymin = 3 - 0.5, ymax = 3 + 0.5),
            fill = NA, color = "green", linewidth = 1, inherit.aes = FALSE)+
  geom_rect(aes(xmin = 5 - 0.5, xmax = 5 + 0.5, ymin = 6 - 0.5, ymax = 6 + 0.5),
            fill = NA, color = "green", linewidth = 1, inherit.aes = FALSE)+
  geom_rect(aes(xmin = 6 - 0.5, xmax = 6 + 0.5, ymin = 7 - 0.5, ymax = 7 + 0.5),
            fill = NA, color = "green", linewidth = 1, inherit.aes = FALSE)+
  geom_rect(aes(xmin = 1 - 0.5, xmax = 1 + 0.5, ymin = 4 - 0.5, ymax = 4 + 0.5),
            fill = NA, color = "black", linewidth = 1, inherit.aes = FALSE)+
  geom_rect(aes(xmin = 2 - 0.5, xmax = 2 + 0.5, ymin = 5 - 0.5, ymax = 5 + 0.5),
            fill = NA, color = "black", linewidth = 1, inherit.aes = FALSE)+
  geom_rect(aes(xmin = 3 - 0.5, xmax = 3 + 0.5, ymin = 6 - 0.5, ymax = 6 + 0.5),
            fill = NA, color = "black", linewidth = 1, inherit.aes = FALSE)+
  geom_rect(aes(xmin = 4 - 0.5, xmax = 4 + 0.5, ymin = 7 - 0.5, ymax = 7 + 0.5),
            fill = NA, color = "black", linewidth = 1, inherit.aes = FALSE)

# Top row only in patchwork; stack with p5 via magick so panel A's y-axis is not
# stretched across the full figure width (a quirk of (p1|...|p4) / p5 in patchwork).
pw_top <- (p1 | p2 | p3 | p4) + plot_annotation(tag_levels = "A")
pw_bottom <- p5 + plot_annotation(tag_levels = list(c("E")))

fig_w <- 10
fig_h <- 8
h_top <- fig_h * 1 / 3
h_bot <- fig_h * 2 / 3
tmp_top <- tempfile(fileext = ".png")
tmp_bot <- tempfile(fileext = ".png")
ggsave(tmp_top, pw_top, width = fig_w, height = h_top, dpi = 300)
ggsave(tmp_bot, pw_bottom, width = fig_w, height = h_bot, dpi = 300)
figure_s11 <- magick::image_append(
  c(magick::image_read(tmp_top), magick::image_read(tmp_bot)),
  stack = TRUE
)
unlink(c(tmp_top, tmp_bot))
figure_s11
magick::image_write(figure_s11, path = "../figures/figure_s11.png")
```
## test-retest reliability of new measures
```{r}
#AR and vmu has similar test-retest
# vmu_retest
cor(df_task_var1$day1_block1_AR1,df_task_var1$day2_block1_AR1, use = "pairwise.complete.obs")
cor(df_master$mean5_vmu_d1r1,df_master$mean5_vmu_d2r1, use = "pairwise.complete.obs")

#VAR has higher test-retest
# s_retest
cor(df_task_var1$day1_block1_LOGVAR,df_task_var1$day2_block1_LOGVAR, use = "pairwise.complete.obs")
cor(df_master$mean5_s_d1r1,df_master$mean5_s_d2r1, use = "pairwise.complete.obs")
```

```{r}
s1 <- summary(lm(scale(PANAS_LOGVAR) ~ scale(TASK_AR1)+ scale(TASK_LOGVAR), df_master))
s2 <- summary(lm(scale(PANAS_AR1) ~ scale(TASK_AR1)+ scale(TASK_LOGVAR), df_master))
summary(lm(scale(PANAS_LOGVAR) ~ scale(TASK_AR1)+ scale(TASK_LOGVAR) + scale(TASK_MEAN), df_master))
summary(lm(scale(PANAS_AR1) ~ scale(TASK_AR1)+ scale(TASK_LOGVAR) + scale(TASK_MEAN), df_master))

bars2 <- Reduce(rbind,
       list(as.data.frame(s1$coefficients) %>% 
              mutate(reg = "ESM innovation"),
            as.data.frame(s2$coefficients) %>% 
              mutate(reg = "ESM AR"))) %>% 
  rownames_to_column() %>% 
  rename(variable = rowname,
         se = `Std. Error`,
         p_val = `Pr(>|t|)`) %>% 
  mutate(sig = ifelse(p_val < .001, "***",
                      ifelse(p_val < .01, "**",
                             ifelse(p_val < .05,"*",
                                    ifelse(p_val < .1,"†","ns")))))

bars2$variable[grepl("TASK_AR1",bars2$variable)] <- "task AR"
bars2$variable[grepl("TASK_LOGVAR",bars2$variable)] <- "task innovation"

bars2 <- bars2 %>% 
  mutate(alpha = ifelse(grepl("AR", variable) & grepl("AR", reg), "1", 
                               ifelse(grepl("innovation", variable) & grepl("innovation", reg), "1" ,"0")))


ggplot(bars2 %>% 
         filter(!grepl("Intercept",variable)) %>% 
         mutate(variable = factor(variable, levels = c("task innovation","task AR")),
                reg = factor(reg,levels = c("ESM innovation","ESM AR") )))+
  geom_col(aes(x = variable, y = Estimate, fill = variable, alpha = alpha),
           width = 0.5)+
  geom_errorbar(aes(x = variable, ymin = Estimate - se, ymax = Estimate + se),
                width = 0.1)+
  facet_wrap(~reg)+
  scale_fill_manual(values = c("#66C2A5","#8DA0CB"))+
  scale_alpha_manual(values = c("1" = 1, "0" = 0.5), guide = "none")+
  labs(y = "Standardized beta",
       title = "Regression weights (multiple regression)",
       x = "")+
  geom_text(aes(x = variable, y = (Estimate + (Estimate) / abs(Estimate) * se  + (Estimate) / abs(Estimate) * 0.05), label = sig))+
  ylim(-0.35,0.8)+
  theme(legend.position = "none")

ggsave("../figures/figure_s12.png",width = 6, height = 4)
```



# make the master correlation matrix
```{r}
df_corr <- df_master %>% 
                    ungroup() %>% 
                    dplyr::select(PAminusNA_mean,PAminusNA_sd,PAminusNA_mssd,AR_PAminusNA_sum,
                                  mean5_vmu_posminusneg,mean5_s_posminusneg,PANAS_MEAN,PANAS_AR1,PANAS_LOGVAR,
                                  moodrate_mean,moodrate_sd,moodrate_mssd,AR_task,mean5_vmu,mean5_s,
                                  TASK_MEAN,TASK_AR1,TASK_LOGVAR) %>% 
  rename(`ESM mean` = PAminusNA_mean,`ESM AR` = AR_PAminusNA_sum, `ESM rmssd` = PAminusNA_mssd,`ESM sd`=PAminusNA_sd,
         `ESM vmu` = mean5_vmu_posminusneg, `ESM S` = mean5_s_posminusneg,
         `ESM model mean` = PANAS_MEAN,
         `task mean` = moodrate_mean,`task AR`= AR_task,`task rmssd` = moodrate_mssd,`task sd` = moodrate_sd, `task vmu` = mean5_vmu,
         `task S`= mean5_s,
         `ESM model AR1` = PANAS_AR1,
         `ESM model innovation` = PANAS_LOGVAR,
         `task model AR1` = TASK_AR1,
         `task model innovation` = TASK_LOGVAR,
         `task model mean` = TASK_MEAN
         )

corm <- cor(df_corr,
            method = "pearson", use = "complete.obs")

p.mat <- cor_pmat(df_corr,
            method = "pearson", use = "complete.obs")

knitr::kable(corm, digits = 3)
knitr::kable(p.mat, digits = 3)

ggcorrplot::ggcorrplot(corm, 
           p.mat = p.mat, lab = T, insig = "blank", type = "lower",tl.cex = 10,lab_size = 3,
           colors = c("skyblue", "white", "orange"))+
  geom_rect(aes(xmin = 10 - 0.5, xmax = 10 + 0.5, ymin = 2 - 0.5, ymax = 2 + 0.5),
              fill = NA, color = "red", size = 1)+
  geom_rect(aes(xmin = 11 - 0.5, xmax = 11 + 0.5, ymin = 3 - 0.5, ymax = 3 + 0.5),
              fill = NA, color = "red", size = 1)+
  geom_rect(aes(xmin = 12 - 0.5, xmax = 12 + 0.5, ymin = 4 - 0.5, ymax = 4 + 0.5),
              fill = NA, color = "red", size = 1)+
  geom_rect(aes(xmin = 13 - 0.5, xmax = 13 + 0.5, ymin = 5 - 0.5, ymax = 5 + 0.5),
              fill = NA, color = "red", size = 1)+
  geom_rect(aes(xmin = 14 - 0.5, xmax = 14 + 0.5, ymin = 6 - 0.5, ymax = 6 + 0.5),
              fill = NA, color = "red", size = 1)+
  geom_rect(aes(xmin = 16 - 0.5, xmax = 16 + 0.5, ymin = 8 - 0.5, ymax = 8 + 0.5),
              fill = NA, color = "red", size = 1)+
  geom_rect(aes(xmin = 17 - 0.5, xmax = 17 + 0.5, ymin = 9 - 0.5, ymax = 9 + 0.5),
              fill = NA, color = "red", size = 1)+
  geom_rect(aes(xmin = 13 - 0.52, xmax = 14 + 0.52, ymin = 5 - 0.52, ymax = 6 + 0.52),
              fill = NA, color = "black", size = 0.5, linetype = "dashed")

ggsave("../figures/figure_s13.png",width = 8, height = 7)

```

### AR(1) model parameters with affective impact

```{r}
s1a <- summary(lm(scale(TASK_LOGVAR) ~ scale(X1), df_master))
s1b <- summary(lm(scale(TASK_LOGVAR) ~ scale(X1) + scale(X2), df_master))
s1c <- summary(lm(scale(TASK_LOGVAR) ~ scale(X1) + scale(X2) + scale(X3), df_master))

s2a <- summary(lm(scale(TASK_AR1) ~ scale(X1), df_master))
s2b <- summary(lm(scale(TASK_AR1)  ~ scale(X1) + scale(X2), df_master))
s2c <- summary(lm(scale(TASK_AR1) ~ scale(X1) + scale(X2) + scale(X3), df_master))


df_master$residuals1[!is.na(df_master$X1)] <- as.vector(residuals(s1a))
s1bb <- summary(lm(scale(residuals1) ~ scale(X2), df_master))
df_master$residuals2[!is.na(df_master$X2)] <- as.vector(residuals(s1bb))
s1cc <- summary(lm(scale(residuals2) ~ scale(X3), df_master))

df_master$residuals1[!is.na(df_master$X1)] <- as.vector(residuals(s2a))
s2bb <- summary(lm(scale(residuals1) ~ scale(X2), df_master))
df_master$residuals2[!is.na(df_master$X2)] <- as.vector(residuals(s2bb))
s2cc <- summary(lm(scale(residuals2) ~ scale(X3), df_master))

bars <- Reduce(rbind,
       list(as.data.frame(rbind(s1a$coefficients[2,],
                                s1bb$coefficients[2,],
                                s1cc$coefficients[2,]))
                          %>% 
              mutate(reg = "task model innovation"),
            as.data.frame(rbind(s2a$coefficients[2,],
                                s2bb$coefficients[2,],
                                s2cc$coefficients[2,])) %>% 
              mutate(reg = "task model AR"))) %>% 
  rownames_to_column() %>% 
  rename(variable = rowname,
         se = `Std. Error`,
         p_val = `Pr(>|t|)`) %>% 
  mutate(sig = ifelse(p_val < .001, "***",
                      ifelse(p_val < .01, "**",
                             ifelse(p_val < .05,"*",
                                    ifelse(p_val < .1,"†","ns")))))

bars$variable <- rep(c("trial -1~3","trial -4~6","trial -7~9"),2)

p1 <- ggplot(bars %>% 
         filter(!grepl("Intercept",variable)) %>% 
         mutate(variable = factor(variable, levels = c("trial -1~3","trial -4~6","trial -7~9")),
                reg = factor(reg,levels = c("task model innovation","task model AR") )))+
  geom_col(aes(x = variable, y = Estimate, fill = reg),
           width = 0.5)+
  geom_errorbar(aes(x = variable, ymin = Estimate - se, ymax = Estimate + se),
                width = 0.1)+
  facet_wrap(~reg)+
  scale_fill_brewer(palette = "Set2")+
  # scale_fill_manual(values = c(muColor,vmuColor,noiseColor))+
  scale_alpha_manual(values = c("1" = 1, "0" = 0.5), guide = "none")+
  labs(y = "Standardized regression weights",
       x = "Time of affective impact",
       title = "Reward outcome")+
  geom_text(aes(x = variable, y = (Estimate + (Estimate) / abs(Estimate) * se  
                                   + (Estimate) / abs(Estimate) * 0.05), label = sig))+
  theme(legend.position = "none")+
  ylim(-0.55,1)+ 
  theme(axis.text.x = element_text(angle = 45,hjust=1))


s1a <- summary(lm(scale(PANAS_LOGVAR) ~ scale(X1), df_master))
s1b <- summary(lm(scale(PANAS_LOGVAR) ~ scale(X1) + scale(X2), df_master))
s1c <- summary(lm(scale(PANAS_LOGVAR) ~ scale(X1) + scale(X2) + scale(X3), df_master))

s2a <- summary(lm(scale(PANAS_AR1) ~ scale(X1), df_master))
s2b <- summary(lm(scale(PANAS_AR1)  ~ scale(X1) + scale(X2), df_master))
s2c <- summary(lm(scale(PANAS_AR1) ~ scale(X1) + scale(X2) + scale(X3), df_master))

df_master$residuals1[!is.na(df_master$X1)] <- as.vector(residuals(s1a))
s1bb <- summary(lm(scale(residuals1) ~ scale(X2), df_master))
df_master$residuals2[!is.na(df_master$X2)] <- as.vector(residuals(s1bb))
s1cc <- summary(lm(scale(residuals2) ~ scale(X3), df_master))

df_master$residuals1[!is.na(df_master$X1)] <- as.vector(residuals(s2a))
s2bb <- summary(lm(scale(residuals1) ~ scale(X2), df_master))
df_master$residuals2[!is.na(df_master$X2)] <- as.vector(residuals(s2bb))
s2cc <- summary(lm(scale(residuals2) ~ scale(X3), df_master))


bars <- Reduce(rbind,
       list(as.data.frame(rbind(s1a$coefficients[2,],
                                s1bb$coefficients[2,],
                                s1cc$coefficients[2,]))
                          %>% 
              mutate(reg = "ESM model innovation"),
            as.data.frame(rbind(s2a$coefficients[2,],
                                s2bb$coefficients[2,],
                                s2cc$coefficients[2,])) %>% 
              mutate(reg = "ESM model AR"))) %>% 
  rownames_to_column() %>% 
  rename(variable = rowname,
         se = `Std. Error`,
         p_val = `Pr(>|t|)`) %>% 
  mutate(sig = ifelse(p_val < .001, "***",
                      ifelse(p_val < .01, "**",
                             ifelse(p_val < .05,"*",
                                    ifelse(p_val < .1,"†","ns")))))

bars$variable <- rep(c("trial -1~3","trial -4~6","trial -7~9"),2)

p2 <- ggplot(bars %>% 
         filter(!grepl("Intercept",variable)) %>% 
         mutate(variable = factor(variable, levels = c("trial -1~3","trial -4~6","trial -7~9")),
                reg = factor(reg,levels = c("ESM model innovation","ESM model AR") )))+
  geom_col(aes(x = variable, y = Estimate, fill = reg),
           width = 0.5)+
  geom_errorbar(aes(x = variable, ymin = Estimate - se, ymax = Estimate + se),
                width = 0.1)+
  facet_wrap(~reg)+
    ylim(-0.55,1)+ 
  scale_fill_brewer(palette = "Set2")+
  # scale_fill_manual(values = c(muColor,vmuColor,noiseColor))+
  scale_alpha_manual(values = c("1" = 1, "0" = 0.5), guide = "none")+
  labs(y = "Standardized regression weights",
       x = "Time of affective impact",
       title = "Reward outcome")+
  geom_text(aes(x = variable, y = (Estimate + (Estimate) / abs(Estimate) * se  
                                   + (Estimate) / abs(Estimate) * 0.05), label = sig))+
  theme(legend.position = "none")+
  theme(axis.text.x = element_text(angle = 45,hjust=1))

p1/p2

ggsave("../figures/figure_s19.png",width = 6, height = 7)
```

# report association with self-reported questionnaires
```{r}
df_corr_personality <- df_master %>% 
                    ungroup() %>% 
                    dplyr::select(TEPS_ant_sum,TEPS_con_sum,HPS_sum,CESD_sum,STAI_TA_sum,STAI_SA_sum,
                                  mean5_mu_posminusneg,
                                  mean5_vmu_posminusneg,mean5_s_posminusneg,
                                  mean5_mu,mean5_vmu,mean5_s) %>% 
  rename(`ESM mean` = mean5_mu_posminusneg,
         `ESM volatility` = mean5_vmu_posminusneg,`ESM noise` = mean5_s_posminusneg,
         `task mean` = mean5_mu,`task volatility` = mean5_vmu,
         `task noise`= mean5_s) 

corm <- cor(df_corr_personality,
            method = "pearson", use = "complete.obs")

p.mat <- cor_pmat(df_corr_personality,
            method = "pearson", use = "complete.obs")

ggcorrplot::ggcorrplot(corm, 
           p.mat = p.mat, lab = T, insig = "pch", type = "lower",tl.cex = 10,lab_size = 3,
           colors = c("skyblue", "white", "orange"))

ggsave("../figures/figure_s14.png",width = 6, height = 5)
```

