---
title: "read_data_task_ema"
author: "Ryan Yan"
date: "2024-01-16"
output: html_document
---

<!--
Purpose: load every raw per-subject CSV (baseline questionnaires, PANAS EMA, the four
apple/reward-learning task runs, the two wheel-of-fortune runs) and the MATLAB-derived
Bayesian-filter estimate CSVs, clean/join them into df_master/df_days/df_mood_AR/etc.,
and compute the exclusion list `subj_exclude_novariance_rl`.

Inputs: <repo_root>/data/raw/raw_csv/*.csv (raw, not shared), <repo_root>/data/*.csv
  (MATLAB filter output -- apple_moodrate_params.csv,
  apple_moodrate_params_wholeday.csv, and ema_panas_params.csv specifically come
  from scripts/01_bayesian_filter/step4_data_org.m, which needs
  Gor_PANAS_Mod_Data_anonymized.mat -- see the README's "Two-tier
  reproducibility" section), the private data/raw/subject_id_crosswalk.csv
  (subject -> Prolific_Id, used to bridge those MATLAB CSVs' anonymized "id"
  back to a real Prolific.Id before joining -- see attach_prolific_id() below),
  and an external Prolific demographics export (path hardcoded below, lives
  outside this repo).
Outputs: intermediate (non-anonymized) CSVs written back to <repo_root>/data/.
Requires in scope already: `panas_results`, `mood_results` (from run_var1model.R).

Tier 2 script: needs raw per-subject data that is NOT included in this OSF package.
Not meant to be knit directly -- it is rendered by write_anonymized_data.R, which sets
the knit working directory to the repo root (so `data/...` paths below resolve there).
-->

## baseline questionnaires
```{r load data}
indir <- 'data/raw/raw_csv/'
outdir <- 'data/'
#load initial questionnaires
df_init <- read_csv(paste0(indir,'baseline_questionnaires.csv'))

df_init <- df_init%>% 
  rename(Prolific.Id = Last.Name)%>%
  filter(Prolific.Id != '')%>% #filter those without prolific id
  dplyr::select(Survey.Started.Date,Response.Id:Trigger.Index,During.the.past.week....I.was.bothered.by.things.that.usually.don.t.bother.me.:During.the.past.week....I.could.not.get.going,#25-44
Understand.the.reasons.when.I.feel.very.excited.or.happy.:Can.slow.myself.down.when.I.want.to.,#46-69
When.I.hear.about.a.new.movie.starring.my.favorite.actor.I.can.t.wait.to.see.it.:When.something.exciting.is.coming.up.in.my.life.I.really.look.forward.to.it.,#71-88
Right.now...I.feel.calm:Right.now....I.feel.pleasant,#90-109
In.general....I.feel.pleasant:In.general...I.get.in.a.state.of.tension.or.turmoil.as.I.think.over.recent.concerns.and.interests) #111-130

#load PANAS
df_PANAS <- read.csv(paste0(indir,"ema_panas_sf.csv"))

df_PANAS <- df_PANAS %>%
  rename(Prolific.Id = Last.Name) %>%
  filter(Prolific.Id != '') %>% #filter those without prolific id
  dplyr::select(Response.Id:Trigger.Index, 
         Interested, Distressed, Excited, Upset, Strong,
         Guilty, Scared, Hostile, Enthusiastic, Proud, 
         Irritable, Alert, Ashamed, Inspired, Nervous,
         Determined, Attentive, Jittery, Active, Afraid) 
```

```{r sort obs. and delete duplicates}
#-----------PANAS-----------
df_PANAS <- df_PANAS[order(df_PANAS$Prolific.Id,df_PANAS$Trigger.Index),] #order the data frame by user id and trigger index

#return user ids and the number of rows they have (ie. No of PANAS completed)
user_PANAS <- df_PANAS%>%
  group_by(Prolific.Id)%>%
  count()%>%
  filter(n >= 90)#change the number into the wanted threshold!
  
df_PANAS <- df_PANAS %>%
  filter(Prolific.Id %in% user_PANAS$Prolific.Id) 

#only keep the first of all duplicate cases
df_PANAS <- df_PANAS%>%
  group_by(Prolific.Id,Trigger.Index)%>%
  slice_head()%>%
  ungroup()

#calculate PA and NA for PANAS
df_PANAS <- df_PANAS %>%
  mutate(PA_sum = Interested + Excited + Strong + Enthusiastic + Proud + Alert + Inspired + Determined + Attentive + Active) %>%
  mutate(NA_sum = Distressed + Upset + Guilty + Scared + Hostile + Irritable + Ashamed + Nervous + Jittery + Afraid) %>% 
  mutate(PAminusNA_sum = PA_sum - NA_sum,
         PANA_sum = PA_sum + NA_sum)

# #check if there is still any duplicate, should be none!
df_PANAS%>%
  group_by(Prolific.Id,Trigger.Index)%>%
  count()%>%
  filter(n != 1)

df_PANAS <- df_PANAS%>%
  mutate(day_index = (Trigger.Index-1) %/%6 +1)%>%
  mutate(time_index = (Trigger.Index-1) %%6 + 1)%>%
  mutate(day_time_index = paste0(day_index,'_',time_index)) %>% 
  relocate(c(day_index,time_index),.after = Trigger.Index)

# get max and min rating value of each person for converting mu back into original rating space
df_PANAS <- df_PANAS %>% 
  group_by(Prolific.Id) %>% 
  mutate(max_PAminusNA = max(PAminusNA_sum, na.rm = T),
         min_PAminusNA = min(PAminusNA_sum, na.rm = T))
```

## check uniform responders
```{r}
df_PANAS_uniform_response <-df_PANAS %>%
  rowwise() %>%
  mutate(panas_ndistinct = dplyr::n_distinct(c_across(Interested:Afraid), na.rm = TRUE)) %>%
  ungroup() %>%
  filter(panas_ndistinct == 1) %>% # drop rows with the same response on all PANAS items
  dplyr::select(-panas_ndistinct) %>% 
  group_by(Prolific.Id) %>% 
  count() %>% 
  left_join(user_PANAS %>% rename(total = n)) %>% 
  mutate(proportion_flatline = n/total)

ggplot(df_PANAS_uniform_response, aes(x = proportion_flatline))+
  geom_histogram()

subj_panas_flatliner <- df_PANAS_uniform_response %>% filter(proportion_flatline > 0.3)

subj_panas_flatliner <- subj_panas_flatliner$Prolific.Id
```



```{r}
#-----------init Q-----------
df_init <- df_init%>%
  filter(Prolific.Id %in% user_PANAS$Prolific.Id)%>%
  filter(Survey.Name != 'MIS Consent Form')%>%
  mutate(Trigger.Date = as.Date(Trigger.Date,"%d/%m/%Y"))

#reorder
df_init <- df_init[order(df_init$Prolific.Id,df_init$Trigger.Index,df_init$Trigger.Date),]

#delete duplicates
df_init <- df_init%>%
  group_by(Prolific.Id)%>%
  slice_head(n = 4)%>% #only take the first four rows earliest in time; comment this line to see the original data with duplicates
  ungroup()

df_init_date <- unique(df_init %>% 
  dplyr::select(Prolific.Id,Trigger.Date))
```

```{r calc and aggregate baseline questionnaires}
#-----------CESD: 20 items-----------
#item already reversely coded
df_CESD <- df_init%>%
  filter(Survey.Name == 'CESD')%>%
  dplyr::select(Prolific.Id,
         During.the.past.week....I.was.bothered.by.things.that.usually.don.t.bother.me.:During.the.past.week....I.could.not.get.going)#20-39

names(df_CESD)[2:21] <- paste0('CESD',1:20)
df_CESD$CESD_sum <- rowSums(df_CESD[,2:21])

#-----------HPS: 24 items---------------
df_HPS <- df_init%>%
  filter(Survey.Name == 'HPS')%>%
  dplyr::select(Prolific.Id,
         Understand.the.reasons.when.I.feel.very.excited.or.happy.:Can.slow.myself.down.when.I.want.to.)
#

names(df_HPS)[2:25] <- paste0('HPS',1:24)
df_HPS$HPS_sum <- rowSums(df_HPS[,2:25])
ltm::cronbach.alpha(df_HPS[2:25])

#-----------TEPS: 18 items---------------
df_TEPS <- df_init%>%
  filter(Survey.Name == 'TEPS')%>%
  dplyr::select(Prolific.Id,
         When.I.hear.about.a.new.movie.starring.my.favorite.actor.I.can.t.wait.to.see.it.:When.something.exciting.is.coming.up.in.my.life.I.really.look.forward.to.it.)

names(df_TEPS)[2:19] <- paste0('TEPS',1:18)
df_TEPS$TEPS_sum <- rowSums(df_TEPS[,2:19])
df_TEPS$TEPS_ant_sum <- rowSums(df_TEPS[,1+c(1,4,6,8,10,11,13,15,16,18)])
df_TEPS$TEPS_con_sum <- rowSums(df_TEPS[,1+c(2,3,5,7,9,12,14,17)])
ltm::cronbach.alpha(df_TEPS[2:19])

#-----------STAI: 20*2 items---------------
df_STAI <- df_init%>%
  filter(Survey.Name == 'STAI')%>%
  dplyr::select(Prolific.Id,
         Right.now...I.feel.calm:In.general...I.get.in.a.state.of.tension.or.turmoil.as.I.think.over.recent.concerns.and.interests)

names(df_STAI)[2:21] <- paste0('STAI_SA',1:20)
names(df_STAI)[22:41] <- paste0('STAI_TA',1:20)
df_STAI$STAI_SA_sum <- rowSums(df_STAI[,2:21])
df_STAI$STAI_TA_sum <- rowSums(df_STAI[,22:41])

#aggregate init Qs
df_init_sum <- Reduce(merge, list(df_CESD, df_HPS, df_TEPS, df_STAI))
  # filter(Prolific.Id %in%PANAS_and_gorilla_user$Prolific.Id)

#sanity check
names(df_init_sum)
length(df_init_sum$Prolific.Id)
```

## gorilla task
```{r}
#load data files
df_d1b1 <- read.csv(paste0(indir,"apple_d1b1.csv")) #struct learn day 1 block 1
df_d1b1$day_block <- 'day1_block1'
df_d1b2 <- read.csv(paste0(indir,"apple_d1b2.csv")) #struct learn day 1 block 2
df_d1b2$day_block <- 'day1_block2'
df_d2b1 <- read.csv(paste0(indir,"apple_d2b1.csv")) #struct learn day 2 block 1
df_d2b1$day_block <- 'day2_block1'
df_d2b2 <- read.csv(paste0(indir,"apple_d2b2.csv")) #struct learn day 2 block 2
df_d2b2$day_block <- 'day2_block2'

nrow(df_d1b1) #99997, should be the same for below; if not, check the reason
nrow(df_d1b2) #99801
nrow(df_d2b1) #99993
nrow(df_d2b2) #100112

df_all <- rbind(df_d1b1,df_d1b2,df_d2b1,df_d2b2)

##sanity check
#all subjects
nsub = length(unique(df_all$Participant.Public.ID))-1 #354, but is actually 353!! because the last participant was ""
sub_list <- unique(df_all$Participant.Public.ID)[1:nsub]

df_all <- df_all %>%
  filter(Participant.Public.ID%in%sub_list)%>% #get rid of the ""
  filter(component != '')%>% #get rid of the first row for each participant which is empty
  dplyr::select(Participant.Public.ID, Reaction.Time:totalmon,outcome_mag, outcome, component, moodrate,day_block,Local.Date)%>%
  group_by(Participant.Public.ID,day_block,component,Local.Date)%>%
  mutate(row_id_par = row_number())%>%
  ungroup()%>%
  group_by(Participant.Public.ID)%>%
  mutate(moodrate_scaled = as.numeric(scale(moodrate)))%>%
  ungroup()

count(df_all, Participant.Public.ID)%>% 
  filter(n > 1124)

#get rid of duplicates
df_all <- df_all %>% 
   group_by(Participant.Public.ID,day_block)%>%
   mutate(Trial.Index = ifelse(component == "moodrate",lead(Trial.Index)-1,Trial.Index)) %>% 
   group_by(Participant.Public.ID,day_block,component,Trial.Index)%>%
  mutate(rowid = row_number()) %>% 
   filter(rowid == 1) %>% 
  dplyr::select(-rowid)

count(df_all %>% ungroup(), Participant.Public.ID)

df_totalmon <- df_all %>% 
  filter(Trial.Index==120,component=="choice") %>% 
  dplyr::select(Participant.Public.ID,day_block,Trial.Index,totalmon) %>% 
  pivot_wider(names_from = day_block, values_from = totalmon)
```


## wheel of fortune
```{r impoart WoF and make data frame WoF~moodrate}
#--------------wof--------------
df_wof1 <- read.csv(paste0(indir,"wof_d1.csv"))%>% #WoF day 1
  filter(component != 'wof')%>%
  dplyr::select(Participant.Public.ID, randomiser.tc6s, wofoutcome,Local.Date)%>%
  rename(Local.Date.D1 = Local.Date) %>% 
  mutate(wof_order = randomiser.tc6s,wofoutcome1 = wofoutcome)%>%
  dplyr::select(-randomiser.tc6s,-wofoutcome)

df_wof2 <- read.csv(paste0(indir,"wof_d2.csv"))%>% #WoF day 2
  filter(component != 'wof')%>%
  dplyr::select(Participant.Public.ID, wofoutcome,Local.Date)%>%
  rename(Local.Date.D2 = Local.Date) %>% 
  mutate(wofoutcome2 = wofoutcome)%>%
  dplyr::select(-wofoutcome)

df_wof <- left_join(df_wof1,df_wof2, by = "Participant.Public.ID")%>%
  filter(Participant.Public.ID!='')

#600091ba38fa9b158243c79f was repeated??
df_wof <- df_wof[-which(duplicated(df_wof$Participant.Public.ID)),]

df_wof <- df_wof %>% 
  mutate(Local.Date.D1=as.POSIXct(Local.Date.D1, format = "%d/%m/%Y %H:%M:%S", tz = "UTC"),
         Local.Date.D2=as.POSIXct(Local.Date.D2, format = "%d/%m/%Y %H:%M:%S", tz = "UTC"),
        Local.Date.D1.Day = as.Date(Local.Date.D1),
        Local.Date.D2.Day = as.Date(Local.Date.D2),
        day_diff = Local.Date.D2.Day-Local.Date.D1.Day)

#--------mood rate original-------
df_mood <- df_all%>%
  filter(component == 'moodrate')%>%
  dplyr::select(Participant.Public.ID, moodrate, day_block)%>%
  group_by(Participant.Public.ID,day_block)%>%
  mutate(Index = row_number())%>%
  ungroup() %>% 
  filter(Index <= 41)#should be between 1 and 41

# get the participants who only had 1 rating across the runs
subj_exclude_novariance_rl <- df_mood %>% 
  # filter(day_block %in% c("day1_block1","day2_block1")) %>% 
  group_by(Participant.Public.ID,day_block) %>% 
  summarise(n = length(unique(moodrate))) %>% 
  filter(n==1) %>%
  mutate(subj_day_block = paste0(Participant.Public.ID,"_",day_block))

df_mood <- df_mood %>%
  mutate(subj_day_block = paste0(Participant.Public.ID,"_",day_block)) %>% 
  filter(!subj_day_block %in% subj_exclude_novariance_rl$subj_day_block)

#add variable: day and block
#find another way! loops are too time-consuming
df_mood$day[df_mood$day_block == "day1_block1" | df_mood$day_block == "day1_block2"] <- 1
df_mood$block[df_mood$day_block == "day1_block1" | df_mood$day_block == "day2_block1"] <- 1

df_mood$day[df_mood$day_block == "day2_block1" | df_mood$day_block == "day2_block1"] <- 2
df_mood$block[df_mood$day_block == "day1_block2" | df_mood$day_block == "day2_block2"] <- 2

write.csv(df_mood,paste0(outdir,'moodrate_by_trial.csv'))

#--------mood rate scaled--------
df_mood_scaled <- df_all%>%
  filter(component == 'moodrate')%>%
  dplyr::select(Participant.Public.ID, moodrate_scaled, moodrate,day_block)%>%
  group_by(Participant.Public.ID,day_block)%>%
  mutate(Index = row_number())%>%
  ungroup() %>% 
  filter(Index <= 41) %>%
  mutate(subj_day_block = paste0(Participant.Public.ID,"_",day_block)) %>% 
  filter(!subj_day_block %in% subj_exclude_novariance_rl$subj_day_block)

df_mood_scaled$day[df_mood_scaled$day_block == "day1_block1" | df_mood_scaled$day_block == "day1_block2"] <- 1
df_mood_scaled$block[df_mood_scaled$day_block == "day1_block1" | df_mood_scaled$day_block == "day2_block1"] <- 1

df_mood_scaled$day[df_mood_scaled$day_block == "day2_block1" | df_mood_scaled$day_block == "day2_block2"] <- 2
df_mood_scaled$block[df_mood_scaled$day_block == "day1_block2" | df_mood_scaled$day_block == "day2_block2"] <- 2

df_mood_scaled <- left_join(df_mood_scaled,df_wof, by = "Participant.Public.ID") %>% 
  mutate(day_block2 = ifelse(wofoutcome1 == 1 & day == 1, paste0("winday_block",block),
                             ifelse(wofoutcome1 == 1 & day == 2, paste0("loseday_block",block),
                                    ifelse(wofoutcome1 == 0 & day == 1, paste0("loseday_block",block),
                                           ifelse(wofoutcome1 == 0 & day == 2, paste0("winday_block",block),NA)))))
```

```{r}
df_all<-df_all %>%
  mutate(subj_day_block = paste0(Participant.Public.ID,"_",day_block)) %>% 
  filter(!subj_day_block %in% subj_exclude_novariance_rl$subj_day_block) 

#get DF for completion time
df_all %>% 
  filter(component == "moodrate",
         Trial.Index == 0 | is.na(Trial.Index)) %>% 
  ungroup() %>% 
  dplyr::select(Participant.Public.ID,day_block,Local.Date) %>% 
  arrange(Participant.Public.ID)
```

```{r}
#create a dataframe for running the autoregressive model
df_mood_AR <- df_mood %>% 
  dplyr::select(Participant.Public.ID,day_block,moodrate) %>% 
  rename(Prolific.Id = Participant.Public.ID) %>% 
  group_by(Prolific.Id,day_block) %>% 
  mutate(Trigger.Index = row_number()) %>% 
  pivot_wider(names_from = day_block, values_from = moodrate)
```


```{r}
df_wof_react <- rbind(df_mood_scaled %>% 
                        ungroup() %>% 
                        dplyr::select(-Trial.Index,-subj_day_block) %>% 
  filter(block == 1, (Index >= 1 & Index <= 3) | Index == 41),
  df_mood_scaled %>% 
    ungroup() %>% 
    dplyr::select(-Trial.Index,-subj_day_block) %>% 
    filter(block == 2,(Index >= 1 & Index <= 3) | Index == 41)) %>% 
    dplyr::select(-day,-block,-moodrate,-day_block,-wofoutcome2) %>% 
    ungroup() %>% 
    pivot_wider(names_from = c(day_block2,Index), values_from = moodrate_scaled)

df_wof_react <- df_wof_react %>% 
  mutate(winday_X1 = (winday_block2_1 - winday_block1_41), # - (winday_block1_1 - winday_block2_41)
         winday_X2 = winday_block2_2 - winday_block1_41 , #- (winday_block1_2 - winday_block2_41)
         winday_X3 = winday_block2_3 - winday_block1_41 , #- (winday_block1_3 - winday_block2_41)
         loseday_X1 = loseday_block2_1 - loseday_block1_41 , #- (loseday_block1_1 - loseday_block2_41)
         loseday_X2 = loseday_block2_2 - loseday_block1_41 ,#- (loseday_block1_2 - loseday_block2_41)
         loseday_X3 = loseday_block2_3 - loseday_block1_41) #- (loseday_block1_3 - loseday_block2_41)
```


## reorder mood ratings and combine raw and scaled values
```{r}
before_win <- df_mood_scaled %>% 
  filter( (wofoutcome1 == 1 & day == 1 & block == 1) |
           (wofoutcome2 == 1 & day == 2 & block == 1)) %>% 
  mutate(block_type = "before_win")

after_win <- df_mood_scaled %>% 
  filter( (wofoutcome1 == 1 & day == 1 & block == 2) |
           (wofoutcome2 == 1 & day == 2 & block == 2)) %>% 
  mutate(block_type = "after_win")

before_loss <- df_mood_scaled %>% 
  filter( (wofoutcome1 == 0 & day == 1 & block == 1) |
           (wofoutcome2 == 0 & day == 2 & block == 1)) %>% 
  mutate(block_type = "before_loss")

after_loss <- df_mood_scaled %>% 
  filter( (wofoutcome1 == 0 & day == 1 & block == 2) |
           (wofoutcome2 == 0 & day == 2 & block == 2)) %>% 
  mutate(block_type = "after_loss")

df_mood_ratings <- rbind(before_win,after_win,before_loss,after_loss) %>% 
  group_by(Participant.Public.ID) %>% 
  mutate(Mood.Index = Index - 1)#the order of events are mood rating / choice / outcome, so mood rating's index needs to be subtracted by 1

# get max and min rating value of each person for converting mu back into original rating space
#note that because the model estimates mu for each block separately, the range also needs to be for each block
df_mood_ratings <- df_mood_ratings %>% 
  group_by(day_block,Participant.Public.ID) %>% 
  mutate(max_moodrate = max(moodrate, na.rm = T),
         min_moodrate = min(moodrate, na.rm = T))
```


#affective events regression
```{r}
df_betas <- df_all %>% 
  filter(component == "choice") %>% 
  dplyr::select(Participant.Public.ID, Trial.Index,totalmon:outcome,day_block) %>% 
  rename(Index = Trial.Index) %>% 
  mutate(Mood.Index = floor((Index-1)/3)+1) %>% 
  group_by(Participant.Public.ID, day_block,Mood.Index) %>% 
  mutate(Choice.Index = row_number()) %>% 
  ungroup() %>% 
  dplyr::select(Participant.Public.ID, day_block,Mood.Index,Choice.Index,outcome,outcome_mag) %>% 
  group_by(Participant.Public.ID, day_block)%>% 
  mutate(outcome1b = lag(outcome,0),
         outcome2b = lag(outcome,1),
         outcome3b = lag(outcome,2),
         outcome4b = lag(outcome,3),
         outcome5b = lag(outcome,4),
         outcome6b = lag(outcome,5),
         outcome7b = lag(outcome,6),
         outcome8b = lag(outcome,7),
         outcome9b = lag(outcome,8),
         outcome1bo = ifelse(outcome1b == 1, outcome1b, -1), #orthogonalized
         outcome2bo = ifelse(outcome2b == 1, outcome2b, -1),
         outcome3bo = ifelse(outcome3b == 1, outcome3b, -1),
         outcome4bo = ifelse(outcome4b == 1, outcome4b, -1),
         outcome5bo = ifelse(outcome5b == 1, outcome5b, -1),
         outcome6bo = ifelse(outcome6b == 1, outcome6b, -1),
         outcome7bo = ifelse(outcome7b == 1, outcome7b, -1),
         outcome8bo = ifelse(outcome8b == 1, outcome8b, -1),
         outcome9bo = ifelse(outcome9b == 1, outcome9b, -1),
         outcome_mag1b = ifelse(lag(outcome_mag,0) == 0, 0, lag(outcome_mag,0)-5),#orthogonalized
         outcome_mag2b = ifelse(lag(outcome_mag,1) == 0, 0, lag(outcome_mag,1)-5),
         outcome_mag3b = ifelse(lag(outcome_mag,2) == 0, 0, lag(outcome_mag,2)-5),
         outcome_mag4b = ifelse(lag(outcome_mag,3) == 0, 0, lag(outcome_mag,3)-5),
         outcome_mag5b = ifelse(lag(outcome_mag,4) == 0, 0, lag(outcome_mag,4)-5),
         outcome_mag6b = ifelse(lag(outcome_mag,5) == 0, 0, lag(outcome_mag,5)-5),
         outcome_mag7b = ifelse(lag(outcome_mag,6) == 0, 0, lag(outcome_mag,6)-5),
         outcome_mag8b = ifelse(lag(outcome_mag,7) == 0, 0, lag(outcome_mag,7)-5),
         outcome_mag9b = ifelse(lag(outcome_mag,8) == 0, 0, lag(outcome_mag,8)-5),
         outcome_magnitude1b = lag(outcome_mag,0) ,
         outcome_magnitude2b = lag(outcome_mag,1),
         outcome_magnitude3b = lag(outcome_mag,2),
         outcome_magnitude4b = lag(outcome_mag,3),
         outcome_magnitude5b = lag(outcome_mag,4),
         outcome_magnitude6b = lag(outcome_mag,5),
         outcome_magnitude7b = lag(outcome_mag,6),
         outcome_magnitude8b = lag(outcome_mag,7),
         outcome_magnitude9b = lag(outcome_mag,8)) %>%
  filter(Choice.Index == 3) %>% 
  dplyr::select(-outcome,-outcome_mag,-Choice.Index)

df_reg <- full_join(df_betas,df_mood_ratings,
                    by = c("Participant.Public.ID","Mood.Index","day_block"))

```

The MATLAB-derived dataframes read below (`df_gor_Est_raw`/`df_gor_Est*`,
`df_panas_Est`, `df_gor_Est_tc`, `df_panas_Est_tc`) are keyed by `id`, the
*anonymized* sequential subject number written by
`step3_assemble_bayes_model_params.m`/`step4_data_org.m`/`step5_make_bayes_timecourse.m`
(those now run entirely from `RawData_anonymized.mat`, so this package's
`Gor_PANAS_Mod_Data_anonymized.mat` never carries a real Prolific ID). But
`df_master`, `subj_exclude_novariance_rl`, `df_mood_ratings`, and `df_PANAS`
below are all still keyed by the real, non-anonymized `Prolific.Id` at this
point in the pipeline (anonymization happens later, in `write_anonymized_data.R`,
applied to `df_master` etc. as a whole). Bridge `id` -> real `Prolific.Id` via
the private subject-id crosswalk (the same `Prolific.Id -> subject` mapping
`step1_anonymize_raw_data.m` used to anonymize `RawData.mat` in the first
place) wherever these get joined or matched against real-ID-keyed data below,
rather than renaming/using `id` directly as if it were `Prolific.Id` -- that
would silently join on the wrong identity space (anonymized number vs. real
ID) instead of erroring, or type-error like `Can't join x$Prolific.Id ...
y$Prolific.Id due to incompatible types` if the CSV's `id` column got read as
integer. Two helpers below: `attach_prolific_id()` renames `id` to
`Prolific.Id` (for joins keyed by `Prolific.Id`); `anonymized_id_to_prolific_id()`
keeps the column named `id` but replaces its values with the real ID (for
places that need to keep grouping/joining on a column literally called `id`
against other real-ID-keyed data, e.g. `df_gor_Est_tc`/`df_panas_Est_tc` below).
```{r}
subject_id_crosswalk <- read.csv('data/raw/subject_id_crosswalk.csv') # private: subject -> Prolific_Id

attach_prolific_id <- function(df) {
  df %>%
    left_join(subject_id_crosswalk, by = c("id" = "subject")) %>%
    dplyr::select(-id) %>%
    rename(Prolific.Id = Prolific_Id)
}

# Same bridge, but for dataframes that need to keep a column literally named
# `id` (e.g. to `group_by(id, ...)`/`left_join(..., by = c("id", ...))` against
# other real-ID-keyed data below) instead of renaming it to `Prolific.Id`.
# write_anonymized_data.R's own `rename(Prolific.Id = id)` on
# df_gor_Est_tc/df_panas_Est_tc later confirms `id` is expected to hold the
# real Prolific ID throughout this Rmd, not the anonymized number.
anonymized_id_to_prolific_id <- function(df) {
  df %>%
    left_join(subject_id_crosswalk, by = c("id" = "subject")) %>%
    mutate(id = Prolific_Id) %>%
    dplyr::select(-Prolific_Id)
}
```

## Bayesian model estimates
```{r }
df_gor_Est_raw <- read.csv(paste0(outdir,'./apple_moodrate_params.csv')) %>%
  left_join(subject_id_crosswalk, by = c("id" = "subject")) %>% # bridge for subj_day_block only; `id` itself stays the anonymized number below
  mutate(
    subj_day_block = case_when(
      run == "d1r1" ~ paste0(Prolific_Id, "_day1_block1"),
      run == "d2r1" ~ paste0(Prolific_Id, "_day2_block1"),
      run == "d1r2" ~ paste0(Prolific_Id, "_day1_block2"),
      run == "d2r2" ~ paste0(Prolific_Id, "_day2_block2"),
      TRUE ~ NA_character_
    )
  ) %>%
  dplyr::select(-Prolific_Id) %>%
  filter(is.na(subj_day_block) |
           !subj_day_block %in% subj_exclude_novariance_rl$subj_day_block)

df_gor_Est_long <- df_gor_Est_raw %>% 
  filter(run %in% c("d1r1","d2r1","d1r2","d2r2")) 

df_gor_Est_all <- df_gor_Est_raw %>% 
  filter(run %in% c("d1r1","d2r1","d1r2","d2r2")) %>% 
  pivot_wider(id_cols = id,names_from = run, values_from = mean_mu:last_vmu)

df_gor_Est <- df_gor_Est_raw %>% 
  filter(run %in% c("d1r1","d2r1")) %>%  #only take the first run each day
  ungroup() %>% 
  group_by(id) %>% 
  summarise_at(vars(mean_mu:last_vmu), ~mean(.x))

df_gor_Est_wholeday_all <- read.csv(paste0(outdir,'./apple_moodrate_params_wholeday.csv')) %>% 
  group_by(id,run) %>% 
  pivot_wider(id_cols = id,names_from = run, values_from = mean_mu:last_vmu)

df_gor_Est_wholeday <- read.csv(paste0(outdir,'./apple_moodrate_params_wholeday.csv')) %>% 
  ungroup() %>% 
  group_by(id) %>% 
  summarise_at(vars(mean_mu:last_vmu), ~mean(.x))

names(df_gor_Est_wholeday)[2:ncol(df_gor_Est_wholeday)] <- paste0(names(df_gor_Est_wholeday)[2:ncol(df_gor_Est_wholeday)],"_wholeday")

df_gor_Est2 <- df_gor_Est_raw %>% 
  ungroup() %>% 
  group_by(id) %>% 
  summarise_at(vars(mean_mu:last_vmu), ~mean(.x))
names(df_gor_Est2)[2:ncol(df_gor_Est2)] <- paste0(names(df_gor_Est2)[2:ncol(df_gor_Est2)],"_all4runs")

df_panas_Est <- read.csv(paste0(outdir,'./ema_panas_params.csv')) %>%
  pivot_wider(names_from = panas_type, values_from = mean_mu:last_vmu)

```


```{r}
df_PANAS_mean <- df_PANAS %>% 
  ungroup() %>% 
  group_by(Prolific.Id) %>% 
  summarise(PA_mean = mean(PA_sum, na.rm = T),
            NA_mean = mean(NA_sum, na.rm = T),
            PAminusNA_mean = mean(PAminusNA_sum, na.rm = T),
            PA_sd = sd(PA_sum, na.rm = T),
            NA_sd = sd(NA_sum, na.rm = T),
            PAminusNA_sd = sd(PAminusNA_sum, na.rm = T),
            PANA_mean = mean(PANA_sum, na.rm = T),
            PANA_sd = sd(PANA_sum, na.rm = T),
            PA_mssd = psych::rmssd(PA_sum),
            NA_mssd = psych::rmssd(NA_sum),
            PAminusNA_mssd = psych::rmssd(PAminusNA_sum))

df_master <- left_join(df_init_sum,df_PANAS_mean) %>% 
  left_join(df_gor_Est %>%
              attach_prolific_id()) %>% 
  left_join(df_gor_Est2 %>%
              attach_prolific_id()) %>% 
  left_join(df_gor_Est_all %>%
              attach_prolific_id()) %>% 
  left_join(df_gor_Est_wholeday %>%
              attach_prolific_id()) %>% 
  left_join(df_gor_Est_wholeday_all %>%
              attach_prolific_id()) %>% 
  left_join(df_mood %>% 
              filter(block == 1) %>% 
              group_by(Participant.Public.ID,day_block) %>% 
              summarise(moodrate_mean = mean(moodrate, na.rm = T),
                        moodrate_sd = sd(moodrate, na.rm = T),
                        moodrate_mssd = psych::rmssd(moodrate)) %>% 
              rename(Prolific.Id = Participant.Public.ID) %>% 
              pivot_wider(names_from = "day_block", values_from = c("moodrate_mean","moodrate_sd","moodrate_mssd"))%>% 
  mutate(
    moodrate_mean = rowMeans(
      across(c(moodrate_mean_day1_block1, 
               moodrate_mean_day2_block1)), na.rm = TRUE),
    moodrate_sd = rowMeans(
      across(c(moodrate_sd_day1_block1, 
               moodrate_sd_day2_block1)), na.rm = TRUE),
    moodrate_mssd = rowMeans(
      across(c(moodrate_mssd_day1_block1, 
               moodrate_mssd_day2_block1)), na.rm = TRUE)
  ))%>% 
  left_join(df_panas_Est%>%
              attach_prolific_id()) %>% 
  left_join(df_gor_Est_all%>%
              attach_prolific_id())

df_master <- left_join(df_master,df_wof_react %>% 
                         rename(Prolific.Id = Participant.Public.ID))%>% 
  mutate(wof_X1 = (winday_X1 - loseday_X1)/2,
         wof_X2 = (winday_X2 - loseday_X2)/2,
         wof_X3 = (winday_X3 - loseday_X3)/2)
  # mutate(wof_X1 = winday_X1,
  #        wof_X2 = winday_X2,
  #        wof_X3 = winday_X3)


df_days <- df_all %>% 
  filter(day_block %in% c("day1_block2","day2_block2")) %>% 
  group_by(Participant.Public.ID, day_block) %>% 
  slice(1) %>% 
  dplyr::select(Participant.Public.ID, day_block, Local.Date) %>% 
  mutate(
    Local.Date = as.POSIXct(Local.Date, 
                            format = "%d/%m/%Y %H:%M:%S", 
                            tz = "UTC")
  ) %>% 
  pivot_wider(names_from = day_block, values_from = Local.Date) %>% 
  mutate(
    # Exact time difference in hours
    time_diff_hours = as.numeric(difftime(day2_block2, 
                                          day1_block2, 
                                          units = "hours")),
    # Whole calendar day difference
    day_diff = as.numeric(as.Date(day2_block2) - 
                          as.Date(day1_block2))
  ) %>% 
  filter(Participant.Public.ID %in% df_master$Prolific.Id)
  
df_days <- left_join(df_days,df_init_date %>% 
                      mutate(Trigger.Date=as.POSIXct(Trigger.Date, format = "%d/%m/%Y", tz = "UTC"),
                             Trigger.Date=as.Date(Trigger.Date))%>% 
                     rename(Participant.Public.ID=Prolific.Id,Start.Date=Trigger.Date),
                     by  = "Participant.Public.ID") %>% 
  mutate(day_since_enrol = as.Date(day1_block2)-as.Date(Start.Date))
```


### calculate the within-person correlation between PA and NA and use it as a covariate
```{r}
pana_coef <- NULL
for (s in unique(df_PANAS$Prolific.Id)){
  df_PANAS_temp <- df_PANAS %>% filter(Prolific.Id == s) %>% 
    mutate(PA_sum_scaled = as.numeric(scale(PA_sum)),
           NA_sum_scaled = as.numeric(scale(NA_sum)))
  if (prod(!is.na(df_PANAS_temp$NA_sum_scaled)) != 0 &
      prod(!is.na(df_PANAS_temp$PA_sum_scaled)) != 0){
  lm_pana <- lm(scale(PA_sum) ~ scale(NA_sum),df_PANAS_temp)
  lms <- summary(lm_pana)
  
    pana_coef <- rbind(pana_coef,cbind("Prolific.Id" = s,t(lms$coefficients[2,])))
  } else {
    #some participants never rated NA above 10... so in this case the slope is really 0
    pana_coef <- rbind(pana_coef,cbind("Prolific.Id" = s,0,0,0,1))
  }
}


pana_coef <- data.frame(pana_coef) %>% 
  dplyr::select(Prolific.Id, Estimate) %>% 
  mutate(Estimate = as.numeric(Estimate)) %>% 
  rename(PA_NA_corr = Estimate)

df_master <- left_join(df_master,pana_coef)
```

#read demographics
```{r}
# External raw file, outside this repo (not shared): the Prolific demographics
# export used to build demo_info.csv. EDIT this path if re-running on another machine.
demographics_path <- "~/Desktop/MoodInstability/Paper Material for Ryan/AppleTask_scripts_1/Demographics.csv"
demo_info <- read_csv(demographics_path) %>%
  filter(status == "APPROVED") %>% 
  filter(participant_id %in% df_master$Prolific.Id) %>% 
  group_by(participant_id) %>% 
  mutate(rowid = row_number()) %>% 
  filter(rowid == 1) %>% 
  dplyr::select(-rowid)

df_master %>% 
  filter(!Prolific.Id%in% demo_info$participant_id)
```

#output 
```{r}
ls.participant <- intersect(df_master$Prolific.Id,df_all$Participant.Public.ID)
length(ls.participant)

df_master <- df_master %>% 
  filter(Prolific.Id %in% ls.participant)

write.csv(df_master,paste0(outdir,'df_baseline_panas_gorilla_params.csv'))

df_mood_ratings <- df_mood_ratings %>% 
  rename(Prolific.Id = Participant.Public.ID) %>% 
  filter(Prolific.Id %in% ls.participant)

write.csv(df_mood_ratings,paste0(outdir,'moodrate_scaled.csv'))

# ggplot(df_mood_ratings %>% 
#          filter(Prolific.Id == "5f2a94aba340af2e4dab2910", 
#                 day_block %in% c("day1_block1","day2_block1")), aes(x = Trial.Index, y = moodrate))+
#   geom_line(aes(color = day_block),size = 1)+
#   theme_void()+
#   scale_color_brewer(palette = "Paired")+
#   theme(legend.position = "none")+
#   labs(title = "Task")+
# ggplot(df_panas_Est_tc %>% 
#          filter(id == "5f2a94aba340af2e4dab2910",
#                 panas_type %in% c("pos","neg")), aes(x = trial_id, y = origval))+
#   geom_line(aes(color = panas_type),size = 1)+
#   theme_void()+
#     scale_color_brewer(palette = "Dark2")+
#   labs(title = "Ecological")+
#   plot_layout(nrow = 2)
```

## Bayesian model estimate timecourses
### revert mu back into original space!
```{r}
df_gor_Est_tc <- read.csv(paste0(outdir,'./apple_moodrate_params_timecourse.csv')) %>%
  filter(run %in% c("d1r1","d2r1")) %>% #only take the first run each day
  anonymized_id_to_prolific_id() %>%
  group_by(id,run) %>%
  mutate(trial_id = row_number())


df_gor_Est_tc <- left_join(df_gor_Est_tc,
          df_mood_ratings %>% 
  filter(block == 1) %>% 
  dplyr::select(Prolific.Id,day,block,moodrate,max_moodrate,min_moodrate) %>% 
  mutate(run = paste0("d",day,"r",block)) %>% 
  rename(id = Prolific.Id) %>% 
  dplyr::select(-day,-block) %>% #only take the first run each day
  group_by(id,run) %>% 
  mutate(trial_id = row_number()),
  by = c("id","trial_id","run")) %>% 
  rowwise() %>% 
  mutate(mu_orig = mu*10) #y'=y/10 --> y = 10*y'

df_gor_Est_tc <- df_gor_Est_tc%>%
  mutate(subj_day_block = paste0(id,"_",day_block)) %>% 
  filter(!subj_day_block %in% subj_exclude_novariance_rl$subj_day_block)
#the range of mu is from 0.1 to 0.9
#mu = (rawscore - min)/(max-min) * 0.8 + 0.1
#rawscore = (mu - 0.1)/0.8 * (max-min) + min


df_panas_Est_tc <- read.csv(paste0(outdir,'./ema_panas_params_timecourse.csv')) %>%
  anonymized_id_to_prolific_id() %>%
  group_by(id,panas_type) %>%
  mutate(trial_id = row_number())

df_panas_Est_tc <- left_join(df_panas_Est_tc, 
          df_PANAS %>% 
  dplyr::select(Prolific.Id,PA_sum,NA_sum,PAminusNA_sum,max_PAminusNA,min_PAminusNA) %>% 
  rename(id = Prolific.Id,
         pos = PA_sum,
         neg = NA_sum,
         posminusneg = PAminusNA_sum) %>%
    mutate(posminusneg_hr = posminusneg) %>% 
    relocate(posminusneg_hr, .after = posminusneg) %>% 
  pivot_longer(pos:posminusneg_hr,names_to = "panas_type", values_to = "origval") %>% 
  group_by(id,panas_type) %>% 
  mutate(trial_id = row_number()),
  by = c("id","panas_type","trial_id")) %>% 
  rowwise() %>% 
  mutate(mu_orig = mu*100-50) #y'=(y+50)/100 --> y = 100*y'-50

range(df_panas_Est_tc$mu_orig,na.rm = T)
range(df_PANAS$PAminusNA_sum,na.rm = T)
```

```{r}
demo_info <- demo_info %>% 
  filter(participant_id %in% df_master$Prolific.Id)
df_days <- df_days %>% 
  filter(Participant.Public.ID %in% df_master$Prolific.Id)

df_wof <- df_wof %>% 
  filter(Participant.Public.ID %in% df_master$Prolific.Id)

df_totalmon <- df_totalmon %>% 
  filter(Participant.Public.ID %in% df_master$Prolific.Id)

df_wof_react <- df_wof_react %>% 
  filter(Participant.Public.ID %in% df_master$Prolific.Id)
```

```{r}
# panas_results / mood_results (Bayesian AR(1) fits) need df_PANAS / df_mood_AR,
# which only exist once we get to this point in the notebook -- so var1model_utils.R
# and run_var1model.R are sourced here rather than by the caller.
#
# Fitting these 5 brms models (1 PANAS + 4 task blocks, 4 chains x 2000 iter each)
# is slow. Set `read_ar1_from_memory` (in the calling script, e.g.
# write_anonymized_data.R) to TRUE to reuse the cached fit from a prior run instead
# of refitting; FALSE forces a refit and overwrites the cache. Defaults to TRUE
# (prefer the cache) if the caller didn't set it.
if (!exists("read_ar1_from_memory")) read_ar1_from_memory <- TRUE
ar1_cache_path <- "data/var1model_ar1_cache.rds" # relative to repo root (knit_root_dir)

if (read_ar1_from_memory && file.exists(ar1_cache_path)) {
  ar1_cache <- readRDS(ar1_cache_path)
  panas_results <- ar1_cache$panas_results
  mood_results <- ar1_cache$mood_results
} else {
  source("osf_data_and_scripts/scripts/02_deidentify_raw_data/var1model_utils.R")
  source("osf_data_and_scripts/scripts/02_deidentify_raw_data/run_var1model.R")
  saveRDS(
    list(panas_results = panas_results, mood_results = mood_results),
    ar1_cache_path
  )
}

# make task parameter estimates NA for subject × day_block with no mood variance
exclude_pairs <- subj_exclude_novariance_rl %>%
  transmute(Prolific.Id = Participant.Public.ID,
            day_block)

mood_results <- mood_results %>%
  pivot_longer(
    cols = matches("day[12]_block[12]_(AR1|VAR|LOGVAR|MEAN|LOGSIGMA|SIGMA)"),
    names_to = c("day_block","param"),
    names_pattern = "(day[12]_block[12])_(.*)"
  ) %>%
  mutate(value = if_else(
    paste(Prolific.Id, day_block) %in%
      paste(exclude_pairs$Prolific.Id, exclude_pairs$day_block),
    NA_real_, value
  )) %>%
  pivot_wider(
    names_from = c("day_block","param"),
    values_from = "value",
    names_sep = "_"
  )
df_master <- df_master %>%
  left_join(panas_results, by = "Prolific.Id") %>%
  left_join(mood_results,  by = "Prolific.Id") %>%
  mutate(
    TASK_AR1 = rowMeans(cbind(day1_block1_AR1,  day2_block1_AR1),  na.rm = TRUE),
    TASK_VAR = rowMeans(cbind(day1_block1_VAR,  day2_block1_VAR),  na.rm = TRUE),
    TASK_LOGVAR = rowMeans(cbind(day1_block1_LOGVAR, day2_block1_LOGVAR), na.rm = TRUE),
    TASK_SIGMA = rowMeans(cbind(day1_block1_SIGMA,  day2_block1_SIGMA),  na.rm = TRUE),
    TASK_LOGSIGMA = rowMeans(cbind(day1_block1_LOGSIGMA, day2_block1_LOGSIGMA), na.rm = TRUE),
    TASK_MEAN = rowMeans(cbind(day1_block1_MEAN, day2_block1_MEAN), na.rm = TRUE)
  ) %>%
  mutate(
    across(c(TASK_AR1, TASK_VAR, TASK_LOGVAR, TASK_SIGMA, TASK_LOGSIGMA,TASK_MEAN),
           ~ ifelse(is.nan(.x), NA_real_, .x))
  )
```

